### 2016-09-29 Background.tex
add all but eps files

\chapter{Literature Review and Geometric Models}

\section{Introduction}
%not sure what to put here, maybe combine with rbm section
This section details the the basic phenomenon behind rotor blade modulation along with its significance in other applications, and the defining characteristics that allow its use in this application. The second part of this section describes the geometric models for the 2 dimensional case and several 3 dimensional cases. These models will form the basis for verification of the simulations.

\section{Literature Review}
%this is the literature review section on what rbm is and current research in the area
The rotating blades of the helicopter modulate signals that hit the blades by reflecting them. The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point (refs?). The rotor blade modulation (RBM) has a complex form and is influenced by several object parameters. These parameters range from the positioning of a signal source to the physical dimensions of the blades. The resulting modulated signal has been used in radar applications relating to the classification of any aircraft with a rotor blade, propeller or even jet engines (refs?). The doppler shifted signal has also been shown to have a parasitic effect on GPS anti-jamming algorithms (refs?). The role of RBM is based on the specific doppler shift associated with where a dominant reflection occurs along the length of the of the blade, and the associated elevation angle of the transmitter. The modulated signal will then be used to create a mapping between the amount of doppler present and the distance of a transmitter on the ground.

\section{Geometric Models}
The geometric model will begin with a two dimensional scene that will describe the geometry between the rotor blade, the transmitter and the receiver. Then the model will evolve into a selection of three dimensional models that will form the foundation for the results of the ray tracer.

\subsection{2D Geometric Model}
%might want this one to define some parameters but then show what happens when directly over.
The two dimensional geometric mode is based on a few assumptions, one is that the receiver is placed as close as possible to the center of rotation, and second that all the physical objects are located within a single 2D plane. This model is represented in figure \ref{fig:2D_model}.

%2d model figure
\begin{figure}[h]
	\begin{center}
		\includegraphics[width=15cm]{images/background/2d_geometry.eps}
		\caption{2D Geometric model with Rx at the Axis of Rotation}
		\label{fig:2D_model}
	\end{center}
\end{figure}

%describe the situation and the position of the objects
There are three physical objects within this scene. The first is the Rotor blade which is the dark green bar depicted in the figure, next are the transmitter in green $T_x$ and the receiver $R_x$ in blue. The measurements depicted as black bars with denoting start and stop points reference the various distances used in the following equations. The dashed green line shows at which altitude the helicopter is hovering at, and the red dashed line transverses the transmitter and the center of rotation for the blades. $\theta_{El}$ is the elevation angle of the transmitter with respect to the rotor blades and $\theta_r$ denotes the specular reflection of the casted and reflected rays in orange. Lastly the line of sight (LOS) ray shows that the transmitter and receiver are in visual line of sight of each other.

%formulate the geometric equations
(equations for doppler profile)

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/2d_theoretical_doppler_profile.eps}
		\caption{Doppler Frequency vs. Rotor Position with varying Elevation Angle}
		\label{fig:2D_theoretical_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:2D_theoretical_doppler} shows the varying doppler frequency caused by the RBM at various elevation angles of the transmitter. The results of this is a sinusoidal doppler profile in which its amplitude increases as the elevation angle decreases.

%validation consideration
Since this model has the receiver located at the axis of rotation this model can be seen as a special case of the next 3D models, this is because it is symmetric around the axis of rotation. Therefore any placement of the transmitter in 3D space can be distilled down to a 2D profile as such. This symmetry should then be mirrored in the ray tracing simulation as verification.

\subsection{3D Geometric Model}
The three dimensional geometric model is categorized by the position of the rotor blade and the position of the signal source. Since the rotor blade has a specific airfoil shape the models will take that into account through an approximation of that surface. The first model will be representative of having the transmitter inline with both the receiver and the blade, with the transmitter in both fore and aft positions. The next model will have the rotor approaching both the receiver and transmitter, and lastly the rotor will be receding from both the receiver and transmitter. All of the 3D models will have the receiver positioned offset from the axis of rotation.

\subsubsection{Transmitter inline with Receiver and Rotor Blade}
%go over the 3d model for the tx inline with blade fore and aft
The first two models as mentioned above fall under the criteria of the transmitter being inline with both the rotor blade and the offset receiver.

Figure \ref{fig:3D_model_90az} depicts the transmitter at a 90\textdegree \space azimuth angle, which places it inline with the position of the receiver and the current location of the rotating blades.

%describe the situation and the position of the objects
The objects in \ref{fig:3D_model_90az}  are similar to the ones previously stated in the 2D case. The X and Y axis are specifically drawn in blue and red respectfully, with the Z axis now the green dashed line and altitude is now denoted with a measurement bar. The receiver offset in the +Y direction is now stated. and the Blades are now colored gray. All other variables and colors denote their objects as previously stated in the 2D case.

%3d pictures
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_90az.eps}
		\caption{3D Geometric model with Tx at Azimuth angle of 90\textdegree}
		\label{fig:3D_model_90az}
	\end{center}
\end{figure}

%formulate the geometric equations
(equations doppler profile 90 deg)

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_90az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 90\textdegree}
		\label{fig:3D_model_90az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_90az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 90\textdegree. The elevation angle is limited by the reflection angle, caused by the limited distance between the tip of the blade and the location of the receiver. This limitation constrains the doppler profile causing inaccurate transmitter elevation estimation at this transmitter azimuth position.

Figure \ref{fig:3D_model_270az} depicts the transmitter at a 270\textdegree \space azimuth angle, which places it inline with the position of the receiver and the current location of the rotating blades. This placement of the transmitter behind the helicopter is different from the situation in figure \ref{fig:3D_model_90az} because the value of $\theta_r$ is now not limited by the tip of the rotor and can go to smaller elevation angles.

\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_270az.eps}
		\caption{3D Geometric model with Tx at Azimuth angle of 270\textdegree}
		\label{fig:3D_model_270az}
	\end{center}
\end{figure}

%formulate the geometric equations
(equations doppler profile 270 deg)

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_270az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 270\textdegree}
		\label{fig:3D_model_270az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_270az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 270\textdegree. The data from the figure is similar to the data from the previous figure \ref{fig:3D_model_90az} but does not exhibit the limitation on the reflection angle, allowing for smaller elevation angles and larger doppler shifts to occur.

\subsubsection{Approaching Model}
%go over the 3d model for the approaching blade
The approaching model shown in figure \ref{fig:3D_model_180az} depicts the transmitter at an azimuth of 180 \textdegree \space and the axis of X has now been rotated to be -X. The direction of the rotor blades is depicted ,in green, to follow the previous assumptions.

%describe the situation and the position of the objects
This case of the 3D model places the transmitter at 180 \textdegree \space so that the oncoming blades move toward both the receiver and the transmitter at the same time. This particular placement will cause a positive doppler profile because the blades will be moving in the direction of both objects, compressing the reflected wave accordingly.

%3d picture
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_180az.eps}
		\caption{3D Geometric model with Tx at Azimuth angle of 180\textdegree}
		\label{fig:3D_model_180az}
	\end{center}
\end{figure}

%formulate the geometric equations
(equations doppler profile 180 deg)

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_180az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 180\textdegree}
		\label{fig:3D_model_180az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree. The data from the figure shows the maximum of the doppler profile decrease as the elevation angle gets larger.

\subsubsection{Receding Model}
%go over the 3d model for the receding blade
The receding model shown in figure \ref{fig:3D_model_0az} depicts the transmitter at an azimuth of 0 \textdegree \space where the axis positions back to their original places and the direction of the rotor blade is now depicted in red.

%describe the situation and the position of the objects
This case of the 3D model places the transmitter at 0 \textdegree \space so that the receding blades move away from both the receiver and the transmitter at the same time. This particular placement should provide a negative doppler profile because the blades will be moving in the opposite direction of both objects, stretching the reflected wave accordingly.

%3d picture 
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/background/3d_geometry_tx_0az.eps}
		\caption{3D Geometric model with Tx at Azimuth angle of 0\textdegree}
		\label{fig:3D_model_0az}
	\end{center}
\end{figure}

%formulate the geometric equations
(equations doppler profile 0 deg)

%doppler profile result
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/background/3d_geometry_tx_0az_doppler_profile.eps}
		\caption{Doppler profile of Tx at Azimuth angle of 0\textdegree}
		\label{fig:3D_model_0az_doppler}
	\end{center}
\end{figure}

Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree. The data from the figure shows the minimum of the doppler profile increase as the elevation angle gets larger.

### 2016-09-29 Conclusion.tex
add all but eps files

\chapter{Conclusion and Future Work}

\section{Summary}

\section{Future Improvements}

### 2016-09-29 Introduction.tex
add all but eps files

\chapter{Introduction}

\section{Motivation}
In RF communications with a rotorcraft, such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the elevation angle between the axis of rotation and the emitter. RBM can be used in RADAR to detect and classify aircraft based on a specific signature and can degrade communication system located on the rotorcraft itself. The motivation behind this work is to use the RBM effect to locate uncooperative emitters on the ground. This is done through the use of specific knowledge of the craft itself and measuring the RBM in the received signal.

\section{Contribution}
The main contributions of this thesis are as follows. A 3D Ray Tracing software is provided to simulate the RF propagation in the presence of a helicopter rotor blade. The software provides insight into the complex interaction between the rotor blade shape and the placement of the receiver and transmitters. The second contribution is the ability to use the imparted rotor blade modulation to estimate the azimuth and elevation angles with respect to the location of the rotating blades.

\section{Organization}
In Chapter 2 we present the background and theory behind rotor blade modulation. we then formulate the basic geometry behind the RBM effect.

In Chapter 3 we Introduce the radio propagation simulation in several sections. First is the RF propagation model which defines the physical effects that are simulated within the software. Next the objects of the scene model, as well as the dimensionality, are defined in software to be representative of their physical  dimensions and functionality. Lastly we describe the core ray tracing engine that traces the scene in successive frames to build the receiver output.

In Chapter 4 we present the result of the parameter swept simulations of the ray tracing software. Next the received signals from the simulation are analyzed using several DSP techniques to define the signal characteristics that will be used in the next chapter for estimation.

In Chapter 5 Those characteristics are then used to estimate the azimuth and elevation angle of the transmitter based on the given rotor and receiver parameters. Those estimates are then compared with the original position of the transmitter to determine the methods accuracy.

In Chapter 6 the summery of the results are detailed along with the current limitations. Lastly future improvements on the work will be discussed.

### 2016-09-29 MSc. Thesis Template.tex
add all but eps files

%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ----------------------------------------------------------------

% Set up the document
\documentclass[a4paper, 14pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\graphicspath{Figures/}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
%\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
%\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\usepackage{lipsum}

\usepackage{doxygen}

\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
}

\usepackage{setspace}
\doublespacing
\usepackage{tikz}
\usetikzlibrary{fit}
\tikzset{%
  highlight/.style={rectangle,rounded corners,fill=red!15,draw,
    fill opacity=0.5,thick,inner sep=0pt}
}
\newcommand{\tikzmark}[2]{\tikz[overlay,remember picture,
  baseline=(#1.base)] \node (#1) {#2};}
%
\newcommand{\Highlight}[1][submatrix]{%
    \tikz[overlay,remember picture]{
    \node[highlight,fit=(left.north west) (right.south east)] (#1) {};}
}
\usepackage{algorithm}
\usepackage{amsmath, amssymb}
\usepackage[noend]{algpseudocode}
\usepackage{graphicx}
\makeatletter
\def\BState{\State\hskip-\ALG@thistlm}
\makeatother
\usepackage{epstopdf}
\usepackage{amsfonts}
\usepackage{siunitx}
\usepackage{caption}
\usepackage{float}
\usepackage{relsize}
\usepackage{amsmath}
\usepackage[framed,numbered,autolinebreaks,useliterate]{mcode}
\usepackage{url,textcomp}
%\usepackage[style=ieee]{biblatex}
\usepackage{cite}
\usepackage{subcaption}

% ----------------------------------------------------------------
\begin{document}

% Set up the Title Page
\title  {Emitter Source Geolocation from Imparted Rotor Blade Modulation}
\authors  {\texorpdfstring
            {\href{your web site or email address}{Thomas Schucker}}
            {Author Name}
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}
\maketitle

%% ----------------------------------------------------------------
\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round
% Define the page headers using the FancyHdr package and set up for one-sided printing
\fancyhead{}  % Clears all page headers and footers
\rhead{\thepage}  % Sets the right side header to show the page number
\lhead{}  % Clears the left side page header
\pagestyle{fancy}  % Finally, use the "fancy" page style to implement the FancyHdr headers

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\Declaration{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics

\qquad This thesis has been submitted in partial fulfillment of requirements for an advanced degree at the University of Arizona and is deposited in the University Library to be made available to borrowers under rules of the Library.

\qquad	Brief quotations from this thesis are allowable without special permission, provided that an accurate acknowledgement of the source is made. Requests for permission for extended quotation from or reproduction of this manuscript in whole or in part may be granted by the head of the major department or the Dean of the Graduate College when in his or her judgment the proposed use of the material is in the interests of scholarship.  In all other instances, however, permission must be obtained from the author.

\center{ SIGNED:  Thomas Schucker}

\vspace{3cm}

APPROVAL BY THESIS DIRECTOR

This thesis has been approved on the date shown below:\\
 \bigskip
 \bigskip
 \bigskip 
\rule[1em]{15em}{0.5pt} \hfil \rule[1em]{15em}{0.5pt}\\  % This prints a line for 
Tamal Bose\hspace{10cm}Date\\
Professor of\hspace{10.5cm}.\\
Electrical and Computer Engineering\hspace{6.3cm}.\\
}
\clearpage  % Declaration ended, now start a new page
%% ----------------------------------------------------------------

\setstretch{1.3}  % Reset the line-spacing to 1.3 for body text (if it has changed)

% The Acknowledgements page, for thanking everyone
\acknowledgements{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
I would like to thank my thesis advisor Dr. Tamal Bose for the opportunity to work in his lab, and for the guidance through graduate school. I would also like to thank Matt Kruse and Charlie Cooper for coming up the research topic and support through the process. I would also like to thank the Broadband Wireless Access \& Applications Center and Rincon Research Corporation for supporting my research.
}
\clearpage  
% End of the Acknowledgements

%% ----------------------------------------------------------------
% Begin the Dedication page

\setstretch{1.3}  % Return the line spacing back to 1.3
\pagestyle{empty}  % Page style needs to be empty for this page
\dedicatory{To my Mother and Father, \\my brother Danny, \\and my lovely girlfriend Clarice,\\all with love, \\Thank you for your unconditional support.}
\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics

%-------------------------------------------------
\pagestyle{fancy}  
%The page style headers have been "empty" all this time, now use the "fancy" headers as defined before to bring them back

%% ----------------------------------------------------------------
\lhead{\emph{Contents}}  % Set the left side page header to "Contents"
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
\lhead{\emph{List of Figures}}  % Set the left side page header to "List if Figures"
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
\lhead{\emph{List of Tables}}  % Set the left side page header to "List of Tables"
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
\setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
%\clearpage  % Start a new page
%\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
%\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
{
% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\

}

%% ----------------------------------------------------------------
%\clearpage  % Start a new page
%\lhead{\emph{Mathematical Notations}}  % Set the left side page header to "Physical Constants"
%\listofconstants{ll}  % Include a list of Physical Constants (a four column table)
{
% Constant Name & Symbol & = & Constant Value (with units) \\

}

%% ----------------------------------------------------------------
%\clearpage  %Start a new page
%\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
%\listofnomenclature{ll}  % Include a list of Symbols (a three column table)
{
% symbol & name & unit \\

}
%% ----------------------------------------------------------------
% End of the pre-able, contents and lists of things
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{
\addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
In RF communications with a rotorcraft, such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM). This modulation is caused by the reflection of a signal off the rotating blades. The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter. RBM is known to degrade the performance of RF communications on rotorcraft and can be used in RADAR applications to detect and classify aircraft, but there is little on its usefulness in other areas.This project will look at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground. To do this a RF ray tracing program was developed in C++ to produce a simulation of the RBM.
}

\clearpage  % Abstract ended, start a new page

%% ----------------------------------------------------------------
%\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{fancy}  % Return the page headers back to the "fancy" style

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\clearpage  %Start a new page
\lhead{\emph{Introduction}}
\include{Introduction}

\clearpage  %Start a new page
\lhead{\emph{Literature Review and Geometric Models}}
\include{Background}

\clearpage  %Start a new page
\lhead{\emph{Radio Propagation Simulation}}
\include{Radio_Propagation_Simulation}

\clearpage
\lhead{\emph{Received Signal Simulation}}
\include{Simulation}

\clearpage  %Start a new page
\lhead{\emph{Results}}
\include{Results_new}

\clearpage  %Start a new page
\lhead{\emph{Conclusion and Future Work}}
\include{Conclusion}

\clearpage  %Start a new page

%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}} % Add a gap in the Contents, for aesthetics

\appendix % Cue to tell LaTeX that the following 'chapters' are Appendices

\lhead{\emph{Ray Tracing Software}}
\include{Ray_Tracing_Software}

\lhead{\emph{Class Documentation}}
\chapter{Class Documentation}
\include{doxygen/latex/class_blade__surface}
\include{doxygen/latex/class_bounding__box}
\include{doxygen/latex/class_point3_d}
\include{doxygen/latex/class_ray3_d}
\include{doxygen/latex/class_receiver}
\include{doxygen/latex/class_rib}
\include{doxygen/latex/class_rotor}
\include{doxygen/latex/class_scene}
\include{doxygen/latex/class_sphere}
\include{doxygen/latex/class_transmitter}
\include{doxygen/latex/class_triangle}
\include{doxygen/latex/class_vector3_d}

\include{Simulation_Data}

\include{Matlab_Code}

%\input{Appendices/AppendixA} % Appendix Title
%\input{Appendices/AppendixB} % Appendix Title
%\input{Appendices/AppendixC} % Appendix Title

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
\backmatter

%% ----------------------------------------------------------------
\label{Bibliography}
\lhead{\emph{Bibliography}}  % Change the left side page header to "Bibliography"
\bibliographystyle{IEEEtran}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
%\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"

\end{document}  % The End
%% ----------------------------------------------------------------

### 2016-09-29 Radio_Propagation_Simulation.tex
add all but eps files

\chapter{Radio Propagation Simulation}

\section{Introduction}
%introduce the section and what will be discussed here
The simulation software is broken down into three main components, the radio wave propagation model, the scene model, and the ray tracing engine. The wave propagation model is a collection of equations that describe the physical phenomena that affect the propagation when represented by rays. The model used is based upon classical geometric optics to work with the ray tracing engine. The scene model is comprised of a three dimensional environment in order to define the physical rotor blade surface. The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions. The ray tracing engine uses recursive execution described by Turner Whitted (Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively.

\section{Radio Propagation Model}
%define the math behind the physical laws that are simulated within the simulation
The propagation model defined in this project will focus on the following physical phenomena, free-space path loss, reflection, and the doppler effect. They are all formally established models described in full in (place refs here). Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made in the scene model.

\subsection{Free-Space Path Loss}
%describe path loss
Free-Space path loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power is

%FSPL formula
\begin{equation}
	 P_r = G_r G_t P_t \left (\frac{\lambda}{4\pi R}\right)^2
	 \label{eqn:FSPL}
\end{equation}

%formula description
where $P_r $ is the power at the receiver, $P_t$ is the power at the transmitter, $G_r$ and $G_t$ are the antenna gains, 
$\lambda$ is the wavelength, and $R$ is the distance between the receiver and transmitter antennas. In the simulations described in this paper, $G_r$ and $G_t$ are assumed to have a value of 1.

\subsection{Reflection}

\subsubsection{Specular Reflection}
In the case of a perfect reflection the angle of the reflection is calculated by

%Spec formula
\begin{equation}
	\theta_r = \cos^{-1}(\vec{n} \bullet (-\vec{d_i}))
	\label{eqn:spec}
\end{equation}

%formula description
where $\theta_r$ is the angle of the reflected ray, $\vec{n}$ is the normal vector to the surface, and $\vec{d_i}$ is the direction vector of the incident ray.

\subsubsection{Reflection Loss}
Power loss due to surface reflection is described through the following coefficient

%Reflection loss formula
\begin{equation}
	\Gamma = \frac{\cos(\theta_i) - \sqrt{\varepsilon}\cos(\theta_t)}{\cos(\theta_i) + \sqrt{\varepsilon}\cos(\theta_t)}
	\label{eqn:RL}
\end{equation}

%formula description
where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell?s law \ref{eqn:snell}.

\begin{equation}
	\theta_t = \sin^{-1}\left(\frac{\sin(\theta_i)}{\sqrt{\varepsilon}} \right)
	\label{eqn:snell}
\end{equation}

In the following simulations performed, $\varepsilon$ will have a value of (-), which is an approximate value for (-). The final reflected power is

\begin{equation}
	P_{reflected} = P_i|\Gamma|
	\label{eqn:reflected_power}
\end{equation}

where $P_i$ is the incident power before reflection losses.

\subsubsection{Diffuse Reflection}
A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (refs?). The hemisphere is located at the point of the ray hit, producing rays away from the surface. To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (refs?). There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(refs?). This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces. Since is was not designed for longer wavelengths used in RF communications an assumption is made that small scale features of the surface, relevant to light waves,  produce a reflectance distribution similar for larger wavelengths. The BRDF parameters were then selected to be frequency independent to form a plausible reflectance distribution for the physical effects.

\subsection{Doppler Effect}
%define doppler effect
The Doppler effect is characterized by

%Doppler formula
\begin{equation}
	f = \left ( \frac{c + v_r}{c + v_s} \right ) f_0
	\label{eqn:formalDop}
\end{equation}

It is assumed that both the receiver and the transmitter are not moving, therefore the only doppler imparted on the signal will be from the rotation of the blades. The associated Doppler is calculated using

%formula for doppler on the rotor blade.
\begin{equation}
	f = f_0 + \frac{2\Delta v}{\lambda} %reradiated after reflection...
	\label{eqn:observedShift}	
\end{equation}

where $f_0$ is the initial transmitted frequency, $lambda$ is the wavelength, and $\Delta v$ is the difference in velocity.

\begin{equation}
	\lambda = \frac{c}{f_0}
	\label{eqn:wavelength}
\end{equation}

where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$

\begin{equation}
	\Delta v = r \omega_r (\vec{d_p} \bullet \vec{d_r})
	\label{eqn:deltav}
\end{equation}

%formula description
where $\Delta v$ is the difference in velocity between the point of reflection along the length of the rotor blade in the direction of the reflection characterized by equation \ref{eqn:deltav}. Where $r$ is the radius along the length of the blade where the reflection occurs. $\omega_r$ is the angular velocity of the rotor. $\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_r}$ is the normalized vector that is in the direction of the resulting reflected ray.

\section{Scene Model}
% describe what the scene model is and how it will fit in to the ray tracer and the 3d setting
The scene model is the 3D environment in which the physical objects are placed. 
The model is comprised of three types of objects, the rotor blades, transmitter and receiver. The rotor blade is the most complex object due to its airfoil shape. The transmitter is a point source that projects the rays into the scene, and the receiver is described in a similar fashion with a surrounding boundary layer. There are no other objects within the scene, this is because the effect of the rotor on the received signal is to be analyzed for defining characteristics in the best case scenario.

\subsection{Rotor Blade}
%go over the shape of the blade
The rotor blade is the most complex object within the scene due to its airfoil shape. The airfoil shape is designed to produce lift for the helicopter, and designing one is outside the scope of this project. Fortunately there are databases that provide real helicopter airfoil designs in x,y coordinates. Theses designs form a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade.

%figure of 2D airfoil
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/radio_propagation/2d_airfoil.png}
		\caption{Airfoil}
		\label{fig:airfoil}
	\end{center}
\end{figure}

%go over how it is formed and the tessellation code
The 2D airfoil sections will form the ribs of the rotor blade but the surface of the blade will be made up of primitive surfaces to approximate the curved airfoil shape. The primitive shapes are triangles that span between the ribs and go around to cover the surface. The surface normals are then adjusted to match the correct directionality.

%figure of tessilation
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/radio_propagation/blade_surface_tesselation.eps}
		\caption{Tessilation}
		\label{fig:tessilation}
	\end{center}
\end{figure}

%modular parameters
All aspects of the rotor blade are parameterized. Starting with the airfoil shape, which is defined by a set of 2D coordinates. The length and the number of rib sections can be configured along with the number of blades and corresponding altitude. As well as the RPM. This allows the scene to replicate any type of rotor configuration and position it at a specific altitude.

\subsection{Transmitter}
%point source transmitter casting rays in specific direction
The transmitter is modeled as a point source, this means that all the radio waves are projected from this point into the scene. It is assumed that the transmitter is located on the ground within the x,y plane in relation ship to the rotor blades. The transmitter is configured with a center frequency and is assumed to produce a tone at that frequency. Therefor signal produced has no inherent modulation applied to it.
%direction creation
Being that the Transmitter is emitting radio waves into a 3D space it is assumed to be transmitting in an omnidirectional fashion, but because the rotor and the receiver are the only two other objects within the scene radio waves will only be propagated in their direction. This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture and eliminates computational overhead for the tracing engine.

%figure of transmitter direction
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/radio_propagation/transmitted.eps}
		\caption{Transmitter Rays}
		\label{fig:transmitter_direction}
	\end{center}
\end{figure}

\subsection{Receiver}
%physical receiver dimensions and antenna chars
The receiver object is modeled as a point in 3D space with a surrounding boundary layer in the shape of a sphere. This is because the receiver is assumed to have an omnidirectional antenna which will receive radio waves from all directions uniformly. The receiver will record any ray that hits the boundary layer within each frame of the simulation to create a sample of data at that instance in time.
%processing in each frame
The sample is produced using superposition of all the rays that are acting on the receiver at that instance in time which are then extrapolated to produce a clear result.
%realism
The receiver is configurable allowing the user to set a desired center frequency along with the sampling rate of the simulated hardware. The sampling rate will determine several simulation parameters in the ray tracer due to the need to associate this rate with the change in the rotor position for the next frame. The consequence of this is that increasing the sample rate will produce higher resolution results but will increase the computational overhead of the simulation.

\section{Ray Tracing}
%describe the core tracing engine and describe the flow of the program
The ray tracing simulation is performed in the Monte Carlo fashion building in the scene and propagation models. Raytracing is a well established method for creating realistic images in (ray tracing papers). The simulation is performed over successive iterations, each iteration is called a frame. Each frame will be updated to represent the change in the position of the rotor blade.

\subsection{Computation}
%flow of the program
The ray tracing engine first sets up the environment creating the surfaces and placing the objects in the scene. Then the number of frames that will be computed. The number of frames are determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver. This is described by

%frame rates equation
\begin{equation}
	Frames = \frac{60  f_s}{RPM} Rev
	\label{eqn:frames}
\end{equation}

where $Frames$ is the number of frames that will be computed in the simulation, $f_s$ is the sampling frequency of the receiver, $RPM$ is the revolutions per minuet of the rotor, and $Rev$ is the number of revolutions that the rotor makes in the simulation.

In each frame a set number of rays are casted into the scene in a uniformly distributed circle in the direction of the rotor and receiver using

%uniform disk equation
\begin{equation}
	v_{ray} = \begin{bmatrix}
			x \\
			y \\
			z \\
	\end{bmatrix}
	= \begin{pmatrix}
			\sqrt{r} \cos{\theta_u}  + d_x\\
			\sqrt{r} \sin{\theta_u}  + d_y \\
			d_z \\
	\end{pmatrix}
	\label{eqn:disk}
\end{equation}

The casting technique reduces the computation overhead by limiting the space. It also creates higher resolution result by focusing the limited number of rays in the direction of the other objects.

%figure of casting disk
\begin{figure}
	\begin{center}
		\includegraphics[width=15cm]{images/radio_propagation/sampling_method.eps}
		\caption{Disk Sampling Method}
		\label{fig:samp_method}
	\end{center}
\end{figure}

When a ray is casted into the scene it has an origin point, a direction vector, a frequency and an initial power level. The ray then travels through the scene till it encounters another object. If there is a collision with the receiver it is recorded. If the ray collides with a rotor blade a new ray is calculated based on the normal to the geometric surface. The new ray's power is updated as well as an updated frequency since the blade is moving. The power level is adjusted based on the BRDF of the specific material. Due to only the rotor and receiver in the scene, besides the transmitter, rays that are found to hit the rotor the reflection ray is calculated. Then the angle between the reflection and a ray between the point of reflection and the receiver is used to create a dedicated ray in that direction with a decayed power and adjusted frequency.

%psudo code

%uml diagrams

\subsection{Output}
%iq samples
The superposition of these receiver contributions during each frame creates the received signal data. The received signal data will then be visualized in spectrograms over the length of the simulated time. The simulations do not render in real time but creates a CSV file that can then be loaded into MATLAB for signal processing.

### 2016-09-29 Ray_Tracing_Software.tex
add all but eps files

\chapter{Ray Tracing Software}
something for code reuse and the git hub stuff

### 2016-09-29 Results.tex
add all but eps files

\chapter{Results}

\section{Introduction}
%introduce the results section and what processing will be done
The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter. First the azimuth angle will be estimated which will provide the information necessary for calculating the elevation angle.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Transmitter Azimuth Angle Estimation}
%formulate the estimation equation and discuss ambiguity considerations
The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which at a set angle a doppler envelope is calculated and subsequent maximum and minimum values are collected. After a complete rotation the doppler maximum and minimum values produce a sinusoidal pattern as shown in figure \ref{fig:tx_azimuth_angle_200} without the assumption of knowing the starting azimuth angle. With this data we need to find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle. To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in figure \ref{fig:azimuth_estimation_max_vs_absMin}.

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_max_vs_absMin.eps}
		\caption{Max and Absolute value of Min Envelope Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_max_vs_absMin}
	\end{center}
\end{figure}

From figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference \ref{eqn:difference}

%formula for difference
\begin{equation}
	 Envelope Difference = Max Upper Envelope - | Min Lower Envelope |
	 \label{eqn:difference}
\end{equation}

we produce an almost exact sinusoid centered around zero, shown in figure \ref{fig:azimuth_estimation_difference}.

 \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_difference.eps}
		\caption{Difference between Max and Min Envelope Calculations vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_difference}
	\end{center}
\end{figure}

While figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself, therefore by computing \ref{eqn:addition}

% -------------------------dont use------------------------------------
%formula for addition
\begin{equation}
	 Envelope Addition = Max Upper Envelope + | Min Lower Envelope |
	 \label{eqn:addition}
\end{equation}

it results in a trend that contains a global minimum at an azimuth of 90\textdegree \space as shown in figure \ref{fig:azimuth_estimation_max_plus_absMin}.

 \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_max_plus_absMin.eps}
		\caption{Max plus Absolute value of Min envelope Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_max_plus_absMin}
	\end{center}
\end{figure}
% -------------------------dont use------------------------------------

Finding the index location of the minimum determines the point at which the transmitter is at an azimuth of 90\textdegree. Which means the transmitter and receiver are in line with each other producing the case from model \ref{fig:3D_model_90az}. The 90\textdegree \space location is displayed in figure \ref{fig:azimuth_estimation_plotted} which places the point on the difference between max and min envelopes therefore providing an accurate representation of the transmitters azimuth angle.

  \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_plotted.eps}
		\caption{Transmitter Azimuth Estimation After full 360deg Rotation at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_plotted}
	\end{center}
\end{figure}

In order to determine the accuracy of azimuth estimation two more elevation angles were tested using the same method. Figure \ref{fig:two_azimuth_estimation_max_plus_absMin} shows the estimation of the 90\textdegree \space for two more elevation angles to compare the accuracy of the estimation method.

 \begin{figure}
 \centering
 \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{images/results/Azimuth_angle_estimation_max_plus_absMin_26deg.eps}
        \caption{Elevation Angle of 26.56\textdegree}
         \label{fig:azimuth_estimation_max_plus_absMin_26.56deg}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\linewidth]{images/results/Azimuth_angle_estimation_max_plus_absMin_76deg.eps}
        \caption{Elevation Angle of 76\textdegree}
        \label{fig:azimuth_estimation_max_plus_absMin_76deg}
    \end{subfigure}
    \caption{Max plus Absolute value of Min envelope Frequencies vs Transmitter Azimuth Angle}
    \label{fig:two_azimuth_estimation_max_plus_absMin}
 \end{figure}

The error in the estimation for both elevation angles of 45\textdegree \space and 76\textdegree \space are exact matches with no error but at an elevation of 26.56\textdegree \space has an error of 9\textdegree. The issue with this data is that there is a limited sample set of 41 samples around the azimuth range of 360\textdegree. In order to improve the estimation we can combine the information from figure \ref{fig:azimuth_estimation_difference}, which is zero at both azimuth angles of 90\textdegree \space and 270\textdegree, and figure \ref{fig:azimuth_estimation_max_plus_absMin} which contains a global minimum close to 90\textdegree. By taking the absolute value of equation \ref{eqn:difference} and adding that to equation \ref{eqn:addition} we produce equation \ref{eqn:amplified_minimum}

\begin{multline}
	 Amplified Minimum = | Max Upper Envelope - | Min Lower Envelope | | + \\ (Max Upper Envelope + | Min Lower Envelope |)
	 \label{eqn:amplified_minimum}
\end{multline}

figure \ref{fig:amplified_azimuth_estimation} which shows a sharp global minimum at 90\textdegree \space and a sharp local minimum at 270\textdegree alowing for better estimation of the transmitter angle.

  \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Amplified_azimuth_angle_estimation_45deg.eps}
		\caption{ (-) at an Elevation Angle of 45\textdegree}
		\label{fig:amplified_azimuth_estimation}
	\end{center}
\end{figure}

The error in estimation is zero across all three elevation angles using the $AmplifiedMinimum$ data to find the 90\textdegree azimuth angle by exploiting the fact that the intersections of the two data sets in figure \ref{fig:azimuth_estimation_max_vs_absMin} occur at different frequencies, 90\textdegree \space azimuth intersection at the lower frequency and 270\textdegree \space at a higher frequency.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Transmitter Elevation Angle Estimation}
%formulate the estimation equation and discuss ambiguity considerations
Using the information gathered from the azimuth estimation procedure we can compute the elevation angle of the transmitter. In the process of gathering azimuth information the maximum and minimum envelopes follow a sinusoidal pattern that contains a maximum doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles. Using that maximum value and the assumption that it comes from a reflection close to the end of the blade we have enough information to determine the elevation angle.

%using acos to determine angle
The equation from (-) shows how doppler is related to the elevation angle $\alpha$, by assuming that doppler value is coming from the tip of the rotor blade we can solve for $\alpha$

%alpha equation elevation angle
 (theta elevation equation)

%equation for  max doppler on blade at end
(equation max doppler at blade end)

%refer back to elevation angle section in simulations for 180 deg.
Taking the data gathered during the elevation angle simulations in section(-) we can measure the accuracy of the estimation. Figure (-) shows the elevation angle estimation versus the actual, and the percent error of the estimation.

%figure of 180deg estimation and percent error

### 2016-09-29 Results_new.tex
add all but eps files

\chapter{Results}

\section{Introduction}
%introduce the results section and what processing will be done
The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter. First the azimuth angle will be estimated which will provide the information necessary for calculating the elevation angle. The results of the estimation techniques are then analyzed to determine their accuracy compared to the actual.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Transmitter Azimuth Angle Estimation}
%formulate the estimation equation and discuss ambiguity considerations
The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which at a set angle a doppler envelope is calculated and subsequent maximum and minimum values are collected. After a complete rotation the doppler maximum and minimum values produce a sinusoidal pattern as shown in figure \ref{fig:tx_azimuth_angle_200} without the assumption of knowing the starting azimuth angle. With this data we need to find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle. To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in figure \ref{fig:azimuth_estimation_max_vs_absMin}.

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_max_vs_absMin.eps}
		\caption{Max and Absolute value of Min Envelope Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_max_vs_absMin}
	\end{center}
\end{figure}

From figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference \ref{eqn:difference}

%formula for difference
\begin{equation}
	 Envelope Difference = Max Upper Envelope - | Min Lower Envelope |
	 \label{eqn:difference}
\end{equation}

we produce an almost exact sinusoid centered around zero, shown in figure \ref{fig:azimuth_estimation_difference}.

 \begin{figure}[b]
	\begin{center}
		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_difference.eps}
		\caption{Difference between Max and Min Envelope Calculations vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:azimuth_estimation_difference}
	\end{center}
\end{figure}

While figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself, therefore by computing the correct doppler to use from the $Max Upper Envelope$ and the $| Min Lower Envelope |$. This is done by evaluating the difference at each angle and if the difference is negative the $| Min Lower Envelope |$ is used and if positive the $Max Upper Envelope$.

%matlab for corrected doppler
\begin{lstlisting}
%corrected Doppler frequency for processing
for i = 1:length(upper)
    if(difference(i) < 0)
       correct_fd(i) = abs(lower(i));
    else
       correct_fd(i) = upper(i);
    end
end
\end{lstlisting}

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Correct_doppler.eps}
		\caption{Correct Doppler Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:correct_fd}
	\end{center}
\end{figure}

The correct Doppler is shown in figure \ref{fig:correct_fd} which displays the amount of doppler that is currently acting on the signal for that specific azimuth angle. The data gathered contains a global minimum at 90\textdegree \space and a second local minimum at 270\textdegree. The 90\textdegree \space can be found easily by taking the minimum of the correct Doppler signal

%matlab minimum code
\begin{lstlisting}
%Minimum of corrected Doppler
[Min,I_min] = min(correct_fd);
\end{lstlisting}

%figure of minimum located vs azimuth
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Correct_doppler_with_Minumum.eps}
		\caption{Correct Doppler Frequencies with Minimum vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:min_correct_fd}
	\end{center}
\end{figure}

But in order to find the local minimum at 270\textdegree \space we need to use a different method. To do this we can use the peak detection function within Matlab to locate both the 90\textdegree and 270\textdegree point. By taking the inverse of the correct Doppler and tuning the peak detection function with the maximum and minimum values to determine accurate prominence.

%matlab peak detection code with tuning params
\begin{lstlisting}
%peak detection with prominence calculation
min_peak_prominence = (1/(Max - Min))*.5;
[pk,lc] = findpeaks(1./correct_fd, 'NPeaks', 2, 'MinPeakProminence', min_peak_prominence);
\end{lstlisting}

%figure with peak detection plotted vs azimuth
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Correct_doppler_inverse_peaks.eps}
		\caption{Peaks of inverted Correct Doppler vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:peaks}
	\end{center}
\end{figure}

From figure \ref{fig:peaks}  we see the two peaks denoted by the red x's, one at 90\textdegree \space and the other at  270\textdegree. Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space 270\textdegree locations. Because it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.

%figure with power plot with 90 and 270 denoted
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/average_power_vs_Azimuth.eps}
		\caption{Average Power vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
		\label{fig:ave_power}
	\end{center}
\end{figure}

Figure \ref{fig:ave_power}  shows the average power at each angle sample with the angles 90\textdegree \space and 270\textdegree denoted. From the plot we can see that the average power at 90\textdegree \space is much smaller than the the power at 270\textdegree, so this inequality will be used to resolve ambiguity in the azimuth angle.

From there the Minimum method and the peak method can be compared to see if they agree on the 90\textdegree \space location. If this is not the case one will be chosen and the helicopter can fly in that direction and measure based on the physical movement of the helicopter or if the resulting envelope got larger or smaller because of the change in elevation angle.

%azimuth error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
     200 & 76\textdegree & 0 & 0  \\ \hline
     200 & 45\textdegree & 0 & 0  \\ \hline 
     200 & 26.5\textdegree & 0 & 0  \\ \hline
     500 & 78.7\textdegree & 0 & 0  \\ \hline
     500 & 51.34\textdegree & 0 & 0  \\ \hline 
     500 & 35.5\textdegree & 0 & 0  \\ \hline
    \end{tabular}
     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles During Azimuth Estimation}
    \label{tab:az_error_and_percent}
\end{center}
\end{table}

From table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of Altitude and elevation angles that were tested. But because of the algorithm could potentially pick the 270\textdegree we will analyze the difference in peak heights and the power difference to evaluate the estimation further.

\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | p{3cm} | p{3cm} | p{3cm} |}
    \hline
    Altitude & Elevation Angle & Percent Peak Difference & Power Difference in dB & Peak Frequency Difference Hz\\ \hline
     200 & 76\textdegree & -16.8675\% & -14.0914  & 18.67 \\ \hline
     200 & 45\textdegree & -39.1124\% & -19.7476  &  176.267\\ \hline 
     200 & 26.5\textdegree & -69.7368\% & -13.3443 & 424.0 \\ \hline
     500 & 78.7\textdegree & -21.6667\% & -11.4508  & 17.33 \\ \hline
     500 & 51.34\textdegree & -38.1875\% & -22.4610  & 162.93 \\ \hline 
     500 & 35.5\textdegree & -53.4303\% & -18.6043  & 313.6 \\ \hline
    \end{tabular}
    \caption{Percent Peak, Power, and Frequency Difference of Different Elevation Angles During Azimuth Estimation}
    \label{tab:peaks_and_power}
\end{center}
\end{table}

From table \ref{tab:peaks_and_power} we can see that at the larger elevation angles the peak percent difference are significant to determine which is correctly the 90\textdegree value, but from the Peak frequency difference at the large elevation angles the difference is in the tens of Hz so in practical applications it is possible to confuse the estimation by just taking the minimum frequency so other values need to play a role such as the power.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Transmitter Elevation Angle Estimation}
%formulate the estimation equation and discuss ambiguity considerations
Using the information gathered from the azimuth estimation procedure we can compute the elevation angle of the transmitter. In the process of gathering azimuth information the maximum and minimum envelopes follow a sinusoidal pattern that contains a maximum Doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles. Using that maximum value along with the correct Doppler and the assumption that the maximum will occur near the tip of the rotor blade we can approximate the respected reflection radii off the blade as the azimuth angle changes. This is done through 
%reflection radius aproximation equation
\begin{equation}
	R_{Estimate} = BladeLength \left(\frac{f_{DopplerCorrect}(\theta_{Az})}{Max(f_{DopplerCorrect})}\right)
	\label{eqn:r_estimate}
\end{equation}

where $R_{Estimate}$ is the estimated reflection radius at a particular azimuth, $BladeLength$ is the length of a single blade or radius of the rotor, and $f_{DopplerCorrect}$ is the correct doppler frequency for each azimuth angle $\theta_{Az}$.

%figure of radius estimation 
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Estimated_reflection_radius_Azimuth_range.eps}
		\caption{Estimated Reflection Radius at an Elevation Angle of 45\textdegree}
		\label{fig:est_radius_azimuth_range}
	\end{center}
\end{figure}

Figure \ref{fig:est_radius_azimuth_range} shows the estimated reflection radius for each azimuth angle.

Now we find the maximum amount of Doppler that could be induced at that reflection radius location through
%max doppler at radius location
\begin{equation}
	f_{Doppler_{R Estimate Max}} = 2\frac{v_r f_c}{c}
	\label{eqn:max_doppler}
\end{equation}

where $f_{Doppler_{R Estimate Max}}$ is the maximum amount of doppler that could happen at that location if the signal was reflected parallel to the direction of motion. $f_c$ is the center frequency of the signal, $c$ is the speed of light and $v_r$ is the radial velocity based of the $RPM$ defined by

%radial velocity
\begin{equation}
	v_r = \frac{2\pi}{60} RPM R_{Estimate}
	\label{eqn:v_radial}
\end{equation}

Then to find the elevation angle we look back at equation (-) where we then solve for the elevation angle 
%Elevation angle
\begin{equation}
	\theta_{El} = acos\left(\frac{f_{DopplerCorrect(\theta_{Az})}}{f_{Doppler_{R Estimate Max}}}\right)
	\label{eqn:elevation_angle}
\end{equation}

where $\theta_{El}$ is the elevation angle of the transmitter. If the elevation angle is all the information needed equation \ref{eqn:elevation_angle} distills down to

%Elevation angle
\begin{equation}
	\theta_{El} = acos\left(\frac{Max(f_{DopplerCorrect})}{f_{DopplerMax}}\right)
	\label{eqn:elevation_angle_only}
\end{equation}

%figure of elevation angle 
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Elevation_angle_comparason_Azimuth_range.eps}
		\caption{Actual Elevation Angle and Estimated Elevation Angle vs Azimuth Angle}
		\label{fig:elevation_comparason_azimuth_range}
	\end{center}
\end{figure}

Figure \ref{fig:elevation_comparason_azimuth_range} shows the estimation of the elevation angle $\theta_{El}$ with respect to the azimuth angle, what it shows is that the elevation angle remains constant with respect to azimuth angle. which means that the estimation in the reflection radius is correctly compensating for the azimuth angle. The percent error off the actual elevation angle is shown in figure \ref{fig:percent_error_elevation_azimuth_range} which is very small and consistent over the azimuth range.

%figure of percent error
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Elevation_angle_percent_error_Azimuth_range.eps}
		\caption{Elevation Angle Percent Error vsTransmitter Azimuth Angle}
		\label{fig:percent_error_elevation_azimuth_range}
	\end{center}
\end{figure}

% Elevation error table
\begin{table}
\begin{center}
    \begin{tabular}{ | l | l | l | l |}
    \hline
    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
     200 & 76\textdegree & -0.4632\textdegree & -0.6097\%  \\ \hline
     200 & 45\textdegree & -0.3809\textdegree & -0.8464\%  \\ \hline 
     200 & 26.5\textdegree & -0.4072\textdegree & -1.5329\%  \\ \hline
     500 & 78.7\textdegree & 0.0914\textdegree & 0.1162\% \\ \hline
     500 & 51.34\textdegree & -0.6236\textdegree & -1.2146\%  \\ \hline 
     500 & 35.5\textdegree & -0.6803\textdegree & -1.9143\%  \\ \hline
    \end{tabular}
    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles During Azimuth Estimation}
    \label{tab:elevation_error_percent}
\end{center}
\end{table}

From table \ref{tab:elevation_error_percent} elevation estimation error is extremely small for the given actual elevation angles. But there is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.

%-----------------------------------------------------
% range limitations of this aproximation
%-----------------------------------------------------

This error is caused by a limitation on the estimation is that the doppler shift is limited by the maximum amount doppler that the blade rotation can produce shown in equation (-) by replacing $v_r$ with $v_rMax$ which is calculated by

%radial velocity
\begin{equation}
	v_{rMax} = \frac{2\pi}{60} RPM BladeLength
	\label{eqn:v_radial_max}
\end{equation}

then using that to find the maximum available doppler through

%maximum available doppler
\begin{equation}
	f_{DopplerMax} = 2\frac{v_{rMax} f_c}{c}
	\label{eqn:fd_max}
\end{equation}

This limitation is shown by varying the elevation angle at the azimuth angle that provides the maximum Doppler shift, which is 180\textdegree \space. The maximum and minimum envelope data is shown in figure \ref{fig:envelope_180deg}

%figure of 180 deg elevation sweep of envelope
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Elevation_angle_envelopes_180deg_Azimuth.eps}
		\caption{Max and Min Envelope Frequencies vs Elevation Angle with Transmitter Azimuth Angle of 180\textdegree}
		\label{fig:envelope_180deg}
	\end{center}
\end{figure}

%figure of comparing actual to estimated
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Elevation_angle_comparason_180deg_Azimuth.eps}
		\caption{Elevation Estimate and Actual Angle with Transmitter Azimuth Angle of 180\textdegree}
		\label{fig:angle_comparason_180deg}
	\end{center}
\end{figure}

Using the estimation method described above, figure \ref{fig:angle_comparason_180deg} shows the elevation angle estimated versus the actual angle. The estimation method is accurate till about 18\textdegree \space or 20\textdegree \space where it becomes noisy. This is due to the inability of the envelope estimation to resolve the correct maximum doppler for that range. By going back to figure (anglerangerelation) we can see that as the transmitter moves farther and farther away the elevation angle is still decreasing but at a much smaller and smaller rate. So the difference between elevation angles closer to zero are more difficult to resolve.

%figure percent error of increasing error and variability
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/results/Elevation_angle_percent_error_180deg_Azimuth.eps}
		\caption{Elevation Angle Percent Error with Transmitter Azimuth Angle of 180\textdegree}
		\label{fig:percent_error_elevation_180deg}
	\end{center}
\end{figure}

Figure \ref{fig:percent_error_elevation_180deg} shows the percent error with respect to the elevation angle and it starts to become unusable around 18\textdegree \space or 20\textdegree \space where the percent error starts to shoot past acceptable ranges.

### 2016-09-29 Simulation.tex
add all but eps files

\chapter{Received Signal Simulations}
%define the signal characteristics and evaluate the properties of the resulting signal over the parameter sweeps

\section{Introduction}
The following simulations performed will define the search space on the effect of rotor blade modulation. Since the software developed allows for full parameterization of the objects within the scene the simulations will focus on a few that effect the different object's positions in 3D space and the resulting received signal. The parameters that will be changed are the position of the receiver, pitch of the rotor blade, and transmitter position. The effect of each parameter will be analyzed to determine what information can be derived for localization.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------

\section{Analysis Techniques}
The data from the .CSV files generated by the raytracing program is loaded into MATLAB scripts to process the data. The technique that is used is the spectrogram function that computes the short time Fourier transform. This allows for computations to be done in the time frequency domain and provide an accurate picture of how the signal is changing with time. The following figure \label{fig:test_spec} shows an example of the computed spectrograms.

%short Fourier transform alg

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram.eps}
		\caption{Example Spectrum for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec}
	\end{center}
\end{figure}

After the computation of the short time Fourier transform the doppler envelope is calculated by performing a threshold on the power, in both the positive and negative doppler, at each time slice. The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values. The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept. For the azimuth angle sweep, which will be shown later in (-), the maximum power is found in each time slice then those values are averaged. Then for each successive angle the same average is taken and averaged with all the others

%equation for power averaging over successive angles

This technique is used because the elevation angle is remaining constant, so the distance with the helicopter platform should be constant as well. When varying the elevation angle the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram_with_envelope.eps}
		\caption{Example Spectrum with Doppler Profile for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
		\label{fig:test_spec_w_doppler_profile}
	\end{center}
\end{figure}

The Doppler envelopes are displayed in figure \ref{fig:test_spec_w_doppler_profile}, the lower in blue and the upper in red. The minimum is calculated from the lower envelope, and the maximum from the upper envelope. Those values are then used to characterize that doppler profile and analyze signal trends as different variables change.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Receiver Position}
%display spectrograms of the rx position and its affect on doppler and pick a value 7m for all subsequent tests
%use reasoning on cleaner signal more signal variation.
The position of the receiver is determined ultimately by its location on the physical aircraft. The position can be anywhere along the length of the body of the helicopter, but for the purpose of the simulation the receiver position will be varied from directly underneath the rotor to just past the tip.

%figure of the receiver position 0 to 9m
\begin{figure}
	\begin{center}
		\includegraphics[width=9cm]{images/simulation/rotor_rx_position.eps}
		\caption{Position of the Receiver in Relation to the Rotor Blades}
		\label{fig:rx_position_image}
	\end{center}
\end{figure}

The rotor blade length from figure \ref{fig:rx_position_image} is 7.5m so the receiver will be varied from 0m to 9m in 1m increments. The resulting signal is analyzed by calculating its doppler envelope. Then the maximum and minimum of that envelope will then be used to determined the overall effect of the position of the receiver.

%figure of maximum doppler vs rx position
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/receiver_position_max_doppler.eps}
		\caption{Max and Min Doppler vs. Receiver Position with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
		\label{fig:rx_position}
	\end{center}
\end{figure}
%azimuth = 135, elevation = 54deg

The figure \ref{fig:rx_position} shows maximum doppler vs the position of the receiver. From this graph the maximum doppler frequency changes significantly as the receiver is moved from directly under neath the rotor to past the tip of the rotor at 9m.The position of the receiver also effects the resulting signal envelope shapes shown in figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.

%figure of spectrogram at 0m -- figure of spectrogram at 7m side by side
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Doppler_Receiver_0m.eps}
		\caption{Doppler Envelope with receiver at 0m}
		\label{fig:rx_position_0m}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Doppler_Receiver_7m.eps}
		\caption{Doppler Envelope with receiver at 7m}
		\label{fig:rx_position_7m}
	\end{center}
\end{figure}

Comparing figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max doppler reflects the information in figure \ref{fig:rx_position} and the overall envelope is afected. The envelope in figure \ref{fig:rx_position_0m} is much noiser than the envelope of figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks. The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}. Therefore the receiver will be offset from the center of rotation by 7m for the subsequent simulations.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Rotor Pitch}
%display spectrograms of rotor pitch from 0 to -15 deg nominal value, then evaluate the effect.
%try to show that pitch does not change the signal significantly
The pitch of the rotor blades determines the amount of lift the rotors create. The pitch range is determined by the shape of the airfoil and the angle at which it will stall and no longer produce lift. For the purpose of the simulations, and the selected airfoil, the pitch range will be from 0\textdegree  \space to 15\textdegree.

%figure of pitched airfoil at 0 and at 15 deg
\begin{figure}
	\begin{center}
		\includegraphics[width=9cm]{images/simulation/pitch.eps}
		\caption{Rotor Pitch}
		\label{fig:blade_pitch}
	\end{center}
\end{figure}

The resulting signal is analyzed by calculating its doppler envelope. Then the maximum and minimum of that envelope will then be used to determined the overall effect of pitching the rotor blade.

%figure of doppler vs pitch
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/pitch_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Rotor Pitch with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
		\label{fig:pitch_15_135deg}
	\end{center}
\end{figure}
%azimuth = 135deg, elevation = 54deg

From figure \ref{fig:pitch_15_135deg} the effect of pitch on the maximum doppler frequency is a linear increase between a pitch from 0 \textdegree \space to 15\textdegree. Due to the linear increase the pitch of the rotor blade can be accounted for when making measurements on subsequent simulation analysis. One issue does arise in when the transmitter is located underneath the helicopter which is shown in figure \ref{fig:pitch_tx0}.

%figure of tx_0 and increasing pitch slope?
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/pitch_0txPos_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Rotor Pitch Transmitter Underneath the Helicopter}
		\label{fig:pitch_tx0}
	\end{center}
\end{figure}
%azimuth undefined, elevation 90deg

As the pitch increases linearly at first then climbs at a much faster rate. This offset when the transmitter is directly underneath is caused by the pitch of the blade reflecting rays into the receiver which would be reflected back at the ground if the pitch was 0\textdegree. If the assumption is that the helicopter is hovering when these measurements take place the pitch of the rotor will be much less than the maximum pitch available. This assumption will adjust the maximum pitch to 15 \textdegree \space which will allow for the linear assumption to be fulfilled even when the transmitter is directly underneath the helicopter.

%figure max doppler vs range of 15 and 7.5 pitch and 0 pitch side by side
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/elevation_angle_with_pitch_max_doppler.eps}
		\caption{Max Envelope Frequencies vs Transmitter Elevation Angle}
		\label{fig:pitch_tx_elevation_angle}
	\end{center}
\end{figure}
%azimuth = 135deg

In figure \ref{fig:pitch_tx_elevation_angle} the max doppler vs elevation angles are initially shifted up in frequency from a pitch of 0 and has changed in slope. This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel. The interesting thing about this plot is that the pitch envelopes actually become closer to the 0\textdegree \space envelope as the elevation angle becomes smaller. Figure \ref{fig:pitch_tx_elevation_angle_difference} shows the difference plotted over elevation angle.

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/elevation_angle_with_pitch_max_doppler_Difference.eps}
		\caption{Frequency Difference vs Transmitter Elevation Angle}
		\label{fig:pitch_tx_elevation_angle_difference}
	\end{center}
\end{figure}

From figure \ref{fig:pitch_tx_elevation_angle_difference} we can see that the difference in frequency changes linearly as the elevation angle decreases, the slope of which is based on the pitch angle. This slope would have to be characterized on the physical craft and can be accounted for due to its predictable nature.

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Transmitter Azimuth Angle} \label{taa}
%display azimuth angle with respect to max doppler readings and describe patterns
The transmitter azimuth angle corresponds to the cardinal direction of the transmitter with respect to the front of the helicopter.

%figure of azimuth angle positions
\begin{figure}
	\begin{center}
		\includegraphics[width=9cm]{images/simulation/azimuth.eps}
		\caption{Transmitter Azimuth Angle Relationship}
		\label{fig:tx_azimuth_rel}
	\end{center}
\end{figure}

Where $\theta_{Az}$ is the azimuth angle. The azimuth angle of the transmitter in the simulation will effect the amount of doppler added to the signal. This is due to the direction of the rotor blade rotation as it approaches both the receiver and the transmitter and how the rays reflect off the blade as it moves. From the model we see the amount of doppler form a sinusoidal pattern as the azimuth angle goes from $0$ to $2\pi$. This is mirrored in the simulation shown in figure \ref{fig:tx_azimuth_angle_200}.

%figure of doppler vs azimuth angle
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_200_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 45\textdegree}
		\label{fig:tx_azimuth_angle_200}
	\end{center}
\end{figure}
%azimuth variable, elevation = 45deg

The graph in figure \ref{fig:tx_azimuth_angle_200} shows both the max and the minimum measured doppler as the azimuth angle completes a full rotation. The doppler frequency follows the azimuth angle in a sinusoidal fashion. The sinusoidal pattern is held as the elevation angle changes shown in figures \ref{fig:tx_azimuth_angle_50} and \ref{fig:tx_azimuth_angle_400}.

%figure of doppler and azimuth angle for different elevation angles.
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_50_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 76\textdegree}
		\label{fig:tx_azimuth_angle_50}
	\end{center}
\end{figure}
%azimuth variable, elevation = 76deg

\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_400_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 26.5\textdegree}
		\label{fig:tx_azimuth_angle_400}
	\end{center}
\end{figure}
%azimuth variable, elevation = 26.5deg

%description
The sinusoidal pattern of min and max doppler frequencies are only present when the receiver is located away from the axis of rotation. This is shown in figure \ref{fig:tx_azimuth_rx0} which is devoid of any sinusoidal pattern and remains constant as the transmitter azimuth angle is changed.

%figure of 0 rx position
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_rx0_max_doppler.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Rx at Axis of Rotation}
		\label{fig:tx_azimuth_rx0}
	\end{center}
\end{figure}

Therefore all future simulations will set the receiver near the tip of the rotor which would simulate the receiver being in the nose of the helicopter.

The effect of azimuth angle on the maximum measured doppler will be characterized in section (-)

%-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
\section{Transmitter Elevation Angle}
%display elevation angle with respect to max doppler readings and describe patterns
The transmitter elevation angle is the angle between the helicopter rotor and the position of the transmitter shown in figure \ref{fig:azimuth_rel}.

%figure of position of elevation angle with respect to rotor
\begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/elevation.eps}
		\caption{Transmitter Elevation Angle}
		\label{fig:azimuth_rel}
	\end{center}
\end{figure}

Where $\theta_{El}$ is the elevation angle.

The smaller elevation angles mean that the transmitter is farther away from the helicopter. The elevation angle in relation to the distance of the transmitter is shown by figure \ref{fig:tx_range_elevation_rel}.

%figure of range vs elevation angle.
 \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/range_elevation_rel.eps}
		\caption{Transmitter Range vs Elevation Angle at an Altitude of 200m}
		\label{fig:tx_range_elevation_rel}
	\end{center}
\end{figure}

The elevation angle of the transmitter in the simulation will effect the amount of doppler added to the signal. This is due to the rays having a vector component in the direction of the travel of the rotor. When the transmitter is directly underneath the rotor and receiver there is no vector component in the direction of rotor travel so the reflected signal is not doppler shifted. From the model we see the amount of doppler increase as the elevation angle decreases. This is mirrored in the simulation shown in figure \ref{fig:tx_elevation_135deg}.

%figure of doppler vs (elevation angle)
 \begin{figure}
	\begin{center}
		\includegraphics[width=10cm]{images/simulation/elevation_angle_max_doppler_135deg.eps}
		\caption{Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth of 135deg}
		\label{fig:tx_elevation_135deg}
	\end{center}
\end{figure}
%azimuth = 135deg, elevation = var

The graph in figure \ref{fig:tx_elevation_135deg} shows the maximum measured doppler as the elevation angle increases.

The effect of elevation angle on the maximum measured doppler will be characterized in section (-).

### 2016-09-29 doxygen/latex/annotated.tex
add all but eps files

\section{Class List}
Here are the classes, structs, unions and interfaces with brief descriptions\+:\begin{DoxyCompactList}
\item\contentsline{section}{\hyperlink{class_blade__surface}{Blade\+\_\+surface} }{\pageref{class_blade__surface}}{}
\item\contentsline{section}{\hyperlink{class_bounding__box}{Bounding\+\_\+box} }{\pageref{class_bounding__box}}{}
\item\contentsline{section}{\hyperlink{class_point3_d}{Point3D} }{\pageref{class_point3_d}}{}
\item\contentsline{section}{\hyperlink{class_ray3_d}{Ray3D} }{\pageref{class_ray3_d}}{}
\item\contentsline{section}{\hyperlink{class_receiver}{Receiver} }{\pageref{class_receiver}}{}
\item\contentsline{section}{\hyperlink{class_rib}{Rib} }{\pageref{class_rib}}{}
\item\contentsline{section}{\hyperlink{class_rotor}{Rotor} }{\pageref{class_rotor}}{}
\item\contentsline{section}{\hyperlink{class_scene}{Scene} }{\pageref{class_scene}}{}
\item\contentsline{section}{\hyperlink{class_sphere}{Sphere} }{\pageref{class_sphere}}{}
\item\contentsline{section}{\hyperlink{class_transmitter}{Transmitter} }{\pageref{class_transmitter}}{}
\item\contentsline{section}{\hyperlink{class_triangle}{Triangle} }{\pageref{class_triangle}}{}
\item\contentsline{section}{\hyperlink{class_vector3_d}{Vector3D} }{\pageref{class_vector3_d}}{}
\end{DoxyCompactList}

### 2016-09-29 doxygen/latex/class_blade__surface.tex
add all but eps files

\hypertarget{class_blade__surface}{}\section{Blade\+\_\+surface Class Reference}
\label{class_blade__surface}\index{Blade\+\_\+surface@{Blade\+\_\+surface}}

Collaboration diagram for Blade\+\_\+surface\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=211pt]{doxygen/latex/class_blade__surface__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_blade__surface_a0c1a5fa3ea94afa451043ce70d3d7c1e}{}\label{class_blade__surface_a0c1a5fa3ea94afa451043ce70d3d7c1e} 
{\bfseries Blade\+\_\+surface} (const int id, const double length, const int Rib\+\_\+count, \hyperlink{class_rib}{Rib} \&origin\+\_\+\+Rib)
\item 
\hypertarget{class_blade__surface_a160959f632ad73eff846aeea81aa84ae}{}\label{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} 
void {\bfseries create\+\_\+surface} ()
\item 
\hypertarget{class_blade__surface_a34d1f584602a5513960b0647a337232b}{}\label{class_blade__surface_a34d1f584602a5513960b0647a337232b} 
void {\bfseries update\+\_\+surface} ()
\item 
\hypertarget{class_blade__surface_a1eddf9a97aa9c2f4f399d03623e9fb6c}{}\label{class_blade__surface_a1eddf9a97aa9c2f4f399d03623e9fb6c} 
void {\bfseries update\+\_\+bounding\+\_\+box} ()
\item 
\hypertarget{class_blade__surface_a8d08aa093ce9eb861d5061303cc35a3b}{}\label{class_blade__surface_a8d08aa093ce9eb861d5061303cc35a3b} 
void {\bfseries rotate\+\_\+surface\+\_\+Z} (double angle)
\item 
\hypertarget{class_blade__surface_a384b9627c130a436d944264fb001d25b}{}\label{class_blade__surface_a384b9627c130a436d944264fb001d25b} 
void {\bfseries pitch\+\_\+surface\+\_\+X} (const double angle)
\item 
\hypertarget{class_blade__surface_a6823c31d12449828939ddc88ddb23705}{}\label{class_blade__surface_a6823c31d12449828939ddc88ddb23705} 
void {\bfseries height\+\_\+surface\+\_\+Z} (const double height)
\item 
\hypertarget{class_blade__surface_a1d4bc10f18e1ee2002a3fa1b5b0c0cb7}{}\label{class_blade__surface_a1d4bc10f18e1ee2002a3fa1b5b0c0cb7} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point)
\item 
\hypertarget{class_blade__surface_a9d55669ccf429e408ff492cfecf52b6b}{}\label{class_blade__surface_a9d55669ccf429e408ff492cfecf52b6b} 
std\+::vector$<$ \hyperlink{class_rib}{Rib} $>$ {\bfseries get\+Ribs} ()
\item 
\hypertarget{class_blade__surface_a91f5bbe72574182ee6ad9e4014bfebbf}{}\label{class_blade__surface_a91f5bbe72574182ee6ad9e4014bfebbf} 
std\+::vector$<$ \hyperlink{class_triangle}{Triangle} $>$ {\bfseries get\+Surface} ()
\item 
\hypertarget{class_blade__surface_ae2f4aa670e4d320d63c77feffb953ae0}{}\label{class_blade__surface_ae2f4aa670e4d320d63c77feffb953ae0} 
std\+::vector$<$ \hyperlink{class_point3_d}{Point3D} $>$ {\bfseries get\+Points} ()
\item 
\hypertarget{class_blade__surface_a72fcd5b6eeb88c4e18da0ad267b27a93}{}\label{class_blade__surface_a72fcd5b6eeb88c4e18da0ad267b27a93} 
\hyperlink{class_bounding__box}{Bounding\+\_\+box} {\bfseries get\+Box} ()
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_blade__surface_afd3c87a82f107470cea4d3c8c1f5ee78}{}\label{class_blade__surface_afd3c87a82f107470cea4d3c8c1f5ee78} 
int {\bfseries id}
\item 
\hypertarget{class_blade__surface_a23f1ef284f842b523cb4b44235c0cdd7}{}\label{class_blade__surface_a23f1ef284f842b523cb4b44235c0cdd7} 
double {\bfseries length}
\item 
\hypertarget{class_blade__surface_ab1e364b4402fa787dea7d3b601e33778}{}\label{class_blade__surface_ab1e364b4402fa787dea7d3b601e33778} 
double {\bfseries delta\+\_\+l}
\item 
\hypertarget{class_blade__surface_a9ff7e20545a1fbb7ad84b00adb35f070}{}\label{class_blade__surface_a9ff7e20545a1fbb7ad84b00adb35f070} 
int {\bfseries Rib\+\_\+count}
\item 
\hypertarget{class_blade__surface_af1982ac4bb6460c4bae24868bd93e8d5}{}\label{class_blade__surface_af1982ac4bb6460c4bae24868bd93e8d5} 
\hyperlink{class_rib}{Rib} {\bfseries origin\+\_\+\+Rib}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Blade\+\_\+surface.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Blade\+\_\+surface.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_bounding__box.tex
add all but eps files

\hypertarget{class_bounding__box}{}\section{Bounding\+\_\+box Class Reference}
\label{class_bounding__box}\index{Bounding\+\_\+box@{Bounding\+\_\+box}}

Collaboration diagram for Bounding\+\_\+box\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=180pt]{doxygen/latex/class_bounding__box__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_bounding__box_adf45c090850ee7b48b59f8e586450ef3}{}\label{class_bounding__box_adf45c090850ee7b48b59f8e586450ef3} 
{\bfseries Bounding\+\_\+box} (std\+::vector$<$ \hyperlink{class_point3_d}{Point3D} $>$ \&points)
\item 
\hypertarget{class_bounding__box_a29a6d043ac2de9fb152f39c1139e42df}{}\label{class_bounding__box_a29a6d043ac2de9fb152f39c1139e42df} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, \hyperlink{class_point3_d}{Point3D} \&hit\+\_\+point) const
\item 
\hypertarget{class_bounding__box_af2a1aa9cee9c82c2dd2df602cca9f42f}{}\label{class_bounding__box_af2a1aa9cee9c82c2dd2df602cca9f42f} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray) const
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_bounding__box_add720cf740129c859bddbbed01727c48}{}\label{class_bounding__box_add720cf740129c859bddbbed01727c48} 
\hyperlink{class_point3_d}{Point3D} {\bfseries min\+\_\+point}
\item 
\hypertarget{class_bounding__box_a1ee058e226dbf771065c67d62cac8c66}{}\label{class_bounding__box_a1ee058e226dbf771065c67d62cac8c66} 
\hyperlink{class_point3_d}{Point3D} {\bfseries max\+\_\+point}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Bounding\+\_\+box.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Bounding\+\_\+box.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_point3_d.tex
add all but eps files

\hypertarget{class_point3_d}{}\section{Point3D Class Reference}
\label{class_point3_d}\index{Point3D@{Point3D}}

Collaboration diagram for Point3D\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=161pt]{doxygen/latex/class_point3_d__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_point3_d_a72799f11be08ba98bb37cfcf2fa0bb1f}{}\label{class_point3_d_a72799f11be08ba98bb37cfcf2fa0bb1f} 
{\bfseries Point3D} (const double x, const double y, const double z)
\item 
\hypertarget{class_point3_d_af963fbdffd449c8fc2d0631992a996e1}{}\label{class_point3_d_af963fbdffd449c8fc2d0631992a996e1} 
{\bfseries Point3D} (const double y, const double z)
\item 
\hypertarget{class_point3_d_a7ac9d9c06fe0497d868537d2f6ad9454}{}\label{class_point3_d_a7ac9d9c06fe0497d868537d2f6ad9454} 
\hyperlink{class_point3_d}{Point3D} {\bfseries operator-\/} () const
\item 
\hypertarget{class_point3_d_a6cb0fe83bc148a42fb2cf6f9aa907242}{}\label{class_point3_d_a6cb0fe83bc148a42fb2cf6f9aa907242} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator-\/} (const \hyperlink{class_point3_d}{Point3D} \&p) const
\item 
\hypertarget{class_point3_d_a2ab1c2f322e1845e94414fab67139667}{}\label{class_point3_d_a2ab1c2f322e1845e94414fab67139667} 
\hyperlink{class_point3_d}{Point3D} {\bfseries operator+} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_point3_d_a376bb34529614f69a1d79b9633b6ab03}{}\label{class_point3_d_a376bb34529614f69a1d79b9633b6ab03} 
\hyperlink{class_point3_d}{Point3D} {\bfseries operator-\/} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_point3_d_a30f07cec680e5e619289ba0c36c00d34}{}\label{class_point3_d_a30f07cec680e5e619289ba0c36c00d34} 
\hyperlink{class_point3_d}{Point3D} {\bfseries operator$\ast$} (const double a) const
\item 
\hypertarget{class_point3_d_a80016919138ae619c4ae603e0c963460}{}\label{class_point3_d_a80016919138ae619c4ae603e0c963460} 
bool {\bfseries operator==} (const \hyperlink{class_point3_d}{Point3D} \&p) const
\item 
\hypertarget{class_point3_d_a3db617345c47ecf25cee2d8bb08712dc}{}\label{class_point3_d_a3db617345c47ecf25cee2d8bb08712dc} 
double {\bfseries distance} (const \hyperlink{class_point3_d}{Point3D} \&p) const
\item 
\hypertarget{class_point3_d_aa2c65a74cd2605f2f46cd7fa88ed537c}{}\label{class_point3_d_aa2c65a74cd2605f2f46cd7fa88ed537c} 
double {\bfseries x} () const
\item 
\hypertarget{class_point3_d_aeeea1fe4bd6b56727b50c569b71f8207}{}\label{class_point3_d_aeeea1fe4bd6b56727b50c569b71f8207} 
double {\bfseries y} () const
\item 
\hypertarget{class_point3_d_ad663c810a730a64d1e000e366fc366ea}{}\label{class_point3_d_ad663c810a730a64d1e000e366fc366ea} 
double {\bfseries z} () const
\item 
\hypertarget{class_point3_d_a02de7d72811aef8bfc6660dd99267682}{}\label{class_point3_d_a02de7d72811aef8bfc6660dd99267682} 
void {\bfseries rotate\+\_\+Z} (const double angle)
\item 
\hypertarget{class_point3_d_aa282f1dc3a75839d0581583f89eeb1ea}{}\label{class_point3_d_aa282f1dc3a75839d0581583f89eeb1ea} 
void {\bfseries rotate\+\_\+X} (const double angle)
\item 
\hypertarget{class_point3_d_af415dc7a082ad664812b02df15902217}{}\label{class_point3_d_af415dc7a082ad664812b02df15902217} 
void {\bfseries translate\+\_\+Z} (const double height)
\end{DoxyCompactItemize}
\subsection*{Friends}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_point3_d_a84c3d7aa704e44e7f6cfbfe0cb6528f7}{}\label{class_point3_d_a84c3d7aa704e44e7f6cfbfe0cb6528f7} 
void {\bfseries swap} (\hyperlink{class_point3_d}{Point3D} \&a, \hyperlink{class_point3_d}{Point3D} \&b)
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Point3d.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Point3d.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_ray3_d.tex
add all but eps files

\hypertarget{class_ray3_d}{}\section{Ray3D Class Reference}
\label{class_ray3_d}\index{Ray3D@{Ray3D}}

Collaboration diagram for Ray3D\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=254pt]{doxygen/latex/class_ray3_d__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_ray3_d_a0cd2092288763fc6c0fd8dccebf11527}{}\label{class_ray3_d_a0cd2092288763fc6c0fd8dccebf11527} 
{\bfseries Ray3D} (const \hyperlink{class_point3_d}{Point3D} \&origin, const \hyperlink{class_vector3_d}{Vector3D} \&direction, const double power=1.\+0, const double frequency=0.\+0, const double distance=0)
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_ray3_d_aa303389d0d8e8569f4bdef420e850717}{}\label{class_ray3_d_aa303389d0d8e8569f4bdef420e850717} 
\hyperlink{class_point3_d}{Point3D} {\bfseries origin}
\item 
\hypertarget{class_ray3_d_a1b9fbe26d23a38f12be002d0e5990fd2}{}\label{class_ray3_d_a1b9fbe26d23a38f12be002d0e5990fd2} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries direction}
\item 
\hypertarget{class_ray3_d_adbe652ae6043219a7a6d22c3e6a454db}{}\label{class_ray3_d_adbe652ae6043219a7a6d22c3e6a454db} 
double {\bfseries power}
\item 
\hypertarget{class_ray3_d_a5be97a26ac4f733fee0b9a10ca78197a}{}\label{class_ray3_d_a5be97a26ac4f733fee0b9a10ca78197a} 
double {\bfseries frequency}
\item 
\hypertarget{class_ray3_d_a1287339cd3f7358590b2fb65dbb88505}{}\label{class_ray3_d_a1287339cd3f7358590b2fb65dbb88505} 
double {\bfseries distance}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Ray3d.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Ray3d.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_receiver.tex
add all but eps files

\hypertarget{class_receiver}{}\section{Receiver Class Reference}
\label{class_receiver}\index{Receiver@{Receiver}}

Collaboration diagram for Receiver\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=195pt]{doxygen/latex/class_receiver__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_receiver_a94a089e687b5320f02b3000304ffd08c}{}\label{class_receiver_a94a089e687b5320f02b3000304ffd08c} 
{\bfseries Receiver} (const int id, const double Bandwidth, const double center\+\_\+freq, const \hyperlink{class_point3_d}{Point3D} \&center, const double boundary\+\_\+radius, const std\+::string \&savefile\+\_\+name, const std\+::string \&dopplerfile\+\_\+name)
\item 
\hypertarget{class_receiver_a6d0f579d480c7303d8138981e546ff01}{}\label{class_receiver_a6d0f579d480c7303d8138981e546ff01} 
\hyperlink{class_sphere}{Sphere} {\bfseries get\+\_\+\+Boundary} ()
\item 
\hypertarget{class_receiver_a6e97969b694ba385a495bf64f9adc16a}{}\label{class_receiver_a6e97969b694ba385a495bf64f9adc16a} 
double {\bfseries get\+\_\+sampling\+\_\+rate} ()
\item 
\hypertarget{class_receiver_a146b5c800df5f2e17eb89faa16a3929a}{}\label{class_receiver_a146b5c800df5f2e17eb89faa16a3929a} 
std\+::vector$<$ \hyperlink{class_ray3_d}{Ray3D} $>$ {\bfseries get\+\_\+frame\+\_\+data} ()
\item 
\hypertarget{class_receiver_aaa3ac7cecd33cba5a382fb0db441082e}{}\label{class_receiver_aaa3ac7cecd33cba5a382fb0db441082e} 
void {\bfseries save\+\_\+ray\+\_\+to\+Frame} (\hyperlink{class_ray3_d}{Ray3D} \&ray)
\item 
\hypertarget{class_receiver_a72ce8129ebd0720a810959eb0a47dfc8}{}\label{class_receiver_a72ce8129ebd0720a810959eb0a47dfc8} 
void {\bfseries save\+\_\+to\+\_\+file} ()
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_receiver_aaadfb4436bd66669d03811c846985843}{}\label{class_receiver_aaadfb4436bd66669d03811c846985843} 
int {\bfseries id}
\item 
\hypertarget{class_receiver_a19225a5d1c7c5f4cdaa36b99a1184d26}{}\label{class_receiver_a19225a5d1c7c5f4cdaa36b99a1184d26} 
double {\bfseries Bandwidth}
\item 
\hypertarget{class_receiver_a33f4396a9edddf6fe298108ffa12da58}{}\label{class_receiver_a33f4396a9edddf6fe298108ffa12da58} 
double {\bfseries center\+\_\+freq}
\item 
\hypertarget{class_receiver_a7cf7efbe8c86d8f585e744cbba86c267}{}\label{class_receiver_a7cf7efbe8c86d8f585e744cbba86c267} 
double {\bfseries Resolution}
\item 
\hypertarget{class_receiver_ad9a009e1e386791e5c3bd7211d83a3f9}{}\label{class_receiver_ad9a009e1e386791e5c3bd7211d83a3f9} 
double {\bfseries boundary\+\_\+radius}
\item 
\hypertarget{class_receiver_a4432a9eafa52a2483918d2d3119cb597}{}\label{class_receiver_a4432a9eafa52a2483918d2d3119cb597} 
\hyperlink{class_point3_d}{Point3D} {\bfseries center}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Receiver.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Receiver.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_rib.tex
add all but eps files

\hypertarget{class_rib}{}\section{Rib Class Reference}
\label{class_rib}\index{Rib@{Rib}}

Collaboration diagram for Rib\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=168pt]{doxygen/latex/class_rib__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_rib_a417cde052770f55f3344d785aef969ef}{}\label{class_rib_a417cde052770f55f3344d785aef969ef} 
{\bfseries Rib} (int id, \hyperlink{class_rib}{Rib} \&x, const double delta\+\_\+l)
\item 
\hypertarget{class_rib_aaaed7a2c960a33e5ac0c510ea7d8881c}{}\label{class_rib_aaaed7a2c960a33e5ac0c510ea7d8881c} 
{\bfseries Rib} (int id, const std\+::string \&filename)
\item 
\hypertarget{class_rib_ae4ea708286531b624f587f22b9416a36}{}\label{class_rib_ae4ea708286531b624f587f22b9416a36} 
std\+::vector$<$ \hyperlink{class_point3_d}{Point3D} $>$ {\bfseries get\+Rib\+Points} ()
\item 
\hypertarget{class_rib_ab6715214f4a43ed51b46a8f42d6f198b}{}\label{class_rib_ab6715214f4a43ed51b46a8f42d6f198b} 
void {\bfseries pitch} (double angle)
\item 
\hypertarget{class_rib_aafef170600416b0e6a86ccb4e8bd4e32}{}\label{class_rib_aafef170600416b0e6a86ccb4e8bd4e32} 
void {\bfseries rotate} (double angle)
\item 
\hypertarget{class_rib_a08859793a4800c7d160d0b494ad39af7}{}\label{class_rib_a08859793a4800c7d160d0b494ad39af7} 
void {\bfseries height} (const double height)
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_rib_ac88341591298af4d11837a09b47917d5}{}\label{class_rib_ac88341591298af4d11837a09b47917d5} 
int {\bfseries id}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Rib.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Rib.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_rotor.tex
add all but eps files

\hypertarget{class_rotor}{}\section{Rotor Class Reference}
\label{class_rotor}\index{Rotor@{Rotor}}

Collaboration diagram for Rotor\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=196pt]{doxygen/latex/class_rotor__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_rotor_af922b65832291cafdb53c52a545ac136}{}\label{class_rotor_af922b65832291cafdb53c52a545ac136} 
double {\bfseries get\+\_\+\+R\+PM} ()
\item 
\hypertarget{class_rotor_a25eef55d0719b86a255d3aa09f7a2688}{}\label{class_rotor_a25eef55d0719b86a255d3aa09f7a2688} 
int {\bfseries get\+\_\+num\+\_\+blades} ()
\item 
\hypertarget{class_rotor_ad0c276d01564fbdda8ca63c7eff18df6}{}\label{class_rotor_ad0c276d01564fbdda8ca63c7eff18df6} 
double {\bfseries get\+\_\+height} ()
\item 
\hypertarget{class_rotor_a53d18f1d59a1c2b71cdb8c9cab0acd4c}{}\label{class_rotor_a53d18f1d59a1c2b71cdb8c9cab0acd4c} 
double {\bfseries get\+\_\+constant\+\_\+pitch} ()
\item 
\hypertarget{class_rotor_af384431ad8eba046b8541ac5d1a3f9f9}{}\label{class_rotor_af384431ad8eba046b8541ac5d1a3f9f9} 
double {\bfseries get\+\_\+\+Rib\+\_\+count} ()
\item 
\hypertarget{class_rotor_a43485a289837aab864e28dc00109fdf6}{}\label{class_rotor_a43485a289837aab864e28dc00109fdf6} 
double {\bfseries get\+\_\+blade\+\_\+length} ()
\item 
\hypertarget{class_rotor_a31c1b1a9674d87d0b612db4989a4ae16}{}\label{class_rotor_a31c1b1a9674d87d0b612db4989a4ae16} 
std\+::vector$<$ \hyperlink{class_blade__surface}{Blade\+\_\+surface} $>$ {\bfseries get\+\_\+\+Blades} ()
\item 
\hypertarget{class_rotor_ac73f8ab43793bc45b978c6ef14239a4c}{}\label{class_rotor_ac73f8ab43793bc45b978c6ef14239a4c} 
void {\bfseries rotate} (const double angle)
\item 
\hypertarget{class_rotor_ab1ecb2c8efc6e125db1fe9121c6c47b9}{}\label{class_rotor_ab1ecb2c8efc6e125db1fe9121c6c47b9} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point)
\item 
\hypertarget{class_rotor_ad525c69ea4ba137f953675839befcaa6}{}\label{class_rotor_ad525c69ea4ba137f953675839befcaa6} 
{\bfseries Rotor} (const int id, const int num\+\_\+blades, const double R\+PM, const double height, const double constant\+\_\+pitch, const double blade\+\_\+length, const int Rib\+\_\+count)
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_rotor_abcb7f6ed3121a0734eef3763d4d20172}{}\label{class_rotor_abcb7f6ed3121a0734eef3763d4d20172} 
int {\bfseries id}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Rotor.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Rotor.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_scene.tex
add all but eps files

\hypertarget{class_scene}{}\section{Scene Class Reference}
\label{class_scene}\index{Scene@{Scene}}

Collaboration diagram for Scene\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=193pt]{doxygen/latex/class_scene__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_scene_a39f55da2de994a41500a2c0a3bbc207d}{}\label{class_scene_a39f55da2de994a41500a2c0a3bbc207d} 
{\bfseries Scene} (double rx\+\_\+x, double rx\+\_\+y, double rx\+\_\+z, double Bandwidth, double rx\+\_\+fc, double tx\+\_\+x, double tx\+\_\+y, double tx\+\_\+fc, double tx\+\_\+power, int num\+\_\+blades, double R\+PM, double altitude, double pitch, double blade\+\_\+length, int num\+\_\+ribs, const std\+::string \&filename)
\item 
\hypertarget{class_scene_a59d78e42eebf29106e413275abacf983}{}\label{class_scene_a59d78e42eebf29106e413275abacf983} 
\hyperlink{class_rotor}{Rotor} {\bfseries get\+\_\+rotor} ()
\item 
\hypertarget{class_scene_aeca85b3d6824c3509c94991136fe6a1b}{}\label{class_scene_aeca85b3d6824c3509c94991136fe6a1b} 
\hyperlink{class_transmitter}{Transmitter} {\bfseries get\+\_\+transmitter} ()
\item 
\hypertarget{class_scene_aea609d389de6e5c483d3e7f19a3aff0a}{}\label{class_scene_aea609d389de6e5c483d3e7f19a3aff0a} 
\hyperlink{class_receiver}{Receiver} {\bfseries get\+\_\+receiver} ()
\item 
\hypertarget{class_scene_a2d3012d31a139a597d50f5b84fbec51d}{}\label{class_scene_a2d3012d31a139a597d50f5b84fbec51d} 
void {\bfseries trace\+\_\+scene} (int num\+\_\+rays)
\item 
\hypertarget{class_scene_a26979e16c27d21bdd615c24c1c11902c}{}\label{class_scene_a26979e16c27d21bdd615c24c1c11902c} 
void {\bfseries trace\+\_\+vect} (\hyperlink{class_ray3_d}{Ray3D} \&test\+\_\+ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point)
\item 
\hypertarget{class_scene_a9af282cee68bb4748bd15568bda0ecfb}{}\label{class_scene_a9af282cee68bb4748bd15568bda0ecfb} 
void {\bfseries update} (double angle)
\item 
\hypertarget{class_scene_a76fa370d0c210100d4cf8799474faa8d}{}\label{class_scene_a76fa370d0c210100d4cf8799474faa8d} 
double {\bfseries get\+Distance\+Power} (const double frequency, const double power, const double distance) const
\item 
double \hyperlink{class_scene_a969abe0e6022d73ff082d380c59d83f5}{get\+Doppler} (\hyperlink{class_ray3_d}{Ray3D} \&test\+\_\+ray, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point, double R\+PM) const
\end{DoxyCompactItemize}

\subsection{Member Function Documentation}
\hypertarget{class_scene_a969abe0e6022d73ff082d380c59d83f5}{}\label{class_scene_a969abe0e6022d73ff082d380c59d83f5} 
\index{Scene@{Scene}!get\+Doppler@{get\+Doppler}}
\index{get\+Doppler@{get\+Doppler}!Scene@{Scene}}
\subsubsection{\texorpdfstring{get\+Doppler()}{getDoppler()}}
{\footnotesize\ttfamily double Scene\+::get\+Doppler (\begin{DoxyParamCaption}\item[{\hyperlink{class_ray3_d}{Ray3D} \&}]{test\+\_\+ray,  }\item[{\hyperlink{class_vector3_d}{Vector3D} \&}]{hit\+Normal,  }\item[{\hyperlink{class_point3_d}{Point3D} \&}]{hit\+Point,  }\item[{double}]{R\+PM }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}

!!!! doppler does not get affected by the normal, need to check this. not sure if this is correct.

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Scene.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Scene.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_sphere.tex
add all but eps files

\hypertarget{class_sphere}{}\section{Sphere Class Reference}
\label{class_sphere}\index{Sphere@{Sphere}}

Collaboration diagram for Sphere\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=161pt]{doxygen/latex/class_sphere__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_sphere_a7b5d0be5fd60ba94573e3941cf4eb094}{}\label{class_sphere_a7b5d0be5fd60ba94573e3941cf4eb094} 
{\bfseries Sphere} (const double radius, const \hyperlink{class_point3_d}{Point3D} \&center)
\item 
\hypertarget{class_sphere_a5da44ddc57c5a68a1092b0df86dc18cd}{}\label{class_sphere_a5da44ddc57c5a68a1092b0df86dc18cd} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point) const
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_sphere_a45d6c6c870fac7c2a885ad2e226334ad}{}\label{class_sphere_a45d6c6c870fac7c2a885ad2e226334ad} 
double {\bfseries radius}
\item 
\hypertarget{class_sphere_a774cb90ed1b46592e63a112338f1cc58}{}\label{class_sphere_a774cb90ed1b46592e63a112338f1cc58} 
\hyperlink{class_point3_d}{Point3D} {\bfseries center}
\item 
\hypertarget{class_sphere_a50d3abf7b35058bae9bcbba998a82943}{}\label{class_sphere_a50d3abf7b35058bae9bcbba998a82943} 
int {\bfseries num\+\_\+points}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Sphere.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Sphere.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_transmitter.tex
add all but eps files

\hypertarget{class_transmitter}{}\section{Transmitter Class Reference}
\label{class_transmitter}\index{Transmitter@{Transmitter}}

Collaboration diagram for Transmitter\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=177pt]{doxygen/latex/class_transmitter__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_transmitter_a91c51bc1d7c42db81fb390753de5c0ea}{}\label{class_transmitter_a91c51bc1d7c42db81fb390753de5c0ea} 
{\bfseries Transmitter} (const int id, const double frequency, const double power, const \hyperlink{class_point3_d}{Point3D} \&center, const double l)
\item 
\hypertarget{class_transmitter_aa26f745526cba27666812ca7c05b9df7}{}\label{class_transmitter_aa26f745526cba27666812ca7c05b9df7} 
void {\bfseries set\+Power} (const double power)
\item 
\hypertarget{class_transmitter_a72eb7b0c29d6d5e3429f9920dcdf86c9}{}\label{class_transmitter_a72eb7b0c29d6d5e3429f9920dcdf86c9} 
double {\bfseries get\+Power} () const
\item 
\hypertarget{class_transmitter_a8a2727ad1e4b48ec9f64c0285bb5bd04}{}\label{class_transmitter_a8a2727ad1e4b48ec9f64c0285bb5bd04} 
\hyperlink{class_ray3_d}{Ray3D} {\bfseries make\+Ray} ()
\item 
\hypertarget{class_transmitter_a7c51cee738e95fb6f2af955986873b7c}{}\label{class_transmitter_a7c51cee738e95fb6f2af955986873b7c} 
\hyperlink{class_ray3_d}{Ray3D} {\bfseries make\+Ray\+\_\+disk} (const double height)
\item 
\hypertarget{class_transmitter_a5c6bdf0d0dd931f9f4282a7d585f2320}{}\label{class_transmitter_a5c6bdf0d0dd931f9f4282a7d585f2320} 
\hyperlink{class_ray3_d}{Ray3D} {\bfseries make\+Ray} (const \hyperlink{class_vector3_d}{Vector3D} \&ray\+Direction)
\end{DoxyCompactItemize}
\subsection*{Public Attributes}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_transmitter_a3e57cbedcf7ff80c3506c47d43119f5d}{}\label{class_transmitter_a3e57cbedcf7ff80c3506c47d43119f5d} 
int {\bfseries id}
\item 
\hypertarget{class_transmitter_ade036fee92a7f2aad8ecf206f89b8c34}{}\label{class_transmitter_ade036fee92a7f2aad8ecf206f89b8c34} 
double {\bfseries frequency}
\item 
\hypertarget{class_transmitter_a61c6aa4371c98b49d2d9277fd4447f34}{}\label{class_transmitter_a61c6aa4371c98b49d2d9277fd4447f34} 
\hyperlink{class_point3_d}{Point3D} {\bfseries center}
\item 
\hypertarget{class_transmitter_ac339f9fd3011afdbdc729b99b371e617}{}\label{class_transmitter_ac339f9fd3011afdbdc729b99b371e617} 
double {\bfseries power}
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Transmitter.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Transmitter.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_triangle.tex
add all but eps files

\hypertarget{class_triangle}{}\section{Triangle Class Reference}
\label{class_triangle}\index{Triangle@{Triangle}}

Collaboration diagram for Triangle\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=175pt]{doxygen/latex/class_triangle__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_triangle_a995e961620da6b595053ef5560999244}{}\label{class_triangle_a995e961620da6b595053ef5560999244} 
{\bfseries Triangle} (\hyperlink{class_point3_d}{Point3D} \&v0, \hyperlink{class_point3_d}{Point3D} \&v1, \hyperlink{class_point3_d}{Point3D} \&v2)
\item 
\hypertarget{class_triangle_ab09716ce6c0928ce11fe34091c19a1c4}{}\label{class_triangle_ab09716ce6c0928ce11fe34091c19a1c4} 
bool {\bfseries hit} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point) const
\item 
\hypertarget{class_triangle_a7b93ca1524b80830bf8ea07d660ace6a}{}\label{class_triangle_a7b93ca1524b80830bf8ea07d660ace6a} 
bool {\bfseries hit\+No\+Cull} (const \hyperlink{class_ray3_d}{Ray3D} \&ray, double \&hit\+Distance, \hyperlink{class_vector3_d}{Vector3D} \&hit\+Normal, \hyperlink{class_point3_d}{Point3D} \&hit\+Point) const
\item 
\hypertarget{class_triangle_aeeced29a75e5c27db3457804debbb936}{}\label{class_triangle_aeeced29a75e5c27db3457804debbb936} 
bool {\bfseries operator==} (\hyperlink{class_triangle}{Triangle} \&Tri)
\item 
\hypertarget{class_triangle_a7dbe3b94aae0c1966801d50190ab2c25}{}\label{class_triangle_a7dbe3b94aae0c1966801d50190ab2c25} 
\hyperlink{class_point3_d}{Point3D} {\bfseries get\+Vertex0} ()
\item 
\hypertarget{class_triangle_a88c0bdcbda9d290e7ea876714b634b83}{}\label{class_triangle_a88c0bdcbda9d290e7ea876714b634b83} 
\hyperlink{class_point3_d}{Point3D} {\bfseries get\+Vertex1} ()
\item 
\hypertarget{class_triangle_aa29a363ca196b8352c749174cfd0ebd9}{}\label{class_triangle_aa29a363ca196b8352c749174cfd0ebd9} 
\hyperlink{class_point3_d}{Point3D} {\bfseries get\+Vertex2} ()
\item 
\hypertarget{class_triangle_a30e9a577df2eb923fd8c869fc1958cd1}{}\label{class_triangle_a30e9a577df2eb923fd8c869fc1958cd1} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries get\+Normal} () const
\item 
\hypertarget{class_triangle_a557fd01902542dca2bccb3de38aa1534}{}\label{class_triangle_a557fd01902542dca2bccb3de38aa1534} 
void {\bfseries set\+Normal} (const \hyperlink{class_vector3_d}{Vector3D} \&normal)
\item 
\hypertarget{class_triangle_a1fe02e3810a30dca5e6ddf646f7f31a5}{}\label{class_triangle_a1fe02e3810a30dca5e6ddf646f7f31a5} 
void {\bfseries flip\+Normal} ()
\item 
\hypertarget{class_triangle_a8e187af2dd348e5c51a657ca066221ac}{}\label{class_triangle_a8e187af2dd348e5c51a657ca066221ac} 
\hyperlink{class_point3_d}{Point3D} {\bfseries centroid} () const
\item 
\hypertarget{class_triangle_a0e10ae200b1a7698a800ddfa06d8d00d}{}\label{class_triangle_a0e10ae200b1a7698a800ddfa06d8d00d} 
\hyperlink{class_point3_d}{Point3D} {\bfseries centroid\+XY} () const
\item 
\hypertarget{class_triangle_a0674ff79061f6413e6aa721e1ac5dd06}{}\label{class_triangle_a0674ff79061f6413e6aa721e1ac5dd06} 
void {\bfseries update\+Normal} ()
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Triangle.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Triangle.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/latex/class_vector3_d.tex
add all but eps files

\hypertarget{class_vector3_d}{}\section{Vector3D Class Reference}
\label{class_vector3_d}\index{Vector3D@{Vector3D}}

Collaboration diagram for Vector3D\+:
\nopagebreak
\begin{figure}[H]
\begin{center}
\leavevmode
\includegraphics[width=155pt]{doxygen/latex/class_vector3_d__coll__graph}
\end{center}
\end{figure}
\subsection*{Public Member Functions}
\begin{DoxyCompactItemize}
\item 
\hypertarget{class_vector3_d_a9c58f21ac5a280f62067d7f26466ba47}{}\label{class_vector3_d_a9c58f21ac5a280f62067d7f26466ba47} 
{\bfseries Vector3D} (const double x, const double y, const double z)
\item 
\hypertarget{class_vector3_d_a5fc1291699c792e6acd5ea453c47f3f4}{}\label{class_vector3_d_a5fc1291699c792e6acd5ea453c47f3f4} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator-\/} (void) const
\item 
\hypertarget{class_vector3_d_afa1d5717e088826b6dcc0cb35ec836f7}{}\label{class_vector3_d_afa1d5717e088826b6dcc0cb35ec836f7} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator$\ast$} (const double a) const
\item 
\hypertarget{class_vector3_d_a86a2dec32df2740e92e06b651d693c95}{}\label{class_vector3_d_a86a2dec32df2740e92e06b651d693c95} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator/} (const double a) const
\item 
\hypertarget{class_vector3_d_af75a42c25ca6e999f3e7a83d4de105c6}{}\label{class_vector3_d_af75a42c25ca6e999f3e7a83d4de105c6} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator+} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_vector3_d_acd7927ced75a36b459200a791e51acad}{}\label{class_vector3_d_acd7927ced75a36b459200a791e51acad} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator-\/} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_vector3_d_a307962a6472b58ac85af69ad74c4fd6f}{}\label{class_vector3_d_a307962a6472b58ac85af69ad74c4fd6f} 
double {\bfseries operator$\ast$} (const \hyperlink{class_vector3_d}{Vector3D} \&b) const
\item 
\hypertarget{class_vector3_d_ac6d8d994b5c80eaaed1f033fd7baa627}{}\label{class_vector3_d_ac6d8d994b5c80eaaed1f033fd7baa627} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries operator$^\wedge$} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_vector3_d_ac86d9a556616f4c51fecbaf7d8658ce8}{}\label{class_vector3_d_ac86d9a556616f4c51fecbaf7d8658ce8} 
double {\bfseries x} () const
\item 
\hypertarget{class_vector3_d_a7146d35db2c1bf7606c8290282a423ec}{}\label{class_vector3_d_a7146d35db2c1bf7606c8290282a423ec} 
double {\bfseries y} () const
\item 
\hypertarget{class_vector3_d_af4ae427e82a23af845f804106daed509}{}\label{class_vector3_d_af4ae427e82a23af845f804106daed509} 
double {\bfseries z} () const
\item 
\hypertarget{class_vector3_d_af396bfa140d140d818a97100f7d6a532}{}\label{class_vector3_d_af396bfa140d140d818a97100f7d6a532} 
double {\bfseries dot\+Product} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_vector3_d_a15b417a5abd07b8a7403bdb0ac5f95ec}{}\label{class_vector3_d_a15b417a5abd07b8a7403bdb0ac5f95ec} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries cross\+Product} (const \hyperlink{class_vector3_d}{Vector3D} \&v) const
\item 
\hypertarget{class_vector3_d_a4ddb90e85e10f0f32475725cb966a5ce}{}\label{class_vector3_d_a4ddb90e85e10f0f32475725cb966a5ce} 
double {\bfseries length} () const
\item 
\hypertarget{class_vector3_d_aac87aef508e65eb8ada23346b5e552c3}{}\label{class_vector3_d_aac87aef508e65eb8ada23346b5e552c3} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries normalized} () const
\item 
\hypertarget{class_vector3_d_a1698a0e33c975b78f0076b51331e6e94}{}\label{class_vector3_d_a1698a0e33c975b78f0076b51331e6e94} 
\hyperlink{class_vector3_d}{Vector3D} {\bfseries rotated\+AboutZ} (const double angle) const
\item 
\hypertarget{class_vector3_d_a5df051b736bdb50b63995442b0816938}{}\label{class_vector3_d_a5df051b736bdb50b63995442b0816938} 
bool {\bfseries is\+Normal} () const
\end{DoxyCompactItemize}

The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}
\item 
Raytracer3\+D/\+Raytracer3\+D/Vector3d.\+hpp\item 
Raytracer3\+D/\+Raytracer3\+D/Vector3d.\+cpp\end{DoxyCompactItemize}

### 2016-09-29 doxygen/html/search/all_1.js

@@ -1,0 +1,4 @@
+var searchData=
+[
+  ['getdoppler',['getDoppler',['../class_scene.html#a969abe0e6022d73ff082d380c59d83f5',1,'Scene']]]
+];

### 2016-09-29 doxygen/html/search/all_3.js

@@ -1,0 +1,7 @@
+var searchData=
+[
+  ['ray3d',['Ray3D',['../class_ray3_d.html',1,'']]],
+  ['receiver',['Receiver',['../class_receiver.html',1,'']]],
+  ['rib',['Rib',['../class_rib.html',1,'']]],
+  ['rotor',['Rotor',['../class_rotor.html',1,'']]]
+];

### 2016-09-29 doxygen/html/search/classes_0.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['blade_5fsurface',['Blade_surface',['../class_blade__surface.html',1,'']]],
+  ['bounding_5fbox',['Bounding_box',['../class_bounding__box.html',1,'']]]
+];

### 2016-09-29 doxygen/html/search/classes_4.js

@@ -1,0 +1,5 @@
+var searchData=
+[
+  ['transmitter',['Transmitter',['../class_transmitter.html',1,'']]],
+  ['triangle',['Triangle',['../class_triangle.html',1,'']]]
+];

### 2016-09-29 doxygen/html/search/searchdata.js

@@ -1,0 +1,21 @@
+var indexSectionsWithContent =
+{
+  0: "bgprstv",
+  1: "bprstv",
+  2: "g"
+};
+
+var indexSectionNames =
+{
+  0: "all",
+  1: "classes",
+  2: "functions"
+};
+
+var indexSectionLabels =
+{
+  0: "All",
+  1: "Classes",
+  2: "Functions"
+};
+

### 2016-09-29 Thesis MATLAB Scripts/Envelope.m
add matlab files

@@ -1,0 +1,62 @@
+%envelope calculation
+clear;
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/test_locationdatainfile_4.csv');
+rpm = 250;
+
+B = horzcat(samples,samples)';
+
+% altitude = samples(1);
+% tx_x = samples(2);
+% tx_y = samples(3);
+% r = samples(4);
+% elevation = samples(5);
+% azimuth = samples(6);
+
+location = samples(1:6);
+
+samples = samples(7:end);
+
+figure;
+plot(real(samples))
+
+fs = 4000;%program
+fs_real = 1/((1/(rpm/60))/length(samples));
+SNR = 50;
+
+[s,f,t,p] = spectrogram(samples,5000,500,5000,fs_real,'reassign','MinThreshold',-SNR,'yaxis','centered');
+log_power = 10*log10(p);
+[q,nd] = max(10*log10(p));
+
+lower_envelope = zeros(length(t),1);
+upper_envelope = zeros(length(t),1);
+
+for i = 1:length(t)
+    for j = 1:2500
+        if log_power(j,i) > -70
+            lower_envelope(i) = f(j);
+            break;
+        end  
+    end
+    for j = 2501:5000
+        if (log_power(7501-j,i) > -70) && (log_power(7501-j,i) ~= -inf)
+            upper_envelope(i) = f(7501-j);
+            break;
+        end  
+    end
+end
+
+angle_b1 = 0:(2*pi)/length(t):2*pi;
+angle_b2 = pi:(2*pi)/length(t):3*pi;
+z = zeros(1,length(t));
+
+figure;
+hold on
+plot3(t*1000,smooth(lower_envelope/1e6,.02),z,'b','linewidth',4)
+plot3(t*1000,smooth(upper_envelope/1e6,.02),z,'r','linewidth',4)
+legend('Lower Envelope','Upper Envelope');
+spectrogram(samples,5000,500,5000,fs_real,'yaxis','centered')
+hold off
+ylabel('Doppler Frequency (kHz)');
+colormap(jet);
+colorbar
+view(2)

### 2016-09-29 Thesis MATLAB Scripts/elevationEstimation_on_data_with_metadata.m

@@ -1,0 +1,115 @@
+%test alg for elevation angle only sweep
+clear;
+
+%--------------------------------------------------------------------------
+%Load Data
+%--------------------------------------------------------------------------
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/*.csv');
+num_files = length(files);
+data = zeros(num_files,959006); %479000;
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/',files(i).name)));
+end
+
+%--------------------------------------------------------------------------
+%Known Constants
+%--------------------------------------------------------------------------
+fs = 4000;
+RPM = 250;
+fc = 1e9;
+c = 3e8;
+
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%--------------------------------------------------------------------------
+%Find Doppler Envelopes
+%--------------------------------------------------------------------------
+
+%sort data by radius r
+data = sortrows(data,4);
+
+location_data = data(:,1:6);
+signal_data = data(:,7:end);
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    
+    [s,f,t,p] = spectrogram(signal_data(i,:),5000,500,5000,fs,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    ave_q(i) = mean(q);
+    
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q(i)) && (log_power(7501-j,slice) ~= -inf)
[…]

### 2016-09-29 Thesis MATLAB Scripts/max_doppler_0deg_rx_offset.m

@@ -1,0 +1,32 @@
+%max doppler 0deg offset rx
+%looks great :)
+clear;
+RPM = 250;%changed
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+
+%max doppler for reflection radius
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%Rx position (might not be needed)
+Rx_z = 2;
+Rx_y = 7;
+Rx_x = 0;
+
+Tx_radius = 0:1:450;
+elevation_angle = atan(Altitude./(Tx_radius));
+
+doppler_plus = ones(1,length(Tx_radius));
+doppler_minus = -max_fd*cos(elevation_angle);
+
+hold on
+plot(360*elevation_angle/(2*pi),doppler_plus)
+plot(360*elevation_angle/(2*pi),doppler_minus)
+hold off
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+title('Doppler Frequency vs. Elevation angle for 0deg Transmitter Azimuth');
+

### 2016-09-29 Thesis MATLAB Scripts/max_doppler_180deg_rx_offset.m

@@ -1,0 +1,31 @@
+%max doppler 180deg offset rx
+%looks great :)
+clear;
+RPM = 250;%changed
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+
+%max doppler for reflection radius
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%Rx position (might not be needed)
+Rx_z = 2;
+Rx_y = 7;
+Rx_x = 0;
+
+Tx_radius = 0:1:450;
+elevation_angle = atan(Altitude./(Tx_radius));
+
+doppler_plus = -ones(1,length(Tx_radius));
+doppler_minus = max_fd*cos(elevation_angle);
+
+hold on
+plot(360*elevation_angle/(2*pi),doppler_plus)
+plot(360*elevation_angle/(2*pi),doppler_minus)
+hold off
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+title('Doppler Frequency vs. Elevation angle for 180deg Transmitter Azimuth');

### 2016-09-29 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -1,0 +1,30 @@
+%max doppler 270deg offset rx
+%looks great :)
+clear;
+RPM = 250;%changed
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+
+%max doppler for reflection radius
+Reflection_radius = 5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%Rx position (might not be needed)
+Rx_z = 2;
+Rx_y = 7;
+Rx_x = 0;
+
+Tx_radius = 0:1:450;
+elevation_angle = atan(Altitude./(Tx_radius + Reflection_radius));
+doppler_plus = max_fd*cos(elevation_angle);
+doppler_minus = -max_fd*cos(elevation_angle);
+hold on
+plot(360*elevation_angle/(2*pi),doppler_plus)
+plot(360*elevation_angle/(2*pi),doppler_minus)
+hold off
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
+

### 2016-09-29 Thesis MATLAB Scripts/max_doppler_90deg_rx_offset.m

@@ -1,0 +1,36 @@
+%max doppler 90deg offset rx
+%this does not show exactly what happens in the simulation because of the
+%offset doppler.....
+clear;
+RPM = 250;%changed
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+
+%max doppler for reflection radius
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%Rx position (might not be needed)
+Rx_z = 2;
+Rx_y = 7;
+Rx_x = 0;
+
+blade_length = 7.5;
+max_elevation_angle = atan(Rx_z/(blade_length - Rx_y));
+
+max_doppler_minus = -max_fd*cos(max_elevation_angle);
+max_doppler_plus = max_fd*cos(max_elevation_angle);
+
+tip = 0:0.01:.5;
+elevation_angle = atan(Rx_z./tip);
+hold on
+plot(360*elevation_angle/(2*pi),max_fd*cos(elevation_angle))
+plot(360*elevation_angle/(2*pi),-max_fd*cos(elevation_angle))
+hold off
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+title('Doppler Frequency vs. Elevation angle for 90deg Transmitter Azimuth');
+
+

### 2016-09-29 Thesis MATLAB Scripts/max_doppler_theory.m

@@ -1,0 +1,46 @@
+clear;
+RPM = 250;%changed
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+
+%max doppler for reflection radius
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c; % re-radiated frequency......
+
+%Rx position (might not be needed)
+Rx_z = 2;
+Rx_y = 7;
+Rx_x = 0;
+
+%Tx position in radius and angle
+Rotor_angle = 0:(2*pi)/100:2*pi;
+Tx_radius = 0:100/4:100;
+
+
+data = zeros(5,101);
+
+for r = Tx_radius
+    i = 1;
+    for theta = Rotor_angle
+        rotor_x = Reflection_radius * cos(theta);
+        rotor_y = Reflection_radius * sin(theta);
+        distance_rx = sqrt((Rx_x - rotor_x)^2+(Rx_y - rotor_y)^2);
+        Rx_angle = atan(Rx_z/distance_rx);
+        Tx_elevation_angle = atan(Altitude/r);
+        
+        data(r/25 + 1, i) = -max_fd*cos(Tx_elevation_angle)*cos(theta);
+        i = i + 1;
+    end
+end
+hold on
+for j = 1:5
+    plot(360*Rotor_angle/(2*pi),data(j,:))
+end
+hold off
+axis([0 360 -600 600]);
+title('Doppler Frequency vs. Rotor Position with varying Elevation Angle');
+xlabel('Rotor Position (deg)');
+ylabel('Doppler Frequency (Hz)');
+legend(strcat(num2str(360*atan(Altitude/Tx_radius(1))/(2*pi)),' deg'), strcat(num2str(360*atan(Altitude/Tx_radius(2))/(2*pi)),' deg'),strcat(num2str(360*atan(Altitude/Tx_radius(3))/(2*pi)),' deg'),strcat(num2str(360*atan(Altitude/Tx_radius(4))/(2*pi)),' deg'), strcat(num2str(360*atan(Altitude/Tx_radius(5))/(2*pi)),' deg'));

### 2016-09-29 Thesis MATLAB Scripts/plot_elevation_range_vs_pitch_2_ranges.m

@@ -1,0 +1,33 @@
+clear;
+data_pitch = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_pitch7.5deg_135deg.csv');
+data = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_135deg.csv');
+
+data_both = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/compare_pitches_at_135deg.csv');
+
+data_15 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/compare_pitches_at_135deg_15deg_add.csv');
+
+data(:,4) = (data(:,4)./(2*pi)).*360;
+data_pitch(:,4) = (data_pitch(:,4)./(2*pi)).*360;
+data_both(:,4) = (data_both(:,4)./(2*pi)).*360;
+
+
+figure;
+hold on
+plot(data_both(:,4),data_both(:,2));
+plot(data_both(:,4),data_both(:,3));
+plot(data_both(:,4),data_15(:,1));
+hold off
+
+legend('Pitch 0deg', '7.5deg', '15deg');
+title('Max Envelope Frequencies vs Transmitter Elevation Angle');
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+
+figure;
+hold on
+plot(data_both(:,4), data_both(:,3) - data_both(:,2));
+plot(data_both(:,4), data_15(:,1) - data_both(:,2));
+legend('Difference 0deg and 7.5deg','Difference 0deg and 15deg');
+title('Frequency Difference vs Transmitter Elevation Angle');
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');

### 2016-09-29 Thesis MATLAB Scripts/plot_elevation_vs_Doppler.m

@@ -1,0 +1,150 @@
+clear;
+data_45 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_45deg.csv');
+data_135 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_135deg.csv');
+data_225 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_225deg.csv');
+data_315 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_315deg.csv');
+data_x_0 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_x_0deg.csv');
+data_x_180 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_x_180deg.csv');
+data_y_90 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_y_90deg.csv');
+data_y_270 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_y_270deg.csv');
+
+
+% figure;
+% hold on
+% plot((data_45(:,4)/(2*pi))*360,data_45(:,2));
+% plot((data_45(:,4)/(2*pi))*360,data_45(:,3));
+% hold off
+% legend('Max Upper Envelope', 'Min Lower Envelope');
+% title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth at 45deg');
+% xlabel('Elevation Angle (deg)');
+% ylabel('Doppler Frequency (Hz)');
+% 
+% figure;
+% hold on
+% plot((data_135(:,4)/(2*pi))*360,data_135(:,2));
+% plot((data_135(:,4)/(2*pi))*360,data_135(:,3));
+% hold off
+% legend('Max Upper Envelope', 'Min Lower Envelope');
[…]

### 2016-09-29 Thesis MATLAB Scripts/range_elevation_relation.m

@@ -1,0 +1,10 @@
+clear;
+
+altitude = 200;
+range = 0.1:0.1:10000;
+elevation = (atan(altitude./range)./(2*pi))*360;
+
+plot(range,elevation)
+title('Transmitter Range vs Elevation Angle at an Altitude of 200m');
+xlabel('Range (m)');
+ylabel('Elevation Angle (deg)');

### 2016-09-29 Thesis MATLAB Scripts/sig_analysis_fix_timebase.m

@@ -1,0 +1,80 @@
+%fix time frequency base
+clear;
+total_samples = 479000; %959000;
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_range_45deg/*.csv');
+num_files = length(files);
+data = zeros(num_files,total_samples);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_range_45deg/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000; %program
+fs_real = 1/((1/(rpm/60))/total_samples);
+SNR = 50;
+
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,4000,5000,fs_real,'reassign','MinThreshold',-SNR,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > -70
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > -70) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+    figure;
+    hold on
+    %plot3(t*1000,lower_envelope/10000,z,'r','linewidth',4)
+    %plot3(t*1000,upper_envelope/10000,z,'b','linewidth',4)
+    
+    %plot3(t,f(nd)/1,q,'r','linewidth',4)
+    %plot3(t/60,cos(angle_b1(1:end-1)),z);
+    %plot3(t/60,cos(angle_b2(1:end-1)),z);
+    
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_0deg_rx_offset.m

@@ -1,0 +1,80 @@
+%signal not ready.....
+clear;
+RPM = 250;
+Altitude = 200;
+fc = 1e9;
+fs = 4000;
+c = 3e8;
+
+Rx_position = [0;7;Altitude-2];
+Tx_position = [0;0;0];
+
+Blade = 0:0.1:7.5;
+Blade_rotation = 0:0.1:4*pi;
+Blade_normal = [0;0;-1];
+
+for r = 10:10:1000
+
+i = 1;
+for R = -Blade_rotation
+    for B = Blade
+        hit_point = [[cos(R), -sin(R); sin(R), cos(R)]*[B;0];Altitude];
+        
+        perp = [-hit_point(2), hit_point(1), 0];
+        perp_normalized = perp/sqrt(perp(1)^2 + perp(2)^2 + perp(3)^2);
+        
+        Reflection_radius = B;
+        v = ((2*pi)/60)*RPM*Reflection_radius;
+        max_fd = 2*(v*fc)/c;
+        
+        Tx2Blade = hit_point - Tx_position;
+        Tx2Blade_normalized = Tx2Blade/sqrt(Tx2Blade(1)^2 + Tx2Blade(2)^2 + Tx2Blade(3)^2);
+        
+        Blade2Rx = hit_point - Rx_position;
+        Blade2Rx_normalized = Blade2Rx/sqrt(Blade2Rx(1)^2 + Blade2Rx(2)^2 + Blade2Rx(3)^2);
+        
+        Reflection = -Tx2Blade_normalized + (2 * Blade_normal) * dot(Tx2Blade_normalized,Blade_normal);
+        
+        Reflection_angle(i) = dot(Blade2Rx_normalized,Reflection);
+        doppler_angle(i) = dot(Blade2Rx_normalized,perp_normalized);
+        dop_freq(i) = max_fd*doppler_angle(i);
+        
+        if(acos(Reflection_angle(i)) < (pi/3))
+            power(i) = (Reflection_angle(i))^2;
+        else
+            power(i) = 0;
+        end
+        signal(i) = sqrt(power(i))*cos(2*pi*dop_freq(i));
+        i= i+1;
+    end 
+end
+
+% figure
+% plot(acos(doppler_angle))
+% title('doppler angle')
+% figure;
+% plot(acos(Reflection_angle))
+% title('reflection angle')
+% figure;
+% plot(dop_freq)
+% title('doppler freq')
+% figure;
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_analysis.m

@@ -1,0 +1,93 @@
+clear;
+total_samples = 959000;%479000; 
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/*.csv');
+num_files = length(files);
+data = zeros(num_files,total_samples);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+fs_real = 1/((1/(rpm/60))/total_samples);
+SNR = 50;
+%'reassign','MinThreshold',-SNR,
+
+data_table = zeros(num_files,3);
+
+upper_envelope_table = zeros(num_files,106);
+lower_envelope_table = zeros(num_files,106);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    ave_q(i) = mean(q);
+
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q(i)) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+    figure;
+    hold on
+    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+    plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+    spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_analysis_pitch_0tx_pos.m

@@ -1,0 +1,92 @@
+clear;
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_tx0/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_tx0/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+SNR = 50;
+
+freqs = fftshift(fft(data,length(data),2),2);
+freq = -fs/2:fs/size(freqs,2):fs/2;
+freq = freq(1:end-1);
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    t_fixed = 0:(1/(rpm/60))/length(t):(1/(rpm/60));
+    t_fixed = t_fixed(2:end);
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    ave_q(i) = mean(q);
+
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q(i)) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+    figure;
+    hold on
+    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_analysis_pitch_135deg.m

@@ -1,0 +1,88 @@
+clear;
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_pitch_max15deg_135deg/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_pitch_max15deg_135deg/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+SNR = 50;
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    t_fixed = 0:(1/(rpm/60))/length(t):(1/(rpm/60));
+    t_fixed = t_fixed(2:end);
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    ave_q(i) = mean(q);
+
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q(i)) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+    figure;
+    hold on
+    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+    %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+    %plot3(t/60,cos(angle_b1(1:end-1)),z);
+    %plot3(t/60,cos(angle_b2(1:end-1)),z);
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_analysis_rx_position_y.m

@@ -1,0 +1,90 @@
+clear;
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rx_y/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rx_y/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+SNR = 50;
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    t_fixed = 0:(1/(rpm/60))/length(t):(1/(rpm/60));
+    t_fixed = t_fixed(2:end);
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    q = q(q~=-inf);
+    
+    ave_q(i) = mean(q);
+    
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q(i)) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+%     %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+%     %plot3(t/60,cos(angle_b1(1:end-1)),z);
+%     %plot3(t/60,cos(angle_b2(1:end-1)),z);
[…]

### 2016-09-29 Thesis MATLAB Scripts/signal_analysis_tx_azimuth.m

@@ -1,0 +1,94 @@
+clear;
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000);
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+SNR = 50;
+
+freqs = fftshift(fft(data,length(data),2),2);
+freq = -fs/2:fs/size(freqs,2):fs/2;
+freq = freq(1:end-1);
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > -15
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > -15) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+    
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+%     %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+%     %plot3(t/60,cos(angle_b1(1:end-1)),z);
+%     %plot3(t/60,cos(angle_b2(1:end-1)),z);
[…]

### 2016-09-29 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -1,0 +1,245 @@
+%test alg for azimuth angle
+clear;
+
+%--------------------------------------------------------------------------
+%Load Data
+%--------------------------------------------------------------------------
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000); %959000;
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/',files(i).name)));
+end
+
+%--------------------------------------------------------------------------
+%Known Constants
+%--------------------------------------------------------------------------
+fs = 4000;
+RPM = 250;
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+tx_range = 50;
+
+%--------------------------------------------------------------------------
+%Find Doppler Envelopes
+%--------------------------------------------------------------------------
+
+%shift data for different start sections
+%data = circshift(data,31,1);
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    ave_q(i) = mean(q);
+    ave_q_now(i) = mean(ave_q);
+    
+    
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > ave_q_now(i)
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > ave_q_now(i)) && (log_power(7501-j,slice) ~= -inf)
[…]

### 2016-09-29 Thesis MATLAB Scripts/test_alg_azimuth_angle.m

@@ -1,0 +1,224 @@
+%test alg for azimuth angle
+clear;
+
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/*.csv');
+num_files = length(files);
+data = zeros(num_files,479000); %959000;
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/',files(i).name)));
+end
+
+rpm = 250;
+fs = 4000;
+SNR = 50;
+
+%shift data for different start sections
+%data = circshift(data,31,1);
+
+data_table = zeros(num_files,3);
+
+for i=1:num_files
+    [s,f,t,p] = spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
+    log_power = 10*log10(p);
+    [q,nd] = max(10*log10(p));
+    
+    [M_q,I_q] = max(abs(nd-2500));
+    
+    lower_envelope = zeros(length(t),1);
+    upper_envelope = zeros(length(t),1);
+
+    for slice = 1:length(t)
+        for j = 1:2500
+            if log_power(j,slice) > -10
+                lower_envelope(slice) = f(j);
+                break;
+            end  
+        end
+        for j = 2501:5000
+            if (log_power(7501-j,slice) > -10) && (log_power(7501-j,slice) ~= -inf)
+                upper_envelope(slice) = f(7501-j);
+                break;
+            end  
+        end
+    end
+    
+    lower_envelope = smooth(lower_envelope,.02);
+    upper_envelope = smooth(upper_envelope,.02);
+   
+    data_table(i,1) = max(upper_envelope); 
+    data_table(i,2) = min(lower_envelope);
+end
+
+Azimuth = 0:(360)/(num_files - 1):360;
+
+%data_table(:,2) = smooth(data_table(:,2),.1); helps with noisy min values
+
+figure;
+hold on
[…]

### 2016-09-29 Thesis MATLAB Scripts/test_alg_elevation_angle.m

@@ -1,0 +1,72 @@
+%clear;
+data_x_180 = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_x_average_current_frame_method.csv');
+
+figure;
+hold on
+plot(data_x_180(:,5), data_x_180(:,2));
+plot(data_x_180(:,5), data_x_180(:,3));
+hold off
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth at 180deg');
+xlabel('Elevation Angle (deg)');
+ylabel('Doppler Frequency (Hz)');
+
+%---------------------------------------------------------------------------------------------------
+
+%max doppler for reflection radius
+RPM = 250;
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+data_x_180(:,8) = abs(data_x_180(:,8));
+
+test_alg_angle = acos(data_x_180(:,2)/max_fd);
+figure;
+hold on
+plot((data_x_180(:,8)/(2*pi))*360,(test_alg_angle/(2*pi))*360)
+plot((data_x_180(:,8)/(2*pi))*360,(data_x_180(:,8)/(2*pi))*360)
+hold off
+title('Elevation Angle Comparason');
+legend('Estimated Angle', 'Actual Angle');
+xlabel('Elevation Angle Actual (deg)');
+ylabel('Elevation Angle (deg)');
+
+%error
+angle_error = ((((test_alg_angle/(2*pi))*360) - ((data_x_180(:,8)/(2*pi))*360))./((data_x_180(:,8)/(2*pi))*360))*100;
+figure;
+plot((data_x_180(:,8)/(2*pi))*360,angle_error)
+title('Elevation Angle Percent Error');
+xlabel('Elevation Angle (deg)');
+ylabel('Percent Error');
+
+%distance
+dtx_estimate = Altitude./tan(test_alg_angle);
+dtx_actual = abs(data_x_180(:,5));
+
+figure;
+hold on
+plot(dtx_actual,dtx_estimate)
+plot(dtx_actual,dtx_actual)
+hold off
+title('Distance Comparason');
+legend('Estimated Distance', 'Actual Distance');
[…]

### 2016-09-29 Thesis MATLAB Scripts/test_alg_elevation_angle_rx_centered.m

@@ -1,0 +1,104 @@
+clear;
+center_zero = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_maxDoppler_range_180deg_new_apxMethod5.csv');
+
+% figure;
+% hold on
+% plot((center_zero(:,4)/(2*pi))*360, center_zero(:,2));
+% plot((center_zero(:,4)/(2*pi))*360, center_zero(:,3));
+% hold off
+% legend('Max Upper Envelope', 'Min Lower Envelope');
+% title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth at 180deg');
+% xlabel('Elevation Angle (deg)');
+% ylabel('Doppler Frequency (Hz)');
+
+%---------------------------------------------------------------------------------------------------
+
+%max doppler for reflection radius
+RPM = 250;
+Altitude = 200;
+fc = 1e9;
+c = 3e8;
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+distance_Rx = 2;
+lambda_Tx = c/fc;
+RPM_rads = (2*pi/60)*RPM;
+
+r_estimate = (center_zero(:,2)*c)./(2*fc*RPM_rads);
+theta_estimate = atan(distance_Rx./r_estimate);
+dtx_estimate = ((Altitude./tan(theta_estimate)) + r_estimate);
+alpha_estimate = atan(Altitude./dtx_estimate);
+
+dtx_adjusted = dtx_estimate;
+actual = center_zero(:,1);
+error_dtx = (abs(dtx_adjusted) - abs(actual));
+
+figure;
+hold on;
+plot(dtx_adjusted)
+plot(actual)
+hold off;
+
+figure;
+plot(error_dtx)
+
+scan_dist = 0:.01:700;
+
+equality = (center_zero(:,2).*(Altitude+distance_Rx))/(2*(RPM_rads/lambda_Tx)*distance_Rx);
+scan_func = scan_dist.*cos(atan(Altitude./scan_dist));
+
+distance_tx_estimate = zeros(1,11);
+for i = 1:length(equality)
+    index = find(scan_func < equality(i));
+    distance_tx_estimate(i) = scan_dist(index(end));
+end
+
+
+figure;
+hold on
+plot(center_zero(:,1),distance_tx_estimate)
+hold off
+
[…]

### 2016-09-29 Thesis MATLAB Scripts/test_convolution_on_x_range.m

@@ -1,0 +1,29 @@
+%test convolution on range
+clear;
+upper_envelopes = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_upper_envelope_rangeX.csv');
+lower_envelopes = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_lower_envelope_rangeX.csv');
+
+next_upper = zeros(1,106);
+next_lower = zeros(1,106);
+
+for i = 1:41
+    u = upper_envelopes(i,:);
+    l = lower_envelopes(i,:);
+    
+%     figure;
+%     hold on
+%     plot(u(2:end))
+%     plot(l(2:end))
+%     hold off
+    
+    upper_conv = conv(u(2:end),next_upper);
+    lower_conv = conv(l(2:end),next_lower);
+    figure;
+    hold on
+    plot(upper_conv);
+    plot(lower_conv);
+    hold off
+    next_upper = u(2:end);
+    next_lower = l(2:end);
+end
+

### 2016-10-11 Background.tex
update files

@@
-\chapter{Literature Review and Geometric Models}
+\chapter{Literature Review and Geometric Models} \label{ch:background}
 
@@
 The rotating blades of the helicopter modulate signals that hit the blades by reflecting them.
-The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point (refs?).
+The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point (Yaman Zhang 2000).
 The rotor blade modulation (RBM) has a complex form and is influenced by several object parameters.
 These parameters range from the positioning of a signal source to the physical dimensions of the blades.
-The resulting modulated signal has been used in radar applications relating to the classification of any aircraft with a rotor blade, propeller or even jet engines (refs?).
-The doppler shifted signal has also been shown to have a parasitic effect on GPS anti-jamming algorithms (refs?).
+
+The resulting modulated signal has been used in RADAR applications.
+First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in (Barry D.
+Bullard 1991) that defines a specific signature for each parameter.
+The ability to detect a hovering helicopter based on the blade flashes caused by reflected RADAR pulses off the blades is defined in (J Misiurewicz 1997).
+The micro-doppler produced by the RADAR reflection is used in (Thayaparan, T.
+2007) to determine the rotation rate of the main and tail rotor blades using the wavelet transform.
+
+The doppler shifted signal effects the performance of common adaptive GPS anti-jamming algorithms located on a helicopter platform, unless the covariance estimation is completed within a few milliseconds.
+In iterative approaches the non-stationary signal characteristics cause degradation as well (F.
+Barbiero 2009).
+The affect of RBM on the BER of communications is examined in (Yaman Zhang 2000).
+Where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in their model.
+
 The role of RBM is based on the specific doppler shift associated with where a dominant reflection occurs along the length of the of the blade, and the associated elevation angle of the transmitter.

### 2016-10-11 Conclusion.tex
update files

@@
-\chapter{Conclusion and Future Work}
+\chapter{Conclusion and Future Work} \label{ch:conclusion}
 
@@
 
-\section{Future Improvements}
+Over the course of this thesis a three dimensional ray tracer application was built in C++ to produce a RBM signal according to a variety of physical parameters.
+The physical parameters associated with a helicopter blade and the positioning of transmitter and receiver hardware were swept independently to build knowledge on how they affect the resulting signal.
+That data was then processed using time frequency analysis to produce a doppler envelope.
+An envelope of each parameter step was used to determine an overall trend.
+Then with those trends an algorithm was derived to find the azimuth and elevation angle of the transmitter with relationship to the helicopter platform.
+The algorithm accurately finds the azimuth angle and elevation using the data collected in the simulation environment with almost no error in the azimuth estimation and less than 2\% error in elevation angle when blade pitch in 0\textdegree.
+
+\section{Future Work}
+%Real world experiment needs to be conducted starting with small scale and moving towards a large scale implementation on a helicopter platform.
+The first thing that needs to be done in continuing this research is to perform a real world experiment to officially evaluate the ray tracing application.
+To do this appropriate hardware needs to be defined in the form of a software defined radio for both the receiver and transmitter along with a software workflow such as GNU Radio.
+Next a small scale environment would need to be set up, including the above hardware along with some form of rotating metal blade or thin plate rotating at a sufficient rate to produce a doppler spread similar to those defined in the simulation.
+After that data is collected and analyzed a full scale experiment would need to be conducted including a real helicopter platform and an environment with large expanses of flat ground.
+
+%Evaluate the estimation techniques on the real world collected data to see if they are still applicable.
+Once the real world experiments have been conducted, and are shown to be similar to the signal produced by the simulation, the estimation techniques defined in this thesis can be evaluated on the real signal to determine if they are sufficient in practice.
+
+%Improve propagation model to better represent the real world conditions, material, more physical effects on RF, near field problems etc.
+After the physical validation the ray tracing application can be modified to include more physical phenomenon.
+The other improvement would be to introduce more objects into the scene model which would require modification to the tracing algorithm to include ray casting distributions in their particular direction.
+
+%Improve computation speed by employing multithreading or computation on GPU Architecture for reduced simulation time, not necessary but would be more convenient.
+Another improvement on the simulation would be to increase the speed of computation.
+This could be done by implementing multi-threading or, since raytracing is heavily parallelizable, a GPU based architecture.
+The multi-threading option would require minor code modifications but realizing the simulation on a GPU would require a full rewrite of the software to take advantage of the GPU's abilities.
+
+%Introduce a pitch parameter to the estimation equation based on empirical data, so that if the blades are pitched the doppler can be adjusted accordingly.
+The current estimation does not take into account the physical pitch value when correcting for pitch and might not cover all the cases that pitch can effect.
+Therefore further investigation is needed into how the pitch affects the received signal for improved azimuth and elevation estimation.
+
+%Because there is more information in the received envelopes besides the maximum and minimum the specific shape could be used to better estimate azimuth and elevation without the need to complete a full revolution as described in the proposed method.
+The estimation methods described in this thesis rely only on the maximum and minimum values of the doppler envelopes calculated but their shape could also be of particular interest as well.
+When varying the parameters of azimuth and elevation the shape of the envelope changes in a distinctive manner, and by using a training algorithm the position of the transmitter might be able to be tracked in time by evaluating the change in shape.
+where currently if we want to locate the transmitter in a successive fashion a full revolution of the helicopter platform is needed to resolve position ambiguity.

### 2016-10-11 Introduction.tex
update files

@@
 The software provides insight into the complex interaction between the rotor blade shape and the placement of the receiver and transmitters.
-The second contribution is the ability to use the imparted rotor blade modulation to estimate the azimuth and elevation angles with respect to the location of the rotating blades.
+The second contribution is an in depth analysis of how several different variables affect the modulation on the received signal.
+And lastly, techniques to use the imparted rotor blade modulation to estimate the azimuth and elevation angles with respect to the location of the rotating blades.
 
 \section{Organization}
-In Chapter 2 we present the background and theory behind rotor blade modulation. we then formulate the basic geometry behind the RBM effect.
+In Chapter \ref{ch:background} we present the background and theory behind rotor blade modulation. we then formulate the basic geometry behind the RBM effect.
 
-In Chapter 3 we Introduce the radio propagation simulation in several sections.
+In Chapter \ref{ch:radio_propagation} we Introduce the radio propagation simulation in several sections.
 First is the RF propagation model which defines the physical effects that are simulated within the software.
@@
 
-In Chapter 4 we present the result of the parameter swept simulations of the ray tracing software.
+In Chapter \ref{ch:simulations} we present the result of the parameter swept simulations of the ray tracing software.
 Next the received signals from the simulation are analyzed using several DSP techniques to define the signal characteristics that will be used in the next chapter for estimation.
 
-In Chapter 5 Those characteristics are then used to estimate the azimuth and elevation angle of the transmitter based on the given rotor and receiver parameters.
+In Chapter  \ref{ch:results} Those characteristics are then used to estimate the azimuth and elevation angle of the transmitter based on the given rotor and receiver parameters.
 Those estimates are then compared with the original position of the transmitter to determine the methods accuracy.
 
-In Chapter 6 the summery of the results are detailed along with the current limitations. Lastly future improvements on the work will be discussed.
+In Chapter \ref{ch:conclusion} the summery of the results are detailed along with the current limitations. Lastly future improvements on the work will be discussed.

### 2016-10-11 MSc. Thesis Template.tex
update files

@@
 I would also like to thank Matt Kruse and Charlie Cooper for coming up the research topic and support through the process.
-I would also like to thank the Broadband Wireless Access \& Applications Center and Rincon Research Corporation for supporting my research.
+I would also like to thank the Broadband Wireless Access \& Applications Center and Rincon Research Corporation for supporting this research.
 }
@@
 The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter.
-RBM is known to degrade the performance of RF communications on rotorcraft and can be used in RADAR applications to detect and classify aircraft, but there is little on its usefulness in other areas.This project will look at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.
-To do this a RF ray tracing program was developed in C++ to produce a simulation of the RBM.
+RBM is known to degrade the performance of RF communications on rotorcraft and can be used in RADAR applications to detect and classify aircraft, but there is little on its usefulness in other areas.
+This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.
+
+To do this a 3D RF ray tracing program was developed in C++ to produce simulations of RBM signals.
+The developed program is based on optical ray tracing algorithms with modified physical propagation effects for RF signals, and swapping lights and cameras for RF transmitters and receivers respectively.
+The ray tracer was then run over a realistic set of physical parameters to determine their effects on the received signal, this includes transmitter azimuth and elevation angle, receiver position, blade pitch, etc.
+along with their combinations.
+From the simulations the azimuth and elevation angle, of the transmitter, produce predictable modulations on the received signal.
+Based on the trends in the signal's modulation a DSP algorithm was distilled down that accurately determines the azimuth and elevation angle of the transmitter from simulated signal data.
 }
@@
 
-\include{Simulation_Data}
+%\include{Simulation_Data}
 
-\include{Matlab_Code}
+%\include{Matlab_Code}
 

### 2016-10-11 Radio_Propagation_Simulation.tex
update files

@@
-\chapter{Radio Propagation Simulation}
+\chapter{Radio Propagation Simulation} \label{ch:radio_propagation}
 
@@
 The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions.
-The ray tracing engine uses recursive execution described by Turner Whitted (Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively.
+The ray tracing engine uses recursive execution described in (Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
 
@@
 %define the math behind the physical laws that are simulated within the simulation
-The propagation model defined in this project will focus on the following physical phenomena, free-space path loss, reflection, and the doppler effect.
-They are all formally established models described in full in (place refs here).
-Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made in the scene model.
+The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect.
+They are all formally established models described in full in (Bertoni, 2000; Blaunstein, 2000; Griffiths, 1987)(FIND OTHERS).
+Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.
 
@@
 %formula description
-where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell?s law \ref{eqn:snell}.
+where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell's law \ref{eqn:snell}.
 
@@
 
-In the following simulations performed, $\varepsilon$ will have a value of (-), which is an approximate value for (-). The final reflected power is
+The final reflected power is
 
@@
 
+%reflection power loss description
 where $P_i$ is the incident power before reflection losses.
 
+%multipath fading
+\subsection{Frequency-selective Fading}
+The transmitted signal power experiences fading described by
+
+\begin{equation}
+	F = cos\left(2\pi \frac{d}{c} + t_0\right)
+	\label{eqn:fading_coeff}
+\end{equation}
+
+where $F$ is the fading coefficient, $d$ is the total distance the particular ray has traveled, $c$ is the speed of light, and $t_0$ is the starting time of the current frame.
+The power can then be calculated using
+
+\begin{equation}
+	P_{faded} = PF
+	\label{eqn:power_faded}
+\end{equation}
+
+where $P_{faded}$ is the adjusted power due to fading and $P$ is the signal power. The superposition of each ray's faded power becomes the received signal.
+
 \subsubsection{Diffuse Reflection}
-A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (refs?).
+A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (J.
+Lambert, "Photometria Sive de Mensura et Gradibus Luminus Colorum et Umbrae", 1760).
 The hemisphere is located at the point of the ray hit, producing rays away from the surface.
-To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (refs?).
-There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(refs?).
+To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
+There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(Phong, 1998)(OK).
 This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces.
 Since is was not designed for longer wavelengths used in RF communications an assumption is made that small scale features of the surface, relevant to light waves,  produce a reflectance distribution similar for larger wavelengths.
-The BRDF parameters were then selected to be frequency independent to form a plausible reflectance distribution for the physical effects.
+
+%The BRDF parameters were then selected to be frequency independent to form a plausible reflectance distribution for the physical effects.
 
@@
 Theses designs form a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade.
+Figure \ref{fig:airfoil} shows the airfoil cross-section that will be used to create the rotor surface.
 
@@
 		\includegraphics[width=15cm]{images/radio_propagation/2d_airfoil.png}
-		\caption{Airfoil}
+		\caption{Airfoil Cross-Section}
 		\label{fig:airfoil}
@@
 The primitive shapes are triangles that span between the ribs and go around to cover the surface.
+This was done using a lightweight mesh generation method using the a priori knowledge of the blade shape.
+The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the blade being composed of rib sections with consistent shape.
 The surface normals are then adjusted to match the correct directionality.
+Figure \ref{fig:tessilation} shows the created surface for the rotor blade that will be used in the scene.
 
@@
 		\includegraphics[width=15cm]{images/radio_propagation/blade_surface_tesselation.eps}
-		\caption{Tessilation}
+		\caption{Blade Surface Tessilation}
 		\label{fig:tessilation}
@@
 This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture and eliminates computational overhead for the tracing engine.
+Figure \ref{fig:transmitter_direction} shows the rays, in blue, casted only in the vicinity of the rotor blade and receiver.
 
@@
 %describe the core tracing engine and describe the flow of the program
-The ray tracing simulation is performed in the Monte Carlo fashion building in the scene and propagation models.
-Raytracing is a well established method for creating realistic images in (ray tracing papers).
-The simulation is performed over successive iterations, each iteration is called a frame.
-Each frame will be updated to represent the change in the position of the rotor blade.
+The ray tracing simulation is conducted in the Monte Carlo fashion acting on the scene and propagation models.
+This method of raytracing is established for creating realistic images in (Suffern, 2007; Pharr, 2010).
+The simulation is performed over successive iterations.
+Each iteration is a discrete element called a frame.
+Where each frame will be updated to represent the change in the position of the rotor blade.
 
@@
 Then the number of frames that will be computed.
-The number of frames are determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver.
+The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver defined before the beginning of the simulation.
 This is described by
@@
 
-The casting technique reduces the computation overhead by limiting the space. It also creates higher resolution result by focusing the limited number of rays in the direction of the other objects.
+The casting technique reduces the computation overhead by limiting the search space.
+It also creates higher resolution result by focusing the limited number of rays in the direction of the other objects shown in figure \ref{fig:samp_method}.
 
@@
 Due to only the rotor and receiver in the scene, besides the transmitter, rays that are found to hit the rotor the reflection ray is calculated.
-Then the angle between the reflection and a ray between the point of reflection and the receiver is used to create a dedicated ray in that direction with a decayed power and adjusted frequency.
-
-%psudo code
-
-%uml diagrams
+Then the angle between the reflection and a ray between the point of reflection and the receiver is used to create a dedicated ray in that direction with a decayed power and adjusted frequency accordingly.
 

### 2016-10-11 Ray_Tracing_Software.tex
update files

@@
 \chapter{Ray Tracing Software}
-something for code reuse and the git hub stuff
+
+The ray tracing software developed during the course of the thesis is written in C++ in an XCode environment, but a generic implementation is provided to run on other operating systems.
+This code is loosely based on the work of Eric Degroot's developed in (Eric's thesis) and implemented some modified base classes developed by him.
+It is a specific tool for analyzing the affects of rotor blade modulation on a signal tone, it does not provide generic 3D ray tracing in order to optimize the performance for this task.
+The software is provided without a GUI implementation and is run on different parameters by modifying the main.c file.
+This is due to the amount of parameters involved but could be easily extended to provide command line arguments in future iterations.
+
+To use the software for performing RBM simulations there are several key parameters that are needed.
+First a file containing the points that define the 2D section of the airfoil shape, one default file is included in the software package for ease of use and as a template for other airfoil shapes.
+
+the other key parameters that define the simulation are shown in table \ref{tab:key_values}
+
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l | p{3cm} |}
+    \hline
+    Name & type & Default Value& units & Description\\ \hline
+     rx\_x &  double & 0 & m & receiver position in x  \\ \hline
+     rx\_y & double & 7 & m & receiver position in y \\ \hline 
+     rx\_z & double & 2 & m & receiver position in z below rotor  \\ \hline
+     Bandwidth & double & 2000 & Hz & Bandwidth of the receiver  \\ \hline
+     rx\_fc & double & 1000000000 & Hz & center frequency of the receiver \\ \hline 
+     tx\_x & double & 100 & m & transmitter position in x \\ \hline
+     tx\_y & double & 100 & m & transmitter position in y \\ \hline
+     tx\_fc & double & 1000000000 & Hz & transmitter center frequency \\ \hline
+     tx\_power & double & 4000 & & transmitter power \\ \hline
+     num\_blades & int & 2 & none & number of blades \\ \hline
+     RPM & double & 250 & RPM & Blade revolutions per minuet \\ \hline
+     altitude & double & 200 & m & rotor altitude \\ \hline
+     blade\_length & double & 7.5 & m & length of the one rotor blade \\ \hline
+     pitch & double & 0 & radians & pitch of the rotor use $-\theta_p$  \\ \hline
+     num\_ribs & double & 10 & none & number of ribs that makes up one blade \\ \hline
+     files & double & 10 & none & number of files to produce \\ \hline
+    \end{tabular}
+     \caption{Simulation parameters}
+    \label{tab:key_values}
+\end{center}
+\end{table}
+
+The output file also needs to be defined with a unique name that changes, this is important because the program will just write over the old file if you do not have a unique naming scheme.
+this could be just an increasing number or related to one of the variable sweeps.
+
+To run the simulation on a Mac load into XCode the project file and configure the main file to reflect the type of simulation desired, then hit the play button.
+
+On Linux machines the code must first be built using make with the main file configured before hand. Then run the Raytracer3D executable.
+
+The output file contains more than just the signal data the first few data entries are data pertaining to the simulation parameters.
+it is important to separate this data from the signal data before processing the signal.
+The template for this data is shown in table
+\ref{tab:file_values}.
+
+\begin{table}
+\begin{center}
+    \begin{tabular}{| l | l | l | l | l | l | l | l | l | l |}
+    \hline
+    1 & 2 & 3 & 4 & 5 & 6 & 7 & 8 & 9 & 10 \\ \hline
+      rx\_x & rx\_y & rx\_z & Bandwidth & rx\_fc & tx\_x & tx\_y & tx\_fc & tx\_power & num\_ribs \\ \hline
+    \end{tabular}
+    \begin{tabular}{| p{1cm} | p{1cm} | l | l | l | l | p{1.5cm} | p{1.5cm} |}
+    \hline
+    11 & 12 & 13 & 14 & 15 & 16 & 17 & 18\\ \hline
+     num \_blades & blade \_length & pitch & RPM & altitude & tx\_radius & elevation \_angle & azimuth \_angle \\ \hline
+    \end{tabular}
+     \caption{Output file header with simulation parameter order}
+    \label{tab:file_values}
+\end{center}
+\end{table}
+
+this is all provided in a single string of comma separated values called a .CSV file. MATLAB has a built in function to read CSV data.
+
+%matlab csv read
+\begin{lstlisting}
+data = csvread('file_path/file_name')
+\end{lstlisting}
+
+after all the data is read into MATLAB the data can be split into two vectors, one pertaining to the physical simulation parameters and the other to the received signal.

### 2016-10-11 Results_new.tex
update files

@@
-\chapter{Results}
+\chapter{Results} \label{ch:results}
 
@@
 
-\section{Transmitter Azimuth Angle Estimation}
+\section{Transmitter Azimuth Angle Estimation} \label{sec:transmitter_azimuth_angle_estimation}
 %formulate the estimation equation and discuss ambiguity considerations
@@
 
-\section{Transmitter Elevation Angle Estimation}
+\section{Transmitter Elevation Angle Estimation} \label{sec:transmitter_elevation_angle_estimation}
 %formulate the estimation equation and discuss ambiguity considerations
@@
 
+where $f_{DopplerMax}$ is defined in equation \ref{eqn:fd_max}.
+
 %figure of elevation angle 
@@
 
-This error is caused by a limitation on the estimation is that the doppler shift is limited by the maximum amount doppler that the blade rotation can produce shown in equation (-) by replacing $v_r$ with $v_rMax$ which is calculated by
+This error is caused by a limitation on the estimation is that the doppler shift is limited by the maximum amount doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
 
@@
 Figure \ref{fig:percent_error_elevation_180deg} shows the percent error with respect to the elevation angle and it starts to become unusable around 18\textdegree \space or 20\textdegree \space where the percent error starts to shoot past acceptable ranges.
+
+%------------------------------
+%pitch considerations
+%------------------------------
+
+If we now consider a pitched blade the above method for estimating Azimuth and elevation becomes inaccurate due to the increased doppler between 90\textdegree and 270\textdegree and the decreased doppler on the other side.
+To correct this error we need to correct both the difference calculation and the correct doppler data accordingly.
+The uncorrected data is shown in figure \ref{fig:diff_pitch_noCorrection} and \ref{fig:dop_pitch_noCorrection} with percent azimuth error of 20\% and percent elevation error of 35\%.
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=10cm]{images/results/difference_pitch_noCorrection.eps}
+		\caption{Uncorrected Envelope Difference vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
+		\label{fig:diff_pitch_noCorrection}
+	\end{center}
+\end{figure}
+
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=10cm]{images/results/correct_dop_pitch_noCorrection.eps}
+		\caption{Uncorrected Doppler vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
+		\label{fig:dop_pitch_noCorrection}
+	\end{center}
+\end{figure}
+
+Comparing the envelope difference of no pitch and pitched blade, in figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
+Therefore we can first correct this by re-centering the pitch difference to be located around zero.
+
+\begin{equation}
+	A_{shift} = \frac{Max(EnvelopeDifference) - |Min(EnvelopeDifference)|}{2}
+	\label{eqn:pitch_shift}
+\end{equation}
+
+\begin{equation}
+	EnvelopeDifference = EnvelopeDifference - A_{shift}
+	\label{eqn:diff_shift}
+\end{equation}
+
+Then with this knowledge $f_{DopplerCorrect}$ is recalculated and then is adjusted to the correct frequencies with
+
+%fix correct doppler for pitch
+\begin{equation}
+	f_{DopplerCorrect} = f_{DopplerCorrect} + A_{shift}cos\left(\theta_{Az}\right)
+	\label{eqn:fd_max}
+\end{equation}
+
+Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with the a priori information that the cosign should be one period in length.
+These corrections result in the percent azimuth error of 10\% and 6.5\% elevation angle error.
+The error in the azimuth is quite large compared to the results when pitch is 0\textdegree but the sample is only comprised of 41 points which turns out to be 9\textdegree per sample in which 10\% error would be off by one sample.
+Increasing the samples per revolution would most likely decrease this error.
+The elevation angle percent error is within a useable range but could be decreased with further tuning to the preliminary pitch adjustment algorithm.

### 2016-10-11 Simulation.tex
update files

@@
-\chapter{Received Signal Simulations}
+\chapter{Received Signal Simulations} \label{ch:simulations}
 %define the signal characteristics and evaluate the properties of the resulting signal over the parameter sweeps
@@
 The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept.
-For the azimuth angle sweep, which will be shown later in (-), the maximum power is found in each time slice then those values are averaged.
+For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged.
 Then for each successive angle the same average is taken and averaged with all the others
@@
 This technique is used because the elevation angle is remaining constant, so the distance with the helicopter platform should be constant as well.
-When varying the elevation angle the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.
+When varying the elevation angle in section \ref{sec:tea} the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.
 
@@
 
-The effect of azimuth angle on the maximum measured doppler will be characterized in section (-)
+The effect of pitching the blade is that it modifies the results of the azimuth sweep when compared to figure \ref{fig:tx_azimuth_angle_200}.
+The resulting min and max envelope frequencies vs azimuth angle for pitch are shown in \ref{fig:pitch_azimuth_rev}.
+This occurs because the pitch of the blade angles RF reflections more in the direction of travel but not at all points in the azimuth.
+When the transmitter is located between 90\textdegree and 270\textdegree pitch causes an increase in doppler but elsewhere decreases the amount of doppler shift.
+The decrease is caused by the blade surface top reflecting receding doppler away from the receiver at those angles.
+
+%azimuth pitch effect
+\begin{figure}
+	\begin{center}
+		\includegraphics[width=10cm]{images/simulation/pitch_azimuth_rev.eps}
+		\caption{Max and Min Envelope Frequencies vs Transmitter Elevation Angle with 7.5deg Pitch}
+		\label{fig:pitch_azimuth_rev}
+	\end{center}
+\end{figure}
+
+The effect of azimuth angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_azimuth_angle_estimation}
 
 %-----------------------------------------------------------------------------------------------------------------------------------------------------------------------
-\section{Transmitter Elevation Angle}
+\section{Transmitter Elevation Angle} \label{sec:tea}
 %display elevation angle with respect to max doppler readings and describe patterns
@@
 
-The effect of elevation angle on the maximum measured doppler will be characterized in section (-).
+The effect of elevation angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_elevation_angle_estimation}.

### 2016-10-11 doxygen/latex/class_scene.tex
update files

@@
 
-\subsection{Member Function Documentation}
-\hypertarget{class_scene_a969abe0e6022d73ff082d380c59d83f5}{}\label{class_scene_a969abe0e6022d73ff082d380c59d83f5} 
-\index{Scene@{Scene}!get\+Doppler@{get\+Doppler}}
-\index{get\+Doppler@{get\+Doppler}!Scene@{Scene}}
-\subsubsection{\texorpdfstring{get\+Doppler()}{getDoppler()}}
-{\footnotesize\ttfamily double Scene\+::get\+Doppler (\begin{DoxyParamCaption}\item[{\hyperlink{class_ray3_d}{Ray3D} \&}]{test\+\_\+ray,  }\item[{\hyperlink{class_vector3_d}{Vector3D} \&}]{hit\+Normal,  }\item[{\hyperlink{class_point3_d}{Point3D} \&}]{hit\+Point,  }\item[{double}]{R\+PM }\end{DoxyParamCaption}) const\hspace{0.3cm}{\ttfamily [inline]}}
-
-!!!! doppler does not get affected by the normal, need to check this. not sure if this is correct.
-
 The documentation for this class was generated from the following files\+:\begin{DoxyCompactItemize}

### 2016-10-11 Thesis MATLAB Scripts/Envelope.m

@@ -1,5 +1,6 @@
 %envelope calculation
 clear;
+
 samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/test_locationdatainfile_4.csv');
 rpm = 250;
 
@@ -60,3 +61,11 @@ ylabel('Doppler Frequency (kHz)');
 colormap(jet);
 colorbar
 view(2)
+
+% f0 = 5/(2*pi);
+% DT = 1/4000;
+% t = 0:DT:(numel(samples)*DT)-DT;
+% scales = helperCWTTimeFreqVector(1,2e3,f0,DT,32);
+% cwtsig = cwtft({samples,DT},'wavelet','bump','scales',scales);
+% helperCWTTimeFreqPlot(cwtsig.cfs,t.*1e6,cwtsig.frequencies./1000,...
+%     'surf','Bat Echolocation (CWT)','Microseconds','kHz')

### 2016-10-11 Thesis MATLAB Scripts/Signal_analysis_w_metadata.m

@@ -1,0 +1,126 @@
+%test alg for elevation angle only sweep
+clear;
+
+%--------------------------------------------------------------------------
+%Load Data
+%--------------------------------------------------------------------------
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
+num_files = length(files);
+%data = zeros(num_files,959006); %479000;
+for i=1:num_files
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
+end
+
+%--------------------------------------------------------------------------
+%Known Constants
+%--------------------------------------------------------------------------
+fs = 4000;
+RPM = 250;
+fc = 1e9;
+c = 3e8;
+
+Reflection_radius = 7.5;
+v = ((2*pi)/60)*RPM*Reflection_radius;
+max_fd = 2*(v*fc)/c;
+
+%--------------------------------------------------------------------------
+%Find Doppler Envelopes
+%--------------------------------------------------------------------------
+
+%sort data by radius r
+%data = sortrows(data,4);
+
+location_data = data(:,1:6);
+signal_data = data(:,7:end);
+
+data_table = zeros(num_files,3);
+
+window = 5000;
+noverlap = 500;
+
+%signal_data = decimate(signal_data,10);
+% Fpass = 1000;
+% Fstop = 1400;
+% Apass = 1;
+% Astop = 200;
+% Fs = 4e3;
+% 
+% d = designfilt('lowpassfir', ...
+%   'PassbandFrequency',Fpass,'StopbandFrequency',Fstop, ...
+%   'PassbandRipple',Apass,'StopbandAttenuation',Astop, ...
+%   'DesignMethod','equiripple','SampleRate',Fs);
+% 
+% fvtool(d)
+% 
+% signal_data = filter(d,signal_data);
+
+for i=1:num_files
+    
+    [s,f,t,p] = spectrogram(signal_data(i,:),window,noverlap,window,fs,'yaxis','centered');
+    angle_b1 = 0:(2*pi)/length(t):2*pi;
+    angle_b2 = pi:(2*pi)/length(t):3*pi;
+    z = zeros(1,length(t));
+    
[…]

### 2016-10-11 Thesis MATLAB Scripts/max_doppler_180deg_rx_offset.m

@@ -11,11 +11,6 @@ Reflection_radius = 7.5;
 v = ((2*pi)/60)*RPM*Reflection_radius;
 max_fd = 2*(v*fc)/c;
 
-%Rx position (might not be needed)
-Rx_z = 2;
-Rx_y = 7;
-Rx_x = 0;
-
 Tx_radius = 0:1:450;
 elevation_angle = atan(Altitude./(Tx_radius));
 
@@ -29,3 +24,31 @@ hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 title('Doppler Frequency vs. Elevation angle for 180deg Transmitter Azimuth');
+
+% %Rx position (might not be needed)
+% Rx_z = Altitude - 2;
+% Rx_y = 7;
+% Rx_x = 0;
+% Receiver = [Rx_x, Rx_y, Rx_z];
+% 
+% Blade_rotation_update = 2*pi/(900 -1);
+% mRotation = [cos(Blade_rotation_update),-sin(Blade_rotation_update);sin(Blade_rotation_update),cos(Blade_rotation_update)];
+% Blade_points = zeros(3,100);
+% Blade_points(1,:) = 0:7.5/(100 -1):7.5;
+% Blade_points(3,:) = Altitude;
+% 
+% for r = Tx_radius
+%     for Blade_angle = 0:900
+%         for i = 1:length(Blade_points)
+%            temp = mRotation*[Blade_points(1,i);Blade_points(2,i)];
+%            Blade_points(1,i) = temp(1);
+%            Blade_points(2,i) = temp(2);
+%            
+%         end
+%         
+%     end
+%     %reset blade
+%     Blade_points = zeros(3,100);
+%     Blade_points(1,:) = 0:7.5/(100 -1):7.5;
+%     Blade_points(3,:) = Altitude;
+% end

### 2016-10-11 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -28,3 +28,17 @@ xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
 
+ i = 0.01:.01:7;
+ el = fliplr(atan(2./i));
+ v = ((2*pi)/60)*RPM*2;
+ max_fd = 2*(v*fc)/c;
+ doppler_plus = max_fd.*cos(el);
+ doppler_minus = -max_fd.*cos(el);
+ figure;
+ hold on
+ plot(360*el/(2*pi),doppler_plus)
+ plot(360*el/(2*pi),doppler_minus)
+ hold off
+ xlabel('Elevation Angle (deg)');
+ ylabel('Doppler Frequency (Hz)');
+ title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth new');

### 2016-10-11 Thesis MATLAB Scripts/range_envelope_y.m

@@ -1,0 +1,12 @@
+%clear;
+data_y = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_Max_Doppler_range_y_nMethod.csv');
+
+figure;
+hold on
+plot(data_y(:,1), data_y(:,2));
+plot(data_y(:,1), data_y(:,3));
+hold off
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth at 180deg');
+xlabel('range m');
+ylabel('Doppler Frequency (Hz)');

### 2016-10-11 Thesis MATLAB Scripts/signal_analysis.m

@@ -52,6 +52,7 @@ for i=1:num_files
     upper_envelope = smooth(upper_envelope,.02);
     
     figure;
+    
     hold on
     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
@@ -62,7 +63,7 @@ for i=1:num_files
     view(2)
     title(files(i).name);
     hold off
-    
+%     
 %     upper_envelope_table(i,:) = upper_envelope;
 %     lower_envelope_table(i,:) = lower_envelope;
     

### 2016-10-11 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
 num_files = length(files);
-data = zeros(num_files,479000); %959000;
+data = zeros(num_files,959006); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -19,7 +19,8 @@ RPM = 250;
 Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 50;
+tx_range = 200;
+pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
 %Find Doppler Envelopes
@@ -29,6 +30,9 @@ tx_range = 50;
 %data = circshift(data,31,1);
 
 data_table = zeros(num_files,3);
+
+location_data = data(:,1:6);
+data = data(:,7:end);
 
 for i=1:num_files
     [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
@@ -82,7 +86,14 @@ lower = data_table(:,2);
 correct_fd = zeros(1,length(upper));
 
 %difference calc
-difference = data_table(:,1) + data_table(:,2);
+difference = data_table(:,1) - abs(data_table(:,2));
+
+%correct for pitch
+zero_correct = max(difference) - abs(min(difference));
+if(zero_correct > .1*max(difference))
+    difference = difference - ((zero_correct/2));
+    pitch_corrected = 1;
+end
 
[…]

### 2016-10-11 Thesis MATLAB Scripts/test_cwt.m

@@ -1,0 +1,4 @@
+clear;
+w = 0:(2*pi/(41-1)):2*pi;
+sig = 20*cos(w);
+plot(sig)

### 2016-10-13 Background.tex
updated references and doppler frequency calculation.

@@
 2007) to determine the rotation rate of the main and tail rotor blades using the wavelet transform.
+Other types of aircraft produce modulations on a returned RADAR pulse, one type known as Jet Engine Modulation (JEM) is the product of a RADAR pulse reflecting off the jet engine blades (RADAR HANDBOOK).
+The information can similarly be used to quantify physical aspects of the aircraft when present in order to perform classification.
 
-The doppler shifted signal effects the performance of common adaptive GPS anti-jamming algorithms located on a helicopter platform, unless the covariance estimation is completed within a few milliseconds.
-In iterative approaches the non-stationary signal characteristics cause degradation as well (F.
+The doppler shifted signal caused by RBM effects the performance of common adaptive GPS anti-jamming algorithms located on a helicopter platform, unless the covariance estimation is completed within a few milliseconds.
+And in iterative based approaches the non-stationary signal characteristics cause degradation as well (F.
 Barbiero 2009).
 The affect of RBM on the BER of communications is examined in (Yaman Zhang 2000).
-Where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in their model.
+Where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in the model.
 
-The role of RBM is based on the specific doppler shift associated with where a dominant reflection occurs along the length of the of the blade, and the associated elevation angle of the transmitter.
-The modulated signal will then be used to create a mapping between the amount of doppler present and the distance of a transmitter on the ground.
+The role of RBM in this thesis is based on specific doppler shifts associated with where a dominant reflection occurs along the length of the blade, and the associated elevation angle of the transmitter.
+The received signal is then be used to create a mapping between the amount of doppler present and the position of the transmitter on the ground.
 

### 2016-10-13 Radio_Propagation_Simulation.tex
updated references and doppler frequency calculation.

@@
 The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect.
-They are all formally established models described in full in (Bertoni, 2000; Blaunstein, 2000; Griffiths, 1987)(FIND OTHERS).
+They are all formally established models described in full in (Bertoni, 2000; Parsons, 2000; Willis, 1991)(OK).
 Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.
@@
 
+\subsubsection{Diffuse Reflection}
+A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (J.
+Lambert, "Photometria Sive de Mensura et Gradibus Luminus Colorum et Umbrae", 1760).
+The hemisphere is located at the point of the ray hit, producing rays away from the surface.
+To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
+There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(Phong, 1998)(OK).
+This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces.
+Since is was not designed for longer wavelengths used in RF communications an assumption is made that small scale features of the surface, relevant to light waves,  produce a reflectance distribution similar for larger wavelengths.
+
+%The BRDF parameters were then selected to be frequency independent to form a plausible reflectance distribution for the physical effects.
+
 %multipath fading
-\subsection{Frequency-selective Fading}
+\subsection{Fading}
 The transmitted signal power experiences fading described by
@@
 
-\subsubsection{Diffuse Reflection}
-A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (J.
-Lambert, "Photometria Sive de Mensura et Gradibus Luminus Colorum et Umbrae", 1760).
-The hemisphere is located at the point of the ray hit, producing rays away from the surface.
-To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
-There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(Phong, 1998)(OK).
-This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces.
-Since is was not designed for longer wavelengths used in RF communications an assumption is made that small scale features of the surface, relevant to light waves,  produce a reflectance distribution similar for larger wavelengths.
-
-%The BRDF parameters were then selected to be frequency independent to form a plausible reflectance distribution for the physical effects.
-
 \subsection{Doppler Effect}
 %define doppler effect
-The Doppler effect is characterized by
+The Doppler effect is characterized by (FIX Update to Bistatic Doppler)
 

### 2016-10-13 Ray_Tracing_Software.tex
updated references and doppler frequency calculation.

@@
 after all the data is read into MATLAB the data can be split into two vectors, one pertaining to the physical simulation parameters and the other to the received signal.
+
+There are several templates for simulation execution in the main.c file that are commented out to help get started, depending on the execution environment the generation of a single file can take anywhere from a few minuets to several days.
+Under the defaults provided a single file can be generated in approximately 15min.

### 2016-10-13 Results_new.tex
updated references and doppler frequency calculation.

@@
 Comparing the envelope difference of no pitch and pitched blade, in figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
-Therefore we can first correct this by re-centering the pitch difference to be located around zero.
+Therefore we can first correct this by re-centering the pitch difference according to
 
 \begin{equation}
-	A_{shift} = \frac{Max(EnvelopeDifference) - |Min(EnvelopeDifference)|}{2}
+	A_{shift} = \frac{Max(Max Uppe rEnvelope) - |Min(Min Lower Envelope)|}{2}
 	\label{eqn:pitch_shift}
 \end{equation}
+
+where $A_{shift}$ is the amount that the difference calculation will be shifted down
 
@@
 Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with the a priori information that the cosign should be one period in length.
-These corrections result in the percent azimuth error of 10\% and 6.5\% elevation angle error.
-The error in the azimuth is quite large compared to the results when pitch is 0\textdegree but the sample is only comprised of 41 points which turns out to be 9\textdegree per sample in which 10\% error would be off by one sample.
-Increasing the samples per revolution would most likely decrease this error.
+These corrections result in the percent azimuth error of 0\% and 7\% elevation angle error.
 The elevation angle percent error is within a useable range but could be decreased with further tuning to the preliminary pitch adjustment algorithm.
+When the pitch corrections are applied to a transmitter elevation angle of 26.56\textdegree \space the correction achieves better performance than the unpitched calculation with percent azimuth error of 0\% and percent elevation error of 0.114\%.
+This is still a preliminary correction method that requires more in depth analysis but from the initial results shows merit.
+The increased accuracy as the elevation angle decreases relates back to figure \ref{fig:pitch_tx_elevation_angle} where as the elevation angle decreases the effect of pitch on the signal converges back to unpitched results.

### 2016-10-13 Simulation.tex
updated references and doppler frequency calculation.

@@
 
+Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space, 90\textdegree \space, 180\textdegree \space, and 270\textdegree \space and their simulated counterparts shown in figure \ref{fig:verify}.
+
+\begin{figure}
+\centering
+	\subfloat[0\textdegree]{
+	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_0deg.eps}
+	}
+	\subfloat[90\textdegree]{
+	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_90deg.eps}
+	}
+	\newline
+	\subfloat[180\textdegree]{
+	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_180deg.eps}
+	}
+	\subfloat[270\textdegree]{
+	\includegraphics[width=7cm]{images/simulation/elevation_angle_max_doppler_270deg.eps}
+	}
+\caption{Doppler Profile vs. Transmitter Elevation angle for various Azimuth angles.}
+\label{fig:verify}
+\end{figure}
+
 The effect of elevation angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_elevation_angle_estimation}.

### 2016-10-13 Thesis MATLAB Scripts/Envelope.m

@@ -1,10 +1,11 @@
 %envelope calculation
 clear;
-
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/test_locationdatainfile_4.csv');
+%test_locationdatainfile_4
+%Altitude_200m/rx_test_Bistatic_dop0.000000rad2
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rx_test_Bistatic_dop0.000000rad3.csv');
 rpm = 250;
 
-B = horzcat(samples,samples)';
+%B = horzcat(samples,samples)';
 
 % altitude = samples(1);
 % tx_x = samples(2);
@@ -62,10 +63,5 @@ colormap(jet);
 colorbar
 view(2)
 
-% f0 = 5/(2*pi);
-% DT = 1/4000;
-% t = 0:DT:(numel(samples)*DT)-DT;
-% scales = helperCWTTimeFreqVector(1,2e3,f0,DT,32);
-% cwtsig = cwtft({samples,DT},'wavelet','bump','scales',scales);
-% helperCWTTimeFreqPlot(cwtsig.cfs,t.*1e6,cwtsig.frequencies./1000,...
-%     'surf','Bat Echolocation (CWT)','Microseconds','kHz')
+figure;
+periodogram(samples,rectwin(length(samples)),length(samples),fs,'centered')

### 2016-10-13 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_400m2/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_400m2/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -19,7 +19,7 @@ RPM = 250;
 Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 200;
+tx_range = 400;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -89,9 +89,9 @@ correct_fd = zeros(1,length(upper));
 difference = data_table(:,1) - abs(data_table(:,2));
 
 %correct for pitch
-zero_correct = max(difference) - abs(min(difference));
+zero_correct = max(data_table(:,1)) - abs(min(data_table(:,2)));
 if(zero_correct > .1*max(difference))
-    difference = difference - ((zero_correct/2));
+    difference = difference - (zero_correct/1);
     pitch_corrected = 1;
 end
 
@@ -107,7 +107,7 @@ end
 %for pitch correction
 if(pitch_corrected)
     w = 0:(2*pi/(num_files-1)):2*pi;
-    correct_fd = correct_fd + (zero_correct/2 + .1*zero_correct)*cos(w);
+    correct_fd = correct_fd + (zero_correct/2)*cos(w);
 end
 
 [Min,Imin] = min(correct_fd);

### 2016-10-14 Background.tex
added bib and modified for bistatic doppler calculation.

--- 2016-09-29 Background.tex
@@
 The rotating blades of the helicopter modulate signals that hit the blades by reflecting them.
-The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point (refs?).
+The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point \cite{YiminZhang2000}.
 The rotor blade modulation (RBM) has a complex form and is influenced by several object parameters.
-These parameters range from the positioning of a signal source to the physical dimensions of the blades.
-The resulting modulated signal has been used in radar applications relating to the classification of any aircraft with a rotor blade, propeller or even jet engines (refs?).
-The doppler shifted signal has also been shown to have a parasitic effect on GPS anti-jamming algorithms (refs?).
-The role of RBM is based on the specific doppler shift associated with where a dominant reflection occurs along the length of the of the blade, and the associated elevation angle of the transmitter.
-The modulated signal will then be used to create a mapping between the amount of doppler present and the distance of a transmitter on the ground.
+These parameters range from the positioning of a signal source to the physical dimensions of the rotor blades.
+
+The resulting modulated signal has been used in several RADAR applications.
+First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in \cite{Bullard1991} that defines a specific signature for physical parameters of a helicopter.
+The ability to detect a hovering helicopter based on the blade flashes caused by reflected RADAR pulses off the blades is examined in \cite{Misiurewicz1997} where they used information the time domain to determine if a helicopter was hovering.
+The micro-doppler produced by the RADAR reflection in \cite{Thayaparan2007} is used to determine the rotation rate of both the main and tail rotor blades using the wavelet transform.
+Other types of aircraft produce modulations on a returned RADAR pulse, one type known as Jet Engine Modulation (JEM) is the product of a RADAR pulse reflecting off the jet engine blades \cite{NavalAirSystemsCommand1999}.
+The information can similarly be used to quantify physical aspects of the aircraft when present in order to perform classification.
+
+The doppler shifted signal caused by RBM is shown in \cite{F.BarbieroF.VincentT.Deloues2014} to effect the performance of common adaptive GPS anti-jamming algorithms located on helicopter platforms.
+They were able to mitigate the effects by estimating the covariance within a few milliseconds but this comes at an extreme computation overhead.
+And for iterative based anti-jamming approaches the non-stationary signal characteristics cause degradation as well.
+The affect of RBM on the BER of communications is examined in \cite{YiminZhang2000} where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in the model.
+
+The role of RBM in this thesis is based on specific doppler shifts associated with where a dominant reflection occurs along the length of the blade, and the associated elevation angle of the transmitter.
+The received signal is then used to create a mapping between the amount of doppler present and the position of the transmitter on the ground.
 
@@
 There are three physical objects within this scene.
-The first is the Rotor blade which is the dark green bar depicted in the figure, next are the transmitter in green $T_x$ and the receiver $R_x$ in blue.
+The first is the Rotor blade which is the dark green bar depicted in the figure, next are the transmitter in green $Tx$ and the receiver $Rx$ in blue.
 The measurements depicted as black bars with denoting start and stop points reference the various distances used in the following equations.

### 2016-10-14 Radio_Propagation_Simulation.tex
added bib and modified for bistatic doppler calculation.

@@
 The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions.
-The ray tracing engine uses recursive execution described in (Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
+The ray tracing engine uses recursive execution described in \cite{Whitted1979}(Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
 
@@
 The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect.
-They are all formally established models described in full in (Bertoni, 2000; Parsons, 2000; Willis, 1991)(OK).
+They are all formally established models described in full in \cite{Bertoni1999}, \cite{Parsons2000}, and \cite{Willis2005} (Bertoni, 2000; Parsons, 2000; Willis, 1991)(OK).
 Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.
@@
 The hemisphere is located at the point of the ray hit, producing rays away from the surface.
-To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
-There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation(Phong, 1998)(OK).
+To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007}, \cite{Pharr2010}, \cite{Glassner1995} (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
+There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980} (Phong, 1998)(OK).
 This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces.
@@
 %define doppler effect
-The Doppler effect is characterized by (FIX Update to Bistatic Doppler)
+The Doppler effect is characterized by
 
@@
 \begin{equation}
-	f = f_0 + \frac{2\Delta v}{\lambda} %reradiated after reflection...
+	f = f_0 + \frac{v_t + v_r}{\lambda} %reradiated after reflection
 	\label{eqn:observedShift}	
@@
 
-where $f_0$ is the initial transmitted frequency, $lambda$ is the wavelength, and $\Delta v$ is the difference in velocity.
+where $f_0$ is the initial transmitted frequency, $lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection.
+This is similar to the Bistatic RADAR equation for doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
 
@@
 \begin{equation}
-	\Delta v = r \omega_r (\vec{d_p} \bullet \vec{d_r})
-	\label{eqn:deltav}
+	v_t = r \omega_r (\vec{d_p} \bullet \vec{d_t})
+	\label{eqn:v_t}
 \end{equation}
@@
 %formula description
-where $\Delta v$ is the difference in velocity between the point of reflection along the length of the rotor blade in the direction of the reflection characterized by equation \ref{eqn:deltav}.
-Where $r$ is the radius along the length of the blade where the reflection occurs.
+where $r$ is the radius along the length of the blade where the reflection occurs.
 $\omega_r$ is the angular velocity of the rotor.
-$\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_r}$ is the normalized vector that is in the direction of the resulting reflected ray.
+$\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_t}$ is the normalized vector that is in the direction of the transmitted ray.
+
+\begin{equation}
+	v_r = r \omega_r (\vec{d_p} \bullet \vec{d_r})
+	\label{eqn:v_r}
+\end{equation}
+
+where $\vec{d_r}$ is the normalized vector that is in the direction of the reflected ray.
 
@@
 The ray tracing simulation is conducted in the Monte Carlo fashion acting on the scene and propagation models.
-This method of raytracing is established for creating realistic images in (Suffern, 2007; Pharr, 2010).
+This method of raytracing is established for creating realistic images in \cite{Suffern2007}, \cite{Pharr2010} (Suffern, 2007; Pharr, 2010).
 The simulation is performed over successive iterations.

### 2016-10-14 Simulation.tex
added bib and modified for bistatic doppler calculation.

@@
 
-Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space, 90\textdegree \space, 180\textdegree \space, and 270\textdegree \space and their simulated counterparts shown in figure \ref{fig:verify}.
+Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space \ref{fig:3D_model_0az_doppler}, 90\textdegree \space \ref{fig:3D_model_90az_doppler}, 180\textdegree \space \ref{fig:3D_model_180az_doppler}, and 270\textdegree \space \ref{fig:3D_model_270az_doppler} and their simulated counterparts shown in figure \ref{fig:verify}.
+We see that the ray traced results match their projections on the maximum and minimum envelope doppler as transmitter elevation angle changes.
+The doppler values do not match exactly but the trends are very similar with exception to the 90\textdegree \space result.
+This discrepancy can be explained in the doppler offset of the other graphs in figure \ref{fig:verify}, where they should start at 0Hz they are shifted up to about 200Hz.
+This shift overshadows the doppler information when the transmitter is located at 90\textdegree \space and the result is not shifted up because the reflection angle is restricted limiting the maximum available doppler.
 

### 2016-10-14 Thesis MATLAB Scripts/Envelope.m

@@ -2,7 +2,7 @@
 clear;
 %test_locationdatainfile_4
 %Altitude_200m/rx_test_Bistatic_dop0.000000rad2
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rx_test_Bistatic_dop0.000000rad3.csv');
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rx_test_Bistatic_dop0.000000rad2.csv');
 rpm = 250;
 
 %B = horzcat(samples,samples)';
@@ -29,18 +29,20 @@ SNR = 50;
 log_power = 10*log10(p);
 [q,nd] = max(10*log10(p));
 
+ave_q = mean(q);
+
 lower_envelope = zeros(length(t),1);
 upper_envelope = zeros(length(t),1);
 
 for i = 1:length(t)
     for j = 1:2500
-        if log_power(j,i) > -70
+        if log_power(j,i) > ave_q
             lower_envelope(i) = f(j);
             break;
         end  
     end
     for j = 2501:5000
-        if (log_power(7501-j,i) > -70) && (log_power(7501-j,i) ~= -inf)
+        if (log_power(7501-j,i) > ave_q) && (log_power(7501-j,i) ~= -inf)
             upper_envelope(i) = f(7501-j);
             break;
         end  
@@ -55,6 +57,8 @@ figure;
 hold on
 plot3(t*1000,smooth(lower_envelope/1e6,.02),z,'b','linewidth',4)
 plot3(t*1000,smooth(upper_envelope/1e6,.02),z,'r','linewidth',4)
+plot3(t*1000,cos(angle_b1(1:end-1)),z);
+plot3(t*1000,cos(angle_b2(1:end-1)),z);
 legend('Lower Envelope','Upper Envelope');
 spectrogram(samples,5000,500,5000,fs_real,'yaxis','centered')
 hold off

### 2016-10-14 Thesis MATLAB Scripts/elevationEstimation_on_data_with_metadata.m

@@ -1,14 +1,14 @@
 %test alg for elevation angle only sweep
 clear;
-
+%data_rangeFar_180deg
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %479000;
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//',files(i).name)));
 end
 
 %--------------------------------------------------------------------------

### 2016-10-14 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_400m2/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_400m2/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -19,7 +19,7 @@ RPM = 250;
 Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 400;
+tx_range = 200;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -70,6 +70,17 @@ for i=1:num_files
    
     data_table(i,1) = max(upper_envelope); 
     data_table(i,2) = min(lower_envelope);
+    
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'b','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'r','linewidth',4)
+%     spectrogram(signal_data(i,:),5000,500,5000,fs,'yaxis','centered')
+%     colormap(jet);
+%     colorbar
+%     view(2)
+%     title(num2str(location_data(i,4)));
+%     hold off
 end
 
 %fix estimation error on first envelope -----
@@ -114,7 +125,7 @@ end
 [Max,Imax] = max(correct_fd);
 
 %peak prominence calc
-min_peak_prominence = (1/(Max - Min))*.1;
+min_peak_prominence = (1/(Max - Min))*.001;
 [pk,lc] = findpeaks(1./correct_fd,'NPeaks',2,'MinPeakProminence',min_peak_prominence);
 
 %double check average power against peaks to fix 90deg

### 2016-10-14 Background.tex
edits to thesis from clarice and modify background to reflect bistatic

@@
 This section details the the basic phenomenon behind rotor blade modulation along with its significance in other applications, and the defining characteristics that allow its use in this application.
-The second part of this section describes the geometric models for the 2 dimensional case and several 3 dimensional cases.
+The second part of this section describes the geometric models for the 2-Dimensional (2D) case and several 3D cases.
 These models will form the basis for verification of the simulations.
@@
 The rotating blades of the helicopter modulate signals that hit the blades by reflecting them.
-The reflected signal, through the doppler effect, become shifted in frequency in relationship to the velocity of the reflection point \cite{YiminZhang2000}.
-The rotor blade modulation (RBM) has a complex form and is influenced by several object parameters.
+The reflected signal, through the Doppler effect, become shifted in frequency in relationship to the velocity of the reflection point \cite{YiminZhang2000}.
+The RBM has a complex form and is influenced by several object parameters.
 These parameters range from the positioning of a signal source to the physical dimensions of the rotor blades.
 
-The resulting modulated signal has been used in several RADAR applications.
+The resulting modulated signal has been used in several radar applications.
 First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in \cite{Bullard1991} that defines a specific signature for physical parameters of a helicopter.
-The ability to detect a hovering helicopter based on the blade flashes caused by reflected RADAR pulses off the blades is examined in \cite{Misiurewicz1997} where they used information the time domain to determine if a helicopter was hovering.
-The micro-doppler produced by the RADAR reflection in \cite{Thayaparan2007} is used to determine the rotation rate of both the main and tail rotor blades using the wavelet transform.
-Other types of aircraft produce modulations on a returned RADAR pulse, one type known as Jet Engine Modulation (JEM) is the product of a RADAR pulse reflecting off the jet engine blades \cite{NavalAirSystemsCommand1999}.
+The ability to detect a hovering helicopter based on the blade flashes caused by reflected radar pulses off the blades is examined in \cite{Misiurewicz1997} where they used information the time domain to determine if a helicopter was hovering.
+The micro-Doppler produced by the radar reflection in \cite{Thayaparan2007} is used to determine the rotation rate of both the main and tail rotor blades using the wavelet transform.
+Other types of aircraft produce modulations on a returned radar pulse, one type known as Jet Engine Modulation (JEM) is the product of a radar pulse reflecting off the jet engine blades \cite{NavalAirSystemsCommand1999}.
 The information can similarly be used to quantify physical aspects of the aircraft when present in order to perform classification.
 
-The doppler shifted signal caused by RBM is shown in \cite{F.BarbieroF.VincentT.Deloues2014} to effect the performance of common adaptive GPS anti-jamming algorithms located on helicopter platforms.
+The Doppler shifted signal caused by RBM is shown in \cite{F.BarbieroF.VincentT.Deloues2014} to effect the performance of common adaptive Global Positioning System (GPS) anti-jamming algorithms located on helicopter platforms.
 They were able to mitigate the effects by estimating the covariance within a few milliseconds but this comes at an extreme computation overhead.
 And for iterative based anti-jamming approaches the non-stationary signal characteristics cause degradation as well.
-The affect of RBM on the BER of communications is examined in \cite{YiminZhang2000} where effects of multi path and doppler cause large bit error rates at small elevation angles and large scattering coefficients described in the model.
+The affect of RBM on the Bit Error Rate (BER) of communications is examined in \cite{YiminZhang2000} where effects of multipath and Doppler cause large BER values at small elevation angles and large scattering coefficients described in the model.
 
-The role of RBM in this thesis is based on specific doppler shifts associated with where a dominant reflection occurs along the length of the blade, and the associated elevation angle of the transmitter.
-The received signal is then used to create a mapping between the amount of doppler present and the position of the transmitter on the ground.
+The role of RBM in this thesis is based on specific Doppler shifts associated with where a dominant reflection occurs along the length of the blade, and the associated elevation angle of the transmitter.
+The received signal is then used to create a mapping between the amount of Doppler present and the position of the transmitter on the ground.
 
 \section{Geometric Models}
-The geometric model will begin with a two dimensional scene that will describe the geometry between the rotor blade, the transmitter and the receiver.
-Then the model will evolve into a selection of three dimensional models that will form the foundation for the results of the ray tracer.
+The geometric model will begin with a 2D scene that will describe the geometry between the rotor blade, the transmitter, and the receiver.
+Then the model will evolve into a selection of 3D models that will form the foundation for the results of the ray tracer.
 
@@
 %might want this one to define some parameters but then show what happens when directly over.
-The two dimensional geometric mode is based on a few assumptions, one is that the receiver is placed as close as possible to the center of rotation, and second that all the physical objects are located within a single 2D plane.
-This model is represented in figure \ref{fig:2D_model}.
+The 2D geometric mode is based on a few assumptions, first that the receiver is placed as close as possible to the center of rotation, and second that all the physical objects are located within a single 2D plane.
+This model is represented in Figure \ref{fig:2D_model}.
 
@@
 There are three physical objects within this scene.
-The first is the Rotor blade which is the dark green bar depicted in the figure, next are the transmitter in green $Tx$ and the receiver $Rx$ in blue.
-The measurements depicted as black bars with denoting start and stop points reference the various distances used in the following equations.
+The first being the rotor blade, which is the dark green bar depicted in the figure.
+Next is the transmitter $Tx$, in green, and the receiver $Rx$ in blue.
+The measurements, depicted as black bars with denoting start and stop points, reference the various distances used in the following equations.
 The dashed green line shows at which altitude the helicopter is hovering at, and the red dashed line transverses the transmitter and the center of rotation for the blades.
@@
 %formulate the geometric equations
-(equations for doppler profile)
+\begin{equation}
+	f_d = -f_{DopplerMax}cos(\theta_{El})cos(\theta_{b})
+	\label{eq:dop_theory_blade}
+\end{equation}
+
+where $f_d$ is the Doppler frequency shift, $f_{DopplerMax}$ is described by equation \ref{eqn:fd_max} as the maximum amount of Doppler shift possible, $\theta_{El}$ is the elevation angle of the transmitter with respect to the rotor blades, and $\theta_{b}$ is the current angle of the rotor blade.
 
@@
 
-Figure \ref{fig:2D_theoretical_doppler} shows the varying doppler frequency caused by the RBM at various elevation angles of the transmitter.
-The results of this is a sinusoidal doppler profile in which its amplitude increases as the elevation angle decreases.
+Figure \ref{fig:2D_theoretical_doppler} shows the varying Doppler frequency caused by the RBM at various elevation angles of the transmitter.
+The results of this is a sinusoidal Doppler profile in which the amplitude increases as the elevation angle decreases.
 
@@
 Since this model has the receiver located at the axis of rotation this model can be seen as a special case of the next 3D models, this is because it is symmetric around the axis of rotation.
-Therefore any placement of the transmitter in 3D space can be distilled down to a 2D profile as such.
+Therefore, any placement of the transmitter in 3D space can be distilled down to a 2D profile as such.
 This symmetry should then be mirrored in the ray tracing simulation as verification.
@@
 \subsection{3D Geometric Model}
-The three dimensional geometric model is categorized by the position of the rotor blade and the position of the signal source.
-Since the rotor blade has a specific airfoil shape the models will take that into account through an approximation of that surface.
-The first model will be representative of having the transmitter inline with both the receiver and the blade, with the transmitter in both fore and aft positions.
+The 3D geometric model is categorized by the position of the rotor blade and the position of the signal source.
+Since the rotor blade has a specific airfoil shape, the models will take that into account through an approximation of that surface.
+The first model will be representative of having the transmitter in-line with both the receiver and the blade, with the transmitter in both fore and aft positions.
 The next model will have the rotor approaching both the receiver and transmitter, and lastly the rotor will be receding from both the receiver and transmitter.
@@
 
-\subsubsection{Transmitter inline with Receiver and Rotor Blade}
+\subsubsection{Transmitter in-line with Receiver and Rotor Blade}
 %go over the 3d model for the tx inline with blade fore and aft
-The first two models as mentioned above fall under the criteria of the transmitter being inline with both the rotor blade and the offset receiver.
+The first two models as mentioned above fall under the criteria of the transmitter being in-line with both the rotor blade and the offset receiver.
 
-Figure \ref{fig:3D_model_90az} depicts the transmitter at a 90\textdegree \space azimuth angle, which places it inline with the position of the receiver and the current location of the rotating blades.
+Figure \ref{fig:3D_model_90az} depicts the transmitter at a 90\textdegree \space azimuth angle, which places it in-line with the position of the receiver and the current location of the rotating blades.
 
@@
 
+The equation for modeling the scenario for a transmitter located at 90\textdegree \space azimuth is
+
 %formulate the geometric equations
-(equations doppler profile 90 deg)
+\begin{equation}
+	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{Limited})
+	\label{eq:theory_90_upper}
+\end{equation}
+
+and
+
+\begin{equation}
+	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{Limited})
+	\label{eq:theory_90_lower}
+\end{equation}
+
+where $MaxUpperEnvelope$ is an array of the maximum upper envelope values for each elevation sample, $MinLowerEnvelope$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range due to
+
+\begin{equation}
+	\theta_{Limited} = atan\left(\frac{Rx_z}{(BladeLength - Rx_y)}\right)
+	\label{eq:theory_90_limited}
+\end{equation}
+
+where $Rx_z$ is the receivers position below the rotor head, $BladeLength$ is the length of the rotor blade, and $Rx_y$ is the receivers position on the Y axis.
 
@@
 
-Figure \ref{fig:3D_model_90az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 90\textdegree.
+Figure \ref{fig:3D_model_90az_doppler} shows the maximum and minimum Doppler values versus elevation angle for a transmitter at an azimuth angle of 90\textdegree.
 The elevation angle is limited by the reflection angle, caused by the limited distance between the tip of the blade and the location of the receiver.
-This limitation constrains the doppler profile causing inaccurate transmitter elevation estimation at this transmitter azimuth position.
+This limitation constrains the Doppler profile causing inaccurate transmitter elevation estimation at this transmitter azimuth position.
 
-Figure \ref{fig:3D_model_270az} depicts the transmitter at a 270\textdegree \space azimuth angle, which places it inline with the position of the receiver and the current location of the rotating blades.
-This placement of the transmitter behind the helicopter is different from the situation in figure \ref{fig:3D_model_90az} because the value of $\theta_r$ is now not limited by the tip of the rotor and can go to smaller elevation angles.
+Figure \ref{fig:3D_model_270az} depicts the transmitter at a 270\textdegree \space azimuth angle, which places it in-line with the position of the receiver and the current location of the rotating blades.
+This placement of the transmitter behind the helicopter is different from the situation in Figure \ref{fig:3D_model_90az} because the value of $\theta_r$ is now not limited by the tip of the rotor and can go to smaller elevation angles.
 
@@
 %formulate the geometric equations
-(equations doppler profile 270 deg)
+The equation for modeling the scenario for a transmitter located at 270\textdegree \space azimuth is similar to the equations for calculating the 90\textdegree \space scenario, the limiting factor is now the reflection radius, because as the transmitter moves farther away the elevation angle is increasing but the reflection radius gets smaller.
 
@@
 
-Figure \ref{fig:3D_model_270az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 270\textdegree.
-The data from the figure is similar to the data from the previous figure \ref{fig:3D_model_90az} but does not exhibit the limitation on the reflection angle, allowing for smaller elevation angles and larger doppler shifts to occur.
+Figure \ref{fig:3D_model_270az_doppler} shows the maximum and minimum Doppler values versus elevation angle for a transmitter at an azimuth angle of 270\textdegree.
+The data from the figure is similar to the data from the previous Figure \ref{fig:3D_model_90az} and even though it is not limited on elevation angle the consequence is a limited reflection radius.
+
+%but does not exhibit the limitation on the reflection angle, allowing for smaller elevation angles and larger Doppler shifts to occur.
 
@@
 %go over the 3d model for the approaching blade
-The approaching model shown in figure \ref{fig:3D_model_180az} depicts the transmitter at an azimuth of 180 \textdegree \space and the axis of X has now been rotated to be -X.
-The direction of the rotor blades is depicted ,in green, to follow the previous assumptions.
+The approaching model shown in Figure \ref{fig:3D_model_180az} depicts the transmitter at an azimuth of 180\textdegree \space and the axis of X has now been rotated to be -X.
+The direction of the rotor blades is depicted, in green, to follow the previous assumptions.
 
 %describe the situation and the position of the objects
-This case of the 3D model places the transmitter at 180 \textdegree \space so that the oncoming blades move toward both the receiver and the transmitter at the same time.
-This particular placement will cause a positive doppler profile because the blades will be moving in the direction of both objects, compressing the reflected wave accordingly.
+This case of the 3D model places the transmitter at 180\textdegree \space so that the oncoming blades move toward both the receiver and the transmitter at the same time.
+This particular placement will cause a positive Doppler profile because the blades will be moving in the direction of both objects, compressing the reflected wave accordingly.
 
@@
 
+The equation for modeling the scenario for a transmitter located at 180\textdegree \space azimuth is
+
 %formulate the geometric equations
-(equations doppler profile 180 deg)
+\begin{equation}
+	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{El})
+	\label{eq:theory_180_upper}
+\end{equation}
+
+and the MinLowerEnvelope is set to 0 for the range.
 
@@
 
-Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree.
-The data from the figure shows the maximum of the doppler profile decrease as the elevation angle gets larger.
+Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree.
+The data from the figure shows the maximum, of the Doppler profile, decrease as the elevation angle gets larger.
 
@@
 %go over the 3d model for the receding blade
-The receding model shown in figure \ref{fig:3D_model_0az} depicts the transmitter at an azimuth of 0 \textdegree \space where the axis positions back to their original places and the direction of the rotor blade is now depicted in red.
+The receding model shown in Figure \ref{fig:3D_model_0az} depicts the transmitter at an azimuth of 0\textdegree \space where the axis positions back to their original places and the direction of the rotor blade is now depicted in red.
 
 %describe the situation and the position of the objects
-This case of the 3D model places the transmitter at 0 \textdegree \space so that the receding blades move away from both the receiver and the transmitter at the same time.
-This particular placement should provide a negative doppler profile because the blades will be moving in the opposite direction of both objects, stretching the reflected wave accordingly.
+This case of the 3D model places the transmitter at 0\textdegree \space so that the receding blades move away from both the receiver and the transmitter at the same time.
+This particular placement should provide a negative Doppler profile because the blades will be moving in the opposite direction of both objects, stretching the reflected wave accordingly.
 
@@
 
+The equation for modeling the scenario for a transmitter located at 0\textdegree \space azimuth is
+
 %formulate the geometric equations
-(equations doppler profile 0 deg)
+\begin{equation}
+	MinLowerEnvelope = f_{DopplerMax}cos(\theta_{El})
+	\label{eq:theory_0_lower}
+\end{equation}
+
+and the MaxUpperEnvelope is set to 0 for the range.
 
@@
 
-Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum doppler values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree.
-The data from the figure shows the minimum of the doppler profile increase as the elevation angle gets larger.
+Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree.
+The data from the figure shows the minimum of the Doppler profile increase as the elevation angle gets larger.

### 2016-10-14 Introduction.tex
edits to thesis from clarice and modify background to reflect bistatic

@@
 The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the elevation angle between the axis of rotation and the emitter.
-RBM can be used in RADAR to detect and classify aircraft based on a specific signature and can degrade communication system located on the rotorcraft itself.
+RBM can be used in radar to detect and classify aircraft based on a specific signature and can degrade communication system located on the rotorcraft itself.
 The motivation behind this work is to use the RBM effect to locate uncooperative emitters on the ground.
@@
 The main contributions of this thesis are as follows.
-A 3D Ray Tracing software is provided to simulate the RF propagation in the presence of a helicopter rotor blade.
+A 3-Dimensional (3D) ray tracing software is provided to simulate the Radio Frequency (RF) propagation in the presence of a helicopter rotor blade.
 The software provides insight into the complex interaction between the rotor blade shape and the placement of the receiver and transmitters.
@@
 Next the objects of the scene model, as well as the dimensionality, are defined in software to be representative of their physical  dimensions and functionality.
-Lastly we describe the core ray tracing engine that traces the scene in successive frames to build the receiver output.
+Lastly, we describe the core ray tracing engine that traces the scene in successive frames to build the receiver output.
 
 In Chapter \ref{ch:simulations} we present the result of the parameter swept simulations of the ray tracing software.
-Next the received signals from the simulation are analyzed using several DSP techniques to define the signal characteristics that will be used in the next chapter for estimation.
+Next the received signals from the simulation are analyzed using several Digital Signal Processing (DSP) techniques to define the signal characteristics that will be used in the next chapter for estimation.
 
@@
 
-In Chapter \ref{ch:conclusion} the summery of the results are detailed along with the current limitations. Lastly future improvements on the work will be discussed.
+In Chapter \ref{ch:conclusion} the results are detailed along with the current limitations. Lastly, future improvements on the work will be discussed.

### 2016-10-14 MSc. Thesis Template.tex
updated references and doppler frequency calculation.
added bib and modified for bistatic doppler calculation.
edits to thesis from clarice and modify background to reflect bistatic

@@
 %\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
-\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
+\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX commentts
 %\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
@@
 \usepackage{doxygen}
+\usepackage{subfig}
 
@@
 \usepackage{cite}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 
@@
 %\clearpage  % Start a new page
-%\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
-%\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
+\lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
+\listofsymbols{ll}  % Include a list of Abbreviations (a table of two columns)
 {
-% \textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
+ %\textbf{Acronym} & \textbf{W}hat (it) \textbf{S}tands \textbf{F}or \\
+ \textbf{2D} & 2-\textbf{D}imensional \\
+ \textbf{3D} & 3-\textbf{D}imensional \\
+ \textbf{BER} & \textbf{B}it \textbf{E}error \textbf{R}ate \\
+ \textbf{BRDF} & \textbf{B}i-directional \textbf{R}eflection  \textbf{D}istrobution \textbf{F}unction \\
+ \textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alue \\
+ \textbf{DSP} & \textbf{D}igital \textbf{S}ignal \textbf{P}rocessing \\
+ \textbf{GPS} & \textbf{G}lobal \textbf{P}ositioning \textbf{S}ystem \\
+ \textbf{GPU} & \textbf{G}raphics \textbf{P}rocessing \textbf{U}nit \\
+ \textbf{GUI} & \textbf{G}raphical \textbf{U}ser \textbf{I}nterface \\
+ \textbf{IQ} & \textbf{I}n-phase and \textbf{Q}uadrature \\
+ \textbf{JEM} & \textbf{J}et \textbf{E}ngine \textbf{M}odulation \\
+ \textbf{LOS} & \textbf{L}ine \textbf{O}f \textbf{S}ight \\
+ \textbf{RBM} & \textbf{R}otor \textbf{B}lade \textbf{M}odulation \\
+ \textbf{RF} & \textbf{R}adio \textbf{F}requency \\
+ \textbf{RPM} & \textbf{R}otations \textbf{P}er \textbf{M}inute \\
+ \textbf{Rx} & \textbf{R}eceiver \\
+ \textbf{STFT} & \textbf{S}hort \textbf{T}ime \textbf{F}ourier \textbf{T}ransform \\ 
+ \textbf{Tx} & \textbf{T}ransmitter \\
 
@@
 The reflected signal is Doppler shifted based on where the signal is reflected along the length of the blade as well as the angle between the axis of rotation and the emitter.
-RBM is known to degrade the performance of RF communications on rotorcraft and can be used in RADAR applications to detect and classify aircraft, but there is little on its usefulness in other areas.
+RBM is known to degrade the performance of RF communications on rotorcraft and can be used in radar applications to detect and classify aircraft, but there is little on its usefulness in other areas.
 This thesis looks at the ability to utilize the RBM phenomenon on the rotorcraft itself to geo-locate and track a signal emitter on the ground.
@@
 \bibliographystyle{IEEEtran}  % Use the "unsrtnat" BibTeX style for formatting the Bibliography
-%\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
+\bibliography{Bibliography}  % The references (bibliography) information are stored in the file named "Bibliography.bib"
 

### 2016-10-14 Radio_Propagation_Simulation.tex
edits to thesis from clarice and modify background to reflect bistatic

@@
 The model used is based upon classical geometric optics to work with the ray tracing engine.
-The scene model is comprised of a three dimensional environment in order to define the physical rotor blade surface.
+The scene model is comprised of a 3D environment in order to define the physical rotor blade surface.
 The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions.
-The ray tracing engine uses recursive execution described in \cite{Whitted1979}(Whitted, 1979), replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
+The ray tracing engine uses recursive execution described in \cite{Whitted1979}, replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
 
@@
 %define the math behind the physical laws that are simulated within the simulation
-The propagation model defined in this project is based on the following physical phenomena, free-space path loss, reflection, and the doppler effect.
-They are all formally established models described in full in \cite{Bertoni1999}, \cite{Parsons2000}, and \cite{Willis2005} (Bertoni, 2000; Parsons, 2000; Willis, 1991)(OK).
-Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in three dimensional space and because of the assumptions made about the scene model.
+The propagation model defined in this project is based on the following physical phenomena; free-space path loss, reflection, and the doppler effect.
+They are all formally established models described in full in \cite{Bertoni1999}, \cite{Parsons2000}, and \cite{Willis2005}.
+Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in 3D space and because of the assumptions made about the scene model.
 
@@
 %formula description
-where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell's law \ref{eqn:snell}.
+where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell's law
 
@@
 
-The final reflected power is
+The final reflected power is then
 
@@
 %reflection power loss description
-where $P_i$ is the incident power before reflection losses.
+where $P_i$ is the incident power before reflection loss.
 
 \subsubsection{Diffuse Reflection}
-A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere (J.
-Lambert, "Photometria Sive de Mensura et Gradibus Luminus Colorum et Umbrae", 1760).
-The hemisphere is located at the point of the ray hit, producing rays away from the surface.
-To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007}, \cite{Pharr2010}, \cite{Glassner1995} (Suffern, 2007; Pharr, 2010; Glassner, 1995)(OK).
-There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980} (Phong, 1998)(OK).
-This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces.
-Since is was not designed for longer wavelengths used in RF communications an assumption is made that small scale features of the surface, relevant to light waves,  produce a reflectance distribution similar for larger wavelengths.
+A perfect diffuse reflection, also known as Lambertian reflection, will reflect rays in all directions in a uniform hemisphere \cite{Sizun2005}.
+The hemisphere is centered at the point the ray hits, producing rays away from the surface.
+To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007}, \cite{Pharr2010}, \cite{Glassner1995}.
+There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980}.
+This method for the BRDF is regularly used in the rendering of computer graphics to simulate the reflection of light off surfaces and combines the diffuse and specular components.
+Since this was not designed for the longer wavelengths used in RF communications, an assumption is made about surface features.
+Where features relevant to light waves,  produce a reflectance distribution similar for this application.
 
@@
 
-It is assumed that both the receiver and the transmitter are not moving, therefore the only doppler imparted on the signal will be from the rotation of the blades.
+It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades.
 The associated Doppler is calculated using
@@
 
-where $f_0$ is the initial transmitted frequency, $lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection.
-This is similar to the Bistatic RADAR equation for doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
+where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection.
+This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
 
@@
 The scene model is the 3D environment in which the physical objects are placed. 
-The model is comprised of three types of objects, the rotor blades, transmitter and receiver.
+The model is comprised of three types of objects; the rotor blades, transmitter and receiver.
 The rotor blade is the most complex object due to its airfoil shape.
 The transmitter is a point source that projects the rays into the scene, and the receiver is described in a similar fashion with a surrounding boundary layer.
-There are no other objects within the scene, this is because the effect of the rotor on the received signal is to be analyzed for defining characteristics in the best case scenario.
+There are no other objects within the scene.
+This is because the effect of the rotor on the received signal is analyzed for defining characteristics without outside variables.
 
@@
 %go over the shape of the blade
-The rotor blade is the most complex object within the scene due to its airfoil shape.
+The rotor blade is the most complex object within the scene, due to its airfoil shape.
 The airfoil shape is designed to produce lift for the helicopter, and designing one is outside the scope of this project.
-Fortunately there are databases that provide real helicopter airfoil designs in x,y coordinates.
-Theses designs form a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade.
+Fortunately, there are databases that provide real helicopter airfoil designs in x,y coordinates.
+This data forms a 2D cross-section of the airfoil shape that will be extruded into the length of the rotor blade.
 Figure \ref{fig:airfoil} shows the airfoil cross-section that will be used to create the rotor surface.
@@
 The primitive shapes are triangles that span between the ribs and go around to cover the surface.
-This was done using a lightweight mesh generation method using the a priori knowledge of the blade shape.
-The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the blade being composed of rib sections with consistent shape.
+This was done using a lightweight mesh generation method using a priori knowledge of the blade's shape.
+The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the object's uniform structure in 2D.
 The surface normals are then adjusted to match the correct directionality.
@@
 The transmitter is modeled as a point source, this means that all the radio waves are projected from this point into the scene.
-It is assumed that the transmitter is located on the ground within the x,y plane in relation ship to the rotor blades.
+It is assumed that the transmitter is located on the ground within the x,y plane in relationship to the rotor blades.
 The transmitter is configured with a center frequency and is assumed to produce a tone at that frequency.
-Therefor signal produced has no inherent modulation applied to it.
+Therefor, the signal produced has no inherent modulation applied to it.
 %direction creation
-Being that the Transmitter is emitting radio waves into a 3D space it is assumed to be transmitting in an omnidirectional fashion, but because the rotor and the receiver are the only two other objects within the scene radio waves will only be propagated in their direction.
-This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture and eliminates computational overhead for the tracing engine.
+Being that the transmitter is emitting radio waves into a 3D space, it is assumed to be transmitting in an omnidirectional fashion.
+But because the rotor and the receiver are the only two other objects within the scene, radio waves will only be propagated in their direction.
+This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture that eliminates computational overhead for the tracing engine.
 Figure \ref{fig:transmitter_direction} shows the rays, in blue, casted only in the vicinity of the rotor blade and receiver.
@@
 The ray tracing simulation is conducted in the Monte Carlo fashion acting on the scene and propagation models.
-This method of raytracing is established for creating realistic images in \cite{Suffern2007}, \cite{Pharr2010} (Suffern, 2007; Pharr, 2010).
+This method of raytracing is established for creating realistic images in \cite{Suffern2007}, \cite{Pharr2010}.
 The simulation is performed over successive iterations.
-Each iteration is a discrete element called a frame.
-Where each frame will be updated to represent the change in the position of the rotor blade.
+Each iteration is a discrete element called a frame and each frame will be updated to represent the change in the position of the rotor blade.
 
@@
 %flow of the program
-The ray tracing engine first sets up the environment creating the surfaces and placing the objects in the scene.
+The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene.
 Then the number of frames that will be computed.
@@
 The casting technique reduces the computation overhead by limiting the search space.
-It also creates higher resolution result by focusing the limited number of rays in the direction of the other objects shown in figure \ref{fig:samp_method}.
+It also creates a higher resolution result by focusing the limited number of rays in the direction of the other objects shown in figure \ref{fig:samp_method}.
 
@@
 
-When a ray is casted into the scene it has an origin point, a direction vector, a frequency and an initial power level.
+When a ray is casted into the scene it has an origin point, a direction vector, a frequency, and an initial power level.
 The ray then travels through the scene till it encounters another object.
 If there is a collision with the receiver it is recorded.
-If the ray collides with a rotor blade a new ray is calculated based on the normal to the geometric surface.
-The new ray's power is updated as well as an updated frequency since the blade is moving.
+If the ray collides with a rotor blade a new ray is calculated based on the normal of the geometric surface.
+The new ray's power is then updated as well as an updated frequency since the blade is moving.
 The power level is adjusted based on the BRDF of the specific material.
-Due to only the rotor and receiver in the scene, besides the transmitter, rays that are found to hit the rotor the reflection ray is calculated.
-Then the angle between the reflection and a ray between the point of reflection and the receiver is used to create a dedicated ray in that direction with a decayed power and adjusted frequency accordingly.
+Due to only the rotor and receiver being in the scene, rays that are found to hit the rotor are reflected, then a dedicated ray in the direction of the receiver is also calculated with a decayed power and adjusted frequency respective to the reflection.
 
@@
 The received signal data will then be visualized in spectrograms over the length of the simulated time.
-The simulations do not render in real time but creates a CSV file that can then be loaded into MATLAB for signal processing.
+The simulation does not render in real time but instead creates a Comma Separated Value (CSV) file of In-phase and Quadrature (IQ) data that can then be loaded into MATLAB for signal processing.

### 2016-10-14 Ray_Tracing_Software.tex
added bib and modified for bistatic doppler calculation.
edits to thesis from clarice and modify background to reflect bistatic

@@
 The ray tracing software developed during the course of the thesis is written in C++ in an XCode environment, but a generic implementation is provided to run on other operating systems.
-This code is loosely based on the work of Eric Degroot's developed in (Eric's thesis) and implemented some modified base classes developed by him.
+This code is loosely based on the work of Eric Degroot's developed for \cite{Groot2015} and implemented some modified base classes developed by him.
 It is a specific tool for analyzing the affects of rotor blade modulation on a signal tone, it does not provide generic 3D ray tracing in order to optimize the performance for this task.
@@
 
-the other key parameters that define the simulation are shown in table \ref{tab:key_values}
+the other key parameters that define the simulation are shown in Table \ref{tab:key_values}
 
@@
 it is important to separate this data from the signal data before processing the signal.
-The template for this data is shown in table
+The template for this data is shown in Table
 \ref{tab:file_values}.

### 2016-10-14 Results_new.tex
edits to thesis from clarice and modify background to reflect bistatic

@@
 %formulate the estimation equation and discuss ambiguity considerations
-The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which at a set angle a doppler envelope is calculated and subsequent maximum and minimum values are collected.
-After a complete rotation the doppler maximum and minimum values produce a sinusoidal pattern as shown in figure \ref{fig:tx_azimuth_angle_200} without the assumption of knowing the starting azimuth angle.
+The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which a Doppler envelope and subsequent maximum and minimum values are calculated.
+After a complete rotation the Doppler maximum and minimum values produce a sinusoidal pattern as shown in Figure \ref{fig:tx_azimuth_angle_200} without the assumption of knowing the starting azimuth angle.
 With this data we need to find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle.
-To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in figure \ref{fig:azimuth_estimation_max_vs_absMin}.
+To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in Figure \ref{fig:azimuth_estimation_max_vs_absMin}.
 
@@
 
-From figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference \ref{eqn:difference}
+From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference
 
@@
 
-we produce an almost exact sinusoid centered around zero, shown in figure \ref{fig:azimuth_estimation_difference}.
+where $Max Upper Envelope$ is an array of the maximum value of each upper envelope calculation, and $Min Lower Envelope$ is an array of the minimum value of each lower envelope calculation.
+$Envelope Difference$ is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.
 
@@
 
-While figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself, therefore by computing the correct doppler to use from the $Max Upper Envelope$ and the $| Min Lower Envelope |$.
+While Figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself, therefore by computing the correct Doppler using the $Max Upper Envelope$ and the $| Min Lower Envelope |$.
 This is done by evaluating the difference at each angle and if the difference is negative the $| Min Lower Envelope |$ is used and if positive the $Max Upper Envelope$.
@@
 
-The correct Doppler is shown in figure \ref{fig:correct_fd} which displays the amount of doppler that is currently acting on the signal for that specific azimuth angle.
+The correct Doppler is shown in Figure \ref{fig:correct_fd} which displays the amount of Doppler that is currently acting on the signal for that specific azimuth angle.
 The data gathered contains a global minimum at 90\textdegree \space and a second local minimum at 270\textdegree.
@@
 But in order to find the local minimum at 270\textdegree \space we need to use a different method.
-To do this we can use the peak detection function within Matlab to locate both the 90\textdegree and 270\textdegree point.
+To do this we can use the peak detection function within MATLAB to locate both the 90\textdegree \space and 270\textdegree \space point.
 By taking the inverse of the correct Doppler and tuning the peak detection function with the maximum and minimum values to determine accurate prominence.
@@
 
-From figure \ref{fig:peaks}  we see the two peaks denoted by the red x's, one at 90\textdegree \space and the other at  270\textdegree.
-Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space 270\textdegree locations.
+From Figure \ref{fig:peaks}  we see the two peaks denoted by the red x's, one at 90\textdegree \space and the other at  270\textdegree.
+Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space and 270\textdegree \space locations.
 Because it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.
@@
 
-Figure \ref{fig:ave_power}  shows the average power at each angle sample with the angles 90\textdegree \space and 270\textdegree denoted.
+Figure \ref{fig:ave_power}  shows the average power at each angle sample with the angles 90\textdegree \space and 270\textdegree \space denoted as red x's.
 From the plot we can see that the average power at 90\textdegree \space is much smaller than the the power at 270\textdegree, so this inequality will be used to resolve ambiguity in the azimuth angle.
@@
 
-From table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of Altitude and elevation angles that were tested.
-But because of the algorithm could potentially pick the 270\textdegree we will analyze the difference in peak heights and the power difference to evaluate the estimation further.
+From Table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of Altitude and elevation angles that were tested.
+But because of the algorithm could potentially pick the 270\textdegree \space we will analyze the difference in peak heights and the power difference to evaluate the estimation further.
 
@@
 
-From table \ref{tab:peaks_and_power} we can see that at the larger elevation angles the peak percent difference are significant to determine which is correctly the 90\textdegree value, but from the Peak frequency difference at the large elevation angles the difference is in the tens of Hz so in practical applications it is possible to confuse the estimation by just taking the minimum frequency so other values need to play a role such as the power.
+From Table \ref{tab:peaks_and_power} we can see that at the larger elevation angles the peak percent difference are significant to determine which is correctly the 90\textdegree \space value, but from the Peak frequency difference at the large elevation angles the difference is in the tens of Hz so in practical applications it is possible to confuse the estimation by just taking the minimum frequency so other values need to play a role such as the power.
 
@@
 
-where $R_{Estimate}$ is the estimated reflection radius at a particular azimuth, $BladeLength$ is the length of a single blade or radius of the rotor, and $f_{DopplerCorrect}$ is the correct doppler frequency for each azimuth angle $\theta_{Az}$.
+where $R_{Estimate}$ is the estimated reflection radius at a particular azimuth, $BladeLength$ is the length of a single blade or radius of the rotor, and $f_{DopplerCorrect}$ is the correct Doppler frequency for each azimuth angle $\theta_{Az}$.
 
@@
 
-where $f_{Doppler_{R Estimate Max}}$ is the maximum amount of doppler that could happen at that location if the signal was reflected parallel to the direction of motion.
+where $f_{Doppler_{R Estimate Max}}$ is the maximum amount of Doppler that could happen at that location if the signal was reflected parallel to the direction of motion.
 $f_c$ is the center frequency of the signal, $c$ is the speed of light and $v_r$ is the radial velocity based of the $RPM$ defined by
@@
 
-Then to find the elevation angle we look back at equation (-) where we then solve for the elevation angle 
+Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxUpperEnvelope$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate.
+we then solve for the elevation angle
+
 %Elevation angle
@@
 which means that the estimation in the reflection radius is correctly compensating for the azimuth angle.
-The percent error off the actual elevation angle is shown in figure \ref{fig:percent_error_elevation_azimuth_range} which is very small and consistent over the azimuth range.
+The percent error off the actual elevation angle is shown in Figure \ref{fig:percent_error_elevation_azimuth_range} which is very small and consistent over the azimuth range.
 
@@
 
-From table \ref{tab:elevation_error_percent} elevation estimation error is extremely small for the given actual elevation angles.
+From Table \ref{tab:elevation_error_percent} elevation estimation error is extremely small for the given actual elevation angles.
 But there is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.
@@
 
-This error is caused by a limitation on the estimation is that the doppler shift is limited by the maximum amount doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
+This error is caused by a limitation on the estimation is that the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
 
@@
 
-then using that to find the maximum available doppler through
+then using that to find the maximum available Doppler through
 
@@
 This limitation is shown by varying the elevation angle at the azimuth angle that provides the maximum Doppler shift, which is 180\textdegree \space.
-The maximum and minimum envelope data is shown in figure \ref{fig:envelope_180deg}
+The maximum and minimum envelope data is shown in Figure \ref{fig:envelope_180deg}
 
@@
 
-Using the estimation method described above, figure \ref{fig:angle_comparason_180deg} shows the elevation angle estimated versus the actual angle.
+Using the estimation method described above, Figure \ref{fig:angle_comparason_180deg} shows the elevation angle estimated versus the actual angle.
 The estimation method is accurate till about 18\textdegree \space or 20\textdegree \space where it becomes noisy.
-This is due to the inability of the envelope estimation to resolve the correct maximum doppler for that range.
-By going back to figure (anglerangerelation) we can see that as the transmitter moves farther and farther away the elevation angle is still decreasing but at a much smaller and smaller rate.
+This is due to the inability of the envelope estimation to resolve the correct maximum Doppler for that range.
+By going back to Figure \ref{fig:tx_range_elevation_rel} we can see that as the transmitter moves farther and farther away the elevation angle is still decreasing but at a much smaller and smaller rate.
 So the difference between elevation angles closer to zero are more difficult to resolve.
@@
 
-If we now consider a pitched blade the above method for estimating Azimuth and elevation becomes inaccurate due to the increased doppler between 90\textdegree and 270\textdegree and the decreased doppler on the other side.
-To correct this error we need to correct both the difference calculation and the correct doppler data accordingly.
-The uncorrected data is shown in figure \ref{fig:diff_pitch_noCorrection} and \ref{fig:dop_pitch_noCorrection} with percent azimuth error of 20\% and percent elevation error of 35\%.
+If we now consider a pitched blade the above method for estimating Azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side.
+To correct this error we need to correct both the difference calculation and the correct Doppler data accordingly.
+The uncorrected data is shown in Figure \ref{fig:diff_pitch_noCorrection} and \ref{fig:dop_pitch_noCorrection} with percent azimuth error of 20\% and percent elevation error of 35\%.
 
@@
 
-Comparing the envelope difference of no pitch and pitched blade, in figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
+Comparing the envelope difference of no pitch and pitched blade, in Figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
 Therefore we can first correct this by re-centering the pitch difference according to
@@
 \begin{equation}
-	A_{shift} = \frac{Max(Max Uppe rEnvelope) - |Min(Min Lower Envelope)|}{2}
+	A_{shift} = \frac{Max(Max Upper Envelope) - |Min(Min Lower Envelope)|}{2}
 	\label{eqn:pitch_shift}
@@
 	f_{DopplerCorrect} = f_{DopplerCorrect} + A_{shift}cos\left(\theta_{Az}\right)
-	\label{eqn:fd_max}
+	\label{eqn:fd_pitch_correct}
 \end{equation}
 
-Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with the a priori information that the cosign should be one period in length.
+Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with a priori information that the cosign should be one period in length.
 These corrections result in the percent azimuth error of 0\% and 7\% elevation angle error.
@@
 This is still a preliminary correction method that requires more in depth analysis but from the initial results shows merit.
-The increased accuracy as the elevation angle decreases relates back to figure \ref{fig:pitch_tx_elevation_angle} where as the elevation angle decreases the effect of pitch on the signal converges back to unpitched results.
+The increased accuracy as the elevation angle decreases relates back to Figure \ref{fig:pitch_tx_elevation_angle} where as the elevation angle decreases the effect of pitch on the signal converges back to the unpitched results.

### 2016-10-14 Simulation.tex
edits to thesis from clarice and modify background to reflect bistatic

--- 2016-10-13 Simulation.tex
@@
 The following simulations performed will define the search space on the effect of rotor blade modulation.
-Since the software developed allows for full parameterization of the objects within the scene the simulations will focus on a few that effect the different object's positions in 3D space and the resulting received signal.
+Since the software developed allows for full parameterization of the objects within the scene, the simulations will focus on a few that effect the different object's positions in 3D space and the resulting received signal.
 The parameters that will be changed are the position of the receiver, pitch of the rotor blade, and transmitter position.
@@
 \section{Analysis Techniques}
-The data from the .CSV files generated by the raytracing program is loaded into MATLAB scripts to process the data.
-The technique that is used is the spectrogram function that computes the short time Fourier transform.
-This allows for computations to be done in the time frequency domain and provide an accurate picture of how the signal is changing with time.
-The following figure \label{fig:test_spec} shows an example of the computed spectrograms.
+The data from the CSV files generated by the raytracing program are loaded into MATLAB scripts to process the data.
+The processing technique used is the spectrogram function that computes the short time Fourier transform.
+This allows for computations to be done in the time frequency domain and provides an accurate picture of how the signal is changing with time.
+Figure \label{fig:test_spec} shows an example of the computed spectrograms.
 
@@
 
-After the computation of the short time Fourier transform the doppler envelope is calculated by performing a threshold on the power, in both the positive and negative doppler, at each time slice.
+After the computation of the short time Fourier transform; the Doppler envelope is calculated by performing a threshold on the power, in both the positive and negative Doppler, at each time slice.
 The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values.
@@
 For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged.
-Then for each successive angle the same average is taken and averaged with all the others
+Then for each successive angle the same average is taken and averaged with all the others.
 
@@
 This technique is used because the elevation angle is remaining constant, so the distance with the helicopter platform should be constant as well.
-When varying the elevation angle in section \ref{sec:tea} the same method cannot be used because the distance is changing so only the maximum power is found in each time slice then those values are averaged without any successive averaging.
+When varying the elevation angle in section \ref{sec:tea}, the same method cannot be used because the distance is changing so only the maximum power is found in each time slice.
+Then all those values are averaged without any successive averaging.
 
@@
 
-The Doppler envelopes are displayed in figure \ref{fig:test_spec_w_doppler_profile}, the lower in blue and the upper in red.
+The Doppler envelopes are displayed in Figure \ref{fig:test_spec_w_doppler_profile}, the lower in blue and the upper in red.
 The minimum is calculated from the lower envelope, and the maximum from the upper envelope.
-Those values are then used to characterize that doppler profile and analyze signal trends as different variables change.
+Those values are then used to characterize that Doppler profile and analyze signal trends as different variables change.
 
@@
 
-The rotor blade length from figure \ref{fig:rx_position_image} is 7.5m so the receiver will be varied from 0m to 9m in 1m increments.
-The resulting signal is analyzed by calculating its doppler envelope.
+The rotor blade length from Figure \ref{fig:rx_position_image} is 7.5m so the receiver will be varied from 0m to 9m in 1m increments.
+The resulting signal is analyzed by calculating its Doppler envelope.
 Then the maximum and minimum of that envelope will then be used to determined the overall effect of the position of the receiver.
@@
 
-The figure \ref{fig:rx_position} shows maximum doppler vs the position of the receiver.
-From this graph the maximum doppler frequency changes significantly as the receiver is moved from directly under neath the rotor to past the tip of the rotor at 9m.The position of the receiver also effects the resulting signal envelope shapes shown in figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
+Figure \ref{fig:rx_position} shows maximum Doppler vs the position of the receiver.
+From this graph the maximum Doppler frequency changes significantly as the receiver is moved from directly under neath the rotor to past the tip of the rotor at 9m.The position of the receiver also effects the resulting signal envelope shapes shown in Figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
 
@@
 
-Comparing figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max doppler reflects the information in figure \ref{fig:rx_position} and the overall envelope is afected.
-The envelope in figure \ref{fig:rx_position_0m} is much noiser than the envelope of figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks.
+Comparing Figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max Doppler reflects the information in Figure \ref{fig:rx_position} and the overall envelope is afected.
+The envelope in Figure \ref{fig:rx_position_0m} is much noiser than the envelope of Figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks.
 The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}.
@@
 
-The resulting signal is analyzed by calculating its doppler envelope. Then the maximum and minimum of that envelope will then be used to determined the overall effect of pitching the rotor blade.
+The resulting signal is analyzed by calculating its Doppler envelope. Then the maximum and minimum of that envelope will then be used to determined the overall effect of pitching the rotor blade.
 
@@
 
-From figure \ref{fig:pitch_15_135deg} the effect of pitch on the maximum doppler frequency is a linear increase between a pitch from 0 \textdegree \space to 15\textdegree.
+From Figure \ref{fig:pitch_15_135deg} the effect of pitch on the maximum Doppler frequency is a linear increase between a pitch from 0 \textdegree \space to 15\textdegree.
 Due to the linear increase the pitch of the rotor blade can be accounted for when making measurements on subsequent simulation analysis.
-One issue does arise in when the transmitter is located underneath the helicopter which is shown in figure \ref{fig:pitch_tx0}.
+One issue does arise in when the transmitter is located underneath the helicopter which is shown in Figure \ref{fig:pitch_tx0}.
 
@@
 
-As the pitch increases linearly at first then climbs at a much faster rate.
+The pitch increases linearly at first then climbs at a much faster rate.
 This offset when the transmitter is directly underneath is caused by the pitch of the blade reflecting rays into the receiver which would be reflected back at the ground if the pitch was 0\textdegree.
 If the assumption is that the helicopter is hovering when these measurements take place the pitch of the rotor will be much less than the maximum pitch available.
-This assumption will adjust the maximum pitch to 15 \textdegree \space which will allow for the linear assumption to be fulfilled even when the transmitter is directly underneath the helicopter.
+This assumption will adjust the maximum pitch to 15\textdegree \space which will allow for the linear assumption to be fulfilled even when the transmitter is directly underneath the helicopter.
 
@@
 
-In figure \ref{fig:pitch_tx_elevation_angle} the max doppler vs elevation angles are initially shifted up in frequency from a pitch of 0 and has changed in slope.
+In Figure \ref{fig:pitch_tx_elevation_angle} the max Doppler vs elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and has changed in slope.
 This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel.
@@
 
-From figure \ref{fig:pitch_tx_elevation_angle_difference} we can see that the difference in frequency changes linearly as the elevation angle decreases, the slope of which is based on the pitch angle.
+From Figure \ref{fig:pitch_tx_elevation_angle_difference} we can see that the difference in frequency changes linearly as the elevation angle decreases, the slope of which is based on the pitch angle.
 This slope would have to be characterized on the physical craft and can be accounted for due to its predictable nature.
@@
 Where $\theta_{Az}$ is the azimuth angle.
-The azimuth angle of the transmitter in the simulation will effect the amount of doppler added to the signal.
+The azimuth angle of the transmitter in the simulation will effect the amount of Doppler added to the signal.
 This is due to the direction of the rotor blade rotation as it approaches both the receiver and the transmitter and how the rays reflect off the blade as it moves.
-From the model we see the amount of doppler form a sinusoidal pattern as the azimuth angle goes from $0$ to $2\pi$.
-This is mirrored in the simulation shown in figure \ref{fig:tx_azimuth_angle_200}.
+From the model we see the amount of Doppler form a sinusoidal pattern as the azimuth angle goes from $0$ to $2\pi$.
+This is mirrored in the simulation shown in Figure \ref{fig:tx_azimuth_angle_200}.
 
@@
 
-The graph in figure \ref{fig:tx_azimuth_angle_200} shows both the max and the minimum measured doppler as the azimuth angle completes a full rotation.
-The doppler frequency follows the azimuth angle in a sinusoidal fashion.
-The sinusoidal pattern is held as the elevation angle changes shown in figures \ref{fig:tx_azimuth_angle_50} and \ref{fig:tx_azimuth_angle_400}.
+The graph in Figure \ref{fig:tx_azimuth_angle_200} shows both the max and the minimum measured Doppler as the azimuth angle completes a full rotation.
+The Doppler frequency follows the azimuth angle in a sinusoidal fashion.
+The sinusoidal pattern is held as the elevation angle changes shown in Figures \ref{fig:tx_azimuth_angle_50} and \ref{fig:tx_azimuth_angle_400}.
 
@@
 %description
-The sinusoidal pattern of min and max doppler frequencies are only present when the receiver is located away from the axis of rotation.
-This is shown in figure \ref{fig:tx_azimuth_rx0} which is devoid of any sinusoidal pattern and remains constant as the transmitter azimuth angle is changed.
+The sinusoidal pattern of min and max Doppler frequencies are only present when the receiver is located away from the axis of rotation.
+This is shown in Figure \ref{fig:tx_azimuth_rx0} which is devoid of any sinusoidal pattern and remains constant as the transmitter azimuth angle is changed.
 
@@
 
-The effect of pitching the blade is that it modifies the results of the azimuth sweep when compared to figure \ref{fig:tx_azimuth_angle_200}.
+Pitching the blade modifies the results of the azimuth sweep when compared to Figure \ref{fig:tx_azimuth_angle_200}.
 The resulting min and max envelope frequencies vs azimuth angle for pitch are shown in \ref{fig:pitch_azimuth_rev}.
-This occurs because the pitch of the blade angles RF reflections more in the direction of travel but not at all points in the azimuth.
-When the transmitter is located between 90\textdegree and 270\textdegree pitch causes an increase in doppler but elsewhere decreases the amount of doppler shift.
-The decrease is caused by the blade surface top reflecting receding doppler away from the receiver at those angles.
+This occurs because the pitch of the blade angles RF reflections differently according to transmitter azimuth.
+When the transmitter is located between 90\textdegree \space and 270\textdegree \space pitch causes an increase in Doppler but elsewhere decreases the amount of Doppler shift.
+The decrease is caused by the blade surface top reflecting receding Doppler away from the receiver at those angles.
 
@@
 
-The effect of azimuth angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_azimuth_angle_estimation}
+The effect of azimuth angle on the maximum measured Doppler is characterized in section \ref{sec:transmitter_azimuth_angle_estimation}
 
@@
 %display elevation angle with respect to max doppler readings and describe patterns
-The transmitter elevation angle is the angle between the helicopter rotor and the position of the transmitter shown in figure \ref{fig:azimuth_rel}.
+The transmitter elevation angle is the angle between the helicopter rotor and the position of the transmitter shown in Figure \ref{fig:azimuth_rel} where $\theta_{El}$ is the elevation angle.
 
@@
 
-Where $\theta_{El}$ is the elevation angle.
-
 The smaller elevation angles mean that the transmitter is farther away from the helicopter.
-The elevation angle in relation to the distance of the transmitter is shown by figure \ref{fig:tx_range_elevation_rel}.
+The elevation angle in relation to the distance of the transmitter is shown by Figure \ref{fig:tx_range_elevation_rel}.
 
@@
 
-The elevation angle of the transmitter in the simulation will effect the amount of doppler added to the signal.
+The elevation angle of the transmitter in the simulation will effect the amount of Doppler added to the signal.
 This is due to the rays having a vector component in the direction of the travel of the rotor.
-When the transmitter is directly underneath the rotor and receiver there is no vector component in the direction of rotor travel so the reflected signal is not doppler shifted.
-From the model we see the amount of doppler increase as the elevation angle decreases.
-This is mirrored in the simulation shown in figure \ref{fig:tx_elevation_135deg}.
+When the transmitter is directly underneath the rotor and receiver there is no vector component in the direction of rotor travel so the reflected signal is not Doppler shifted.
+From the model we see the amount of Doppler increase as the elevation angle decreases.
+This is mirrored in the simulation shown in Figure \ref{fig:tx_elevation_135deg} where the maximum measured Doppler as the elevation angle increases.
 
@@
 
-The graph in figure \ref{fig:tx_elevation_135deg} shows the maximum measured doppler as the elevation angle increases.
-
-Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space, 90\textdegree \space, 180\textdegree \space, and 270\textdegree \space and their simulated counterparts shown in figure \ref{fig:verify}.
+Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space \ref{fig:3D_model_0az_doppler}, 90\textdegree \space \ref{fig:3D_model_90az_doppler}, 180\textdegree \space \ref{fig:3D_model_180az_doppler}, and 270\textdegree \space \ref{fig:3D_model_270az_doppler} and their simulated counterparts shown in Figure \ref{fig:verify}.
+We see that the ray traced results match their projections on the maximum and minimum envelope Doppler as transmitter elevation angle changes.
+The Doppler values do not match exactly but the trends are very similar.
 
@@
 
-The effect of elevation angle on the maximum measured doppler will be characterized in section \ref{sec:transmitter_elevation_angle_estimation}.
+The effect of elevation angle on the maximum measured Doppler will be characterized in section \ref{sec:transmitter_elevation_angle_estimation}.

### 2016-10-14 Thesis MATLAB Scripts/Envelope.m

@@ -2,7 +2,7 @@
 clear;
 %test_locationdatainfile_4
 %Altitude_200m/rx_test_Bistatic_dop0.000000rad2
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rx_test_Bistatic_dop0.000000rad2.csv');
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_range_270deg/rx_-600.000000m_270deg.csv');
 rpm = 250;
 
 %B = horzcat(samples,samples)';

### 2016-10-14 Thesis MATLAB Scripts/elevationEstimation_on_data_with_metadata.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %479000;
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -85,8 +85,8 @@ end
 
 figure;
 hold on
-plot((location_data(:,5)/(2*pi))*360,data_table(:,1))
-plot((location_data(:,5)/(2*pi))*360,data_table(:,2))
+plot((location_data(:,5)/(2*pi))*360,-data_table(:,2))
+plot((location_data(:,5)/(2*pi))*360,-data_table(:,1))
 hold off
 legend('Max Upper Envelope', 'Min Lower Envelope');
 title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle');

### 2016-10-14 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -28,12 +28,12 @@ xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
 
- i = 0.01:.01:7;
- el = fliplr(atan(2./i));
- v = ((2*pi)/60)*RPM*2;
+ i = 0.01:.01:2;
+ el = (atan(2./i));
+ v = ((2*pi)/60)*RPM*i;%? i or 2 .....
  max_fd = 2*(v*fc)/c;
- doppler_plus = max_fd.*cos(el);
- doppler_minus = -max_fd.*cos(el);
+ doppler_plus = max_fd.*(cos(el)+ cos(fliplr(el)));
+ doppler_minus = -max_fd.*(cos(el) + cos(fliplr(el)));
  figure;
  hold on
  plot(360*el/(2*pi),doppler_plus)
@@ -41,4 +41,4 @@ title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
  hold off
  xlabel('Elevation Angle (deg)');
  ylabel('Doppler Frequency (Hz)');
- title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth new');
+ title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');

### 2016-10-14 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -71,16 +71,16 @@ for i=1:num_files
     data_table(i,1) = max(upper_envelope); 
     data_table(i,2) = min(lower_envelope);
     
-%     figure;
-%     hold on
-%     plot3(t/60,lower_envelope/1000,z,'b','linewidth',4)
-%     plot3(t/60,upper_envelope/1000,z,'r','linewidth',4)
-%     spectrogram(signal_data(i,:),5000,500,5000,fs,'yaxis','centered')
-%     colormap(jet);
-%     colorbar
-%     view(2)
-%     title(num2str(location_data(i,4)));
-%     hold off
+    figure;
+    hold on
+    plot3(t/60,lower_envelope/1000,z,'b','linewidth',4)
+    plot3(t/60,upper_envelope/1000,z,'r','linewidth',4)
+    spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
+    colormap(jet);
+    colorbar
+    view(2)
+    title(num2str(location_data(i,4)));
+    hold off
 end
 
 %fix estimation error on first envelope -----

### 2016-10-15 Background.tex
edited second half

@@
 \begin{equation}
-	\theta_{Limited} = atan\left(\frac{Rx_z}{(BladeLength - Rx_y)}\right)
+	\theta_{Limited} = atan\left(\frac{Rx_z}{([0,\dots, (BladeLength - Rx_y)])}\right)
 	\label{eq:theory_90_limited}
@@
 Figure \ref{fig:3D_model_270az} depicts the transmitter at a 270\textdegree \space azimuth angle, which places it in-line with the position of the receiver and the current location of the rotating blades.
-This placement of the transmitter behind the helicopter is different from the situation in Figure \ref{fig:3D_model_90az} because the value of $\theta_r$ is now not limited by the tip of the rotor and can go to smaller elevation angles.
+This placement of the transmitter behind the helicopter is different from the situation in Figure \ref{fig:3D_model_90az} because the value of $\theta_r$ is now limited by the  rotor hub and maximum reflection radius.
 
@@
 %formulate the geometric equations
-The equation for modeling the scenario for a transmitter located at 270\textdegree \space azimuth is similar to the equations for calculating the 90\textdegree \space scenario, the limiting factor is now the reflection radius, because as the transmitter moves farther away the elevation angle is increasing but the reflection radius gets smaller.
+The equation for modeling the scenario for a transmitter located at 270\textdegree \space azimuth is similar to the equations for calculating the 90\textdegree \space scenario where $f_{DopplerMax}$ is now calculated with a smaller reflection radius of 2m and $\theta_{Limited}$ is now calculated by
+
+\begin{equation}
+	\theta_{Limited} = atan\left(\frac{Rx_z}{([0, \dots, BladeLength)}\right)
+	\label{eq:theory_270_limited}
+\end{equation}
 

### 2016-10-15 Conclusion.tex
edited second half

@@
 To do this appropriate hardware needs to be defined in the form of a software defined radio for both the receiver and transmitter along with a software workflow such as GNU Radio.
-Next a small scale environment would need to be set up, including the above hardware along with some form of rotating metal blade or thin plate rotating at a sufficient rate to produce a doppler spread similar to those defined in the simulation.
+Next a small scale environment would need to be set up, with some form of rotating metal blade or thin plate rotating at a sufficient rate to produce a doppler spread similar to those defined in the simulation.
 After that data is collected and analyzed a full scale experiment would need to be conducted including a real helicopter platform and an environment with large expanses of flat ground.
@@
 Another improvement on the simulation would be to increase the speed of computation.
-This could be done by implementing multi-threading or, since raytracing is heavily parallelizable, a GPU based architecture.
+This could be done by implementing multi-threading or, since raytracing is heavily parallelizable, a Graphics Processing Unit (GPU) based architecture.
 The multi-threading option would require minor code modifications but realizing the simulation on a GPU would require a full rewrite of the software to take advantage of the GPU's abilities.
@@
 The estimation methods described in this thesis rely only on the maximum and minimum values of the doppler envelopes calculated but their shape could also be of particular interest as well.
-When varying the parameters of azimuth and elevation the shape of the envelope changes in a distinctive manner, and by using a training algorithm the position of the transmitter might be able to be tracked in time by evaluating the change in shape.
-where currently if we want to locate the transmitter in a successive fashion a full revolution of the helicopter platform is needed to resolve position ambiguity.
+When varying the parameters of azimuth and elevation the shape of the envelope changes in a distinctive manner, by using a training algorithm the position of the transmitter might be able to be tracked in time by evaluating the change in shape.
+Under the defined estimation methods a full revolution of the helicopter platform is needed to resolve position ambiguity.

### 2016-10-15 Radio_Propagation_Simulation.tex
edited second half

@@
 The sampling rate will determine several simulation parameters in the ray tracer due to the need to associate this rate with the change in the rotor position for the next frame.
-The consequence of this is that increasing the sample rate will produce higher resolution results but will increase the computational overhead of the simulation.
+The consequence of this is that increasing the sample rate will produce higher resolution results but, will increase the computational overhead of the simulation.
 

### 2016-10-15 Ray_Tracing_Software.tex
edited second half

@@
 The output file also needs to be defined with a unique name that changes, this is important because the program will just write over the old file if you do not have a unique naming scheme.
-this could be just an increasing number or related to one of the variable sweeps.
+This could be just an increasing number or related to one of the variable sweeps.
 
@@
 
-this is all provided in a single string of comma separated values called a .CSV file. MATLAB has a built in function to read CSV data.
+This data is all provided in a single string of comma separated values called a .CSV file. MATLAB has a built in function to read CSV data.
 
@@
 
-after all the data is read into MATLAB the data can be split into two vectors, one pertaining to the physical simulation parameters and the other to the received signal.
+After all the data is read into MATLAB the data can be split into two vectors, one pertaining to the physical simulation parameters and the other to the received signal.
 

### 2016-10-15 Results_new.tex
edited second half

@@
 First the azimuth angle will be estimated which will provide the information necessary for calculating the elevation angle.
-The results of the estimation techniques are then analyzed to determine their accuracy compared to the actual.
+The results of the estimation techniques are then analyzed to determine their accuracy.
 
@@
 The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which a Doppler envelope and subsequent maximum and minimum values are calculated.
-After a complete rotation the Doppler maximum and minimum values produce a sinusoidal pattern as shown in Figure \ref{fig:tx_azimuth_angle_200} without the assumption of knowing the starting azimuth angle.
-With this data we need to find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle.
+After a complete rotation the Doppler maximum and minimum values produce a sinusoidal pattern as shown in Figure \ref{fig:tx_azimuth_angle_200} without knowing the starting azimuth angle.
+With this data we find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle.
 To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in Figure \ref{fig:azimuth_estimation_max_vs_absMin}.
@@
 
-From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference
+From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference of the two
 
@@
 
-While Figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself, therefore by computing the correct Doppler using the $Max Upper Envelope$ and the $| Min Lower Envelope |$.
-This is done by evaluating the difference at each angle and if the difference is negative the $| Min Lower Envelope |$ is used and if positive the $Max Upper Envelope$.
+While Figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself.
+Therefore by finding the correct Doppler for each azimuth, from the $Max Upper Envelope$ and the $| Min Lower Envelope |$, we can determine an unambiguous reference.
+This is done by evaluating the difference at each angle, and if the difference is negative the $| Min Lower Envelope |$ is used and if positive the $Max Upper Envelope$.
 
@@
 The data gathered contains a global minimum at 90\textdegree \space and a second local minimum at 270\textdegree.
-The 90\textdegree \space can be found easily by taking the minimum of the correct Doppler signal
+The 90\textdegree \space can be found easily by taking the minimum of the correct Doppler signal.
 
@@
 
-But in order to find the local minimum at 270\textdegree \space we need to use a different method.
-To do this we can use the peak detection function within MATLAB to locate both the 90\textdegree \space and 270\textdegree \space point.
+In order to find the local minimum at 270\textdegree \space we need to use a different method.
+We can do this through the peak detection function within MATLAB to locate both the 90\textdegree \space and 270\textdegree \space point.
 By taking the inverse of the correct Doppler and tuning the peak detection function with the maximum and minimum values to determine accurate prominence.
@@
 Figure \ref{fig:ave_power}  shows the average power at each angle sample with the angles 90\textdegree \space and 270\textdegree \space denoted as red x's.
-From the plot we can see that the average power at 90\textdegree \space is much smaller than the the power at 270\textdegree, so this inequality will be used to resolve ambiguity in the azimuth angle.
+From the plot we can see that the average power at 90\textdegree \space is much smaller than at 270\textdegree, so this inequality will be used to resolve ambiguity in the azimuth angle.
 
@@
 
-From Table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of Altitude and elevation angles that were tested.
-But because of the algorithm could potentially pick the 270\textdegree \space we will analyze the difference in peak heights and the power difference to evaluate the estimation further.
+From Table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of altitude and elevation angles that were tested.
+But because the algorithm could potentially pick the 270\textdegree \space we will analyze the difference in peak heights and the power difference to evaluate the estimation further.
 
@@
 
-From Table \ref{tab:peaks_and_power} we can see that at the larger elevation angles the peak percent difference are significant to determine which is correctly the 90\textdegree \space value, but from the Peak frequency difference at the large elevation angles the difference is in the tens of Hz so in practical applications it is possible to confuse the estimation by just taking the minimum frequency so other values need to play a role such as the power.
+From Table \ref{tab:peaks_and_power} we can see that at the larger elevation angles the peak percent difference are significant to determine which is correctly the 90\textdegree \space value.
+Although from the frequency difference, at the large elevation angles, it is possible to confuse the estimation by just taking the minimum frequency.
+Therefore other values need to play a role such as the received power.
 
@@
 %formulate the estimation equation and discuss ambiguity considerations
-Using the information gathered from the azimuth estimation procedure we can compute the elevation angle of the transmitter.
-In the process of gathering azimuth information the maximum and minimum envelopes follow a sinusoidal pattern that contains a maximum Doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles.
-Using that maximum value along with the correct Doppler and the assumption that the maximum will occur near the tip of the rotor blade we can approximate the respected reflection radii off the blade as the azimuth angle changes.
+Using the information gathered from the azimuth estimation procedure, we can compute the elevation angle of the transmitter.
+In the process of gathering azimuth information, the maximum and minimum envelopes follow a sinusoidal pattern that contains a maximum Doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles.
+Using that maximum value, along with the correct Doppler and the assumption that the maximum will occur near the tip of the rotor blade, we can approximate the respected reflection radii off the blade as the azimuth angle changes.
 This is done through
@@
 
-Figure \ref{fig:elevation_comparason_azimuth_range} shows the estimation of the elevation angle $\theta_{El}$ with respect to the azimuth angle, what it shows is that the elevation angle remains constant with respect to azimuth angle.
-which means that the estimation in the reflection radius is correctly compensating for the azimuth angle.
-The percent error off the actual elevation angle is shown in Figure \ref{fig:percent_error_elevation_azimuth_range} which is very small and consistent over the azimuth range.
+Figure \ref{fig:elevation_comparason_azimuth_range} shows the estimation of the elevation angle $\theta_{El}$ with respect to the azimuth angle.
+What it shows is that the elevation angle remains constant with respect to azimuth angle.
+Which means that the estimation in the reflection radius is correctly compensating for the azimuth angle.
+The percent error off the actual elevation angle is shown in Figure \ref{fig:percent_error_elevation_azimuth_range} which is very small but consistent over the azimuth range.
 
@@
 
-From Table \ref{tab:elevation_error_percent} elevation estimation error is extremely small for the given actual elevation angles.
-But there is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.
+From Table \ref{tab:elevation_error_percent} we can see elevation estimation error is extremely small for the given elevation angles.
+There is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.
 
@@
 
-This error is caused by a limitation on the estimation is that the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
+The error in elevation is caused by a limitation on the estimation.
+Where the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
 
@@
 
-This limitation is shown by varying the elevation angle at the azimuth angle that provides the maximum Doppler shift, which is 180\textdegree \space.
+This limitation is shown by varying the elevation angle at the azimuth angle that provides the maximum Doppler shift, which is 180\textdegree.
 The maximum and minimum envelope data is shown in Figure \ref{fig:envelope_180deg}
@@
 Using the estimation method described above, Figure \ref{fig:angle_comparason_180deg} shows the elevation angle estimated versus the actual angle.
-The estimation method is accurate till about 18\textdegree \space or 20\textdegree \space where it becomes noisy.
+The estimation method is accurate till elevation angles of 18\textdegree \space or 20\textdegree, where it becomes noisy.
 This is due to the inability of the envelope estimation to resolve the correct maximum Doppler for that range.
@@
 
-Figure \ref{fig:percent_error_elevation_180deg} shows the percent error with respect to the elevation angle and it starts to become unusable around 18\textdegree \space or 20\textdegree \space where the percent error starts to shoot past acceptable ranges.
+Figure \ref{fig:percent_error_elevation_180deg} shows the percent error with respect to the elevation angle.
+The estimation starts to become unusable around 18\textdegree \space or 20\textdegree \space where the percent error starts to shoot past acceptable ranges.
 
@@
 
-Since $\theta_{Az}$ is unknown during the calculation of this equation the correct starting phase can be determined by matching it to the $EnvelopeDifference$ with a priori information that the cosign should be one period in length.
+Since $\theta_{Az}$ is unknown during the calculation of equation \ref{eqn:fd_pitch_correct} the correct starting phase can be determined by matching it to the $EnvelopeDifference$ and that the cosine should be one period in length.
 These corrections result in the percent azimuth error of 0\% and 7\% elevation angle error.

### 2016-10-15 Simulation.tex
edited second half

@@
 
-The rotor blade length from Figure \ref{fig:rx_position_image} is 7.5m so the receiver will be varied from 0m to 9m in 1m increments.
+The rotor blade length from Figure \ref{fig:rx_position_image} is 7.5 m so the receiver will be varied from 0 m to 9 m in 1 m increments.
 The resulting signal is analyzed by calculating its Doppler envelope.
@@
 
-Figure \ref{fig:rx_position} shows maximum Doppler vs the position of the receiver.
-From this graph the maximum Doppler frequency changes significantly as the receiver is moved from directly under neath the rotor to past the tip of the rotor at 9m.The position of the receiver also effects the resulting signal envelope shapes shown in Figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
+Figure \ref{fig:rx_position} shows maximum Doppler versus the position of the receiver.
+From this graph, the maximum Doppler frequency changes significantly as the receiver is moved from directly underneath the rotor to past the tip of the rotor at 9 m.The position of the receiver also effects the resulting signal envelope shapes shown in Figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
 
@@
 
-Comparing Figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max Doppler reflects the information in Figure \ref{fig:rx_position} and the overall envelope is afected.
-The envelope in Figure \ref{fig:rx_position_0m} is much noiser than the envelope of Figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks.
+Comparing Figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max Doppler reflects the information in Figure \ref{fig:rx_position} and the overall envelope is affected.
+The envelope in Figure \ref{fig:rx_position_0m} is much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks.
 The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}.
-Therefore the receiver will be offset from the center of rotation by 7m for the subsequent simulations.
+Therefore, the receiver will be offset from the center of rotation by 7 m for the subsequent simulations.
 
@@
 
-From Figure \ref{fig:pitch_15_135deg} the effect of pitch on the maximum Doppler frequency is a linear increase between a pitch from 0 \textdegree \space to 15\textdegree.
-Due to the linear increase the pitch of the rotor blade can be accounted for when making measurements on subsequent simulation analysis.
+From Figure \ref{fig:pitch_15_135deg} the effect of pitch on the maximum Doppler frequency is a linear increase between a pitch from 0\textdegree \space to 15\textdegree.
+Due to the linear increase, the pitch of the rotor blade can be accounted for when making measurements on subsequent simulation analysis.
 One issue does arise in when the transmitter is located underneath the helicopter which is shown in Figure \ref{fig:pitch_tx0}.
@@
 The pitch increases linearly at first then climbs at a much faster rate.
-This offset when the transmitter is directly underneath is caused by the pitch of the blade reflecting rays into the receiver which would be reflected back at the ground if the pitch was 0\textdegree.
-If the assumption is that the helicopter is hovering when these measurements take place the pitch of the rotor will be much less than the maximum pitch available.
+This offset is caused by the pitch of the blade reflecting rays into the receiver which would be reflected back at the ground if the pitch was 0\textdegree.
+If the assumption is that the helicopter is hovering when these measurements take place, the pitch of the rotor will be much less than the maximum pitch available.
 This assumption will adjust the maximum pitch to 15\textdegree \space which will allow for the linear assumption to be fulfilled even when the transmitter is directly underneath the helicopter.
@@
 
-In Figure \ref{fig:pitch_tx_elevation_angle} the max Doppler vs elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and has changed in slope.
+In Figure \ref{fig:pitch_tx_elevation_angle} the max Doppler versus elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and, consequently, have changed in slope.
 This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel.
@@
 This is due to the direction of the rotor blade rotation as it approaches both the receiver and the transmitter and how the rays reflect off the blade as it moves.
-From the model we see the amount of Doppler form a sinusoidal pattern as the azimuth angle goes from $0$ to $2\pi$.
+From the model we see the amount of Doppler form a sinusoidal pattern as the azimuth angle goes from 0\textdegree \space to 360\textdegree.
 This is mirrored in the simulation shown in Figure \ref{fig:tx_azimuth_angle_200}.
@@
 
-The graph in Figure \ref{fig:tx_azimuth_angle_200} shows both the max and the minimum measured Doppler as the azimuth angle completes a full rotation.
+The graph in Figure \ref{fig:tx_azimuth_angle_200} shows both the maximum and the minimum measured Doppler as the azimuth angle completes a full rotation.
 The Doppler frequency follows the azimuth angle in a sinusoidal fashion.
@@
 %description
-The sinusoidal pattern of min and max Doppler frequencies are only present when the receiver is located away from the axis of rotation.
+The sinusoidal pattern of minimum and maximum Doppler frequencies are only present when the receiver is located away from the axis of rotation.
 This is shown in Figure \ref{fig:tx_azimuth_rx0} which is devoid of any sinusoidal pattern and remains constant as the transmitter azimuth angle is changed.
@@
 Pitching the blade modifies the results of the azimuth sweep when compared to Figure \ref{fig:tx_azimuth_angle_200}.
-The resulting min and max envelope frequencies vs azimuth angle for pitch are shown in \ref{fig:pitch_azimuth_rev}.
+The resulting minimum and maximum envelope frequencies versus azimuth angle for pitch are shown in Figure \ref{fig:pitch_azimuth_rev}.
 This occurs because the pitch of the blade angles RF reflections differently according to transmitter azimuth.
-When the transmitter is located between 90\textdegree \space and 270\textdegree \space pitch causes an increase in Doppler but elsewhere decreases the amount of Doppler shift.
+When the transmitter is located between 90\textdegree \space and 270\textdegree \space pitch causes an increase in Doppler but elsewhere it decreases the amount of Doppler shift.
 The decrease is caused by the blade surface top reflecting receding Doppler away from the receiver at those angles.
@@
 
-The effect of azimuth angle on the maximum measured Doppler is characterized in section \ref{sec:transmitter_azimuth_angle_estimation}
+The effect of the azimuth angle on the maximum measured Doppler is characterized in section \ref{sec:transmitter_azimuth_angle_estimation}
 
@@
 This is due to the rays having a vector component in the direction of the travel of the rotor.
-When the transmitter is directly underneath the rotor and receiver there is no vector component in the direction of rotor travel so the reflected signal is not Doppler shifted.
+When the transmitter is directly underneath the rotor and receiver, there is no vector component in the direction of rotor travel so the reflected signal is not Doppler shifted.
 From the model we see the amount of Doppler increase as the elevation angle decreases.

### 2016-10-15 Thesis MATLAB Scripts/Envelope.m

@@ -2,7 +2,7 @@
 clear;
 %test_locationdatainfile_4
 %Altitude_200m/rx_test_Bistatic_dop0.000000rad2
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_range_270deg/rx_-600.000000m_270deg.csv');
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/rx_test_Bistatic_dop0.628319rad.csv');
 rpm = 250;
 
 %B = horzcat(samples,samples)';

### 2016-10-15 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -16,7 +16,7 @@ Rx_z = 2;
 Rx_y = 7;
 Rx_x = 0;
 
-Tx_radius = 0:1:450;
+Tx_radius = 0:1:600;
 elevation_angle = atan(Altitude./(Tx_radius + Reflection_radius));
 doppler_plus = max_fd*cos(elevation_angle);
 doppler_minus = -max_fd*cos(elevation_angle);
@@ -28,12 +28,12 @@ xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
 
- i = 0.01:.01:2;
- el = (atan(2./i));
- v = ((2*pi)/60)*RPM*i;%? i or 2 .....
+ i = 0.01:.01:7;
+ el = fliplr(atan(2./i));
+ v = ((2*pi)/60)*RPM*2;%? i or 2 .....
  max_fd = 2*(v*fc)/c;
- doppler_plus = max_fd.*(cos(el)+ cos(fliplr(el)));
- doppler_minus = -max_fd.*(cos(el) + cos(fliplr(el)));
+ doppler_plus = max_fd.*(cos(el));
+ doppler_minus = -max_fd.*(cos(el));
  figure;
  hold on
  plot(360*el/(2*pi),doppler_plus)

### 2016-10-15 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -71,16 +71,16 @@ for i=1:num_files
     data_table(i,1) = max(upper_envelope); 
     data_table(i,2) = min(lower_envelope);
     
-    figure;
-    hold on
-    plot3(t/60,lower_envelope/1000,z,'b','linewidth',4)
-    plot3(t/60,upper_envelope/1000,z,'r','linewidth',4)
-    spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
-    colormap(jet);
-    colorbar
-    view(2)
-    title(num2str(location_data(i,4)));
-    hold off
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'b','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'r','linewidth',4)
+%     spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
+%     colormap(jet);
+%     colorbar
+%     view(2)
+%     title(num2str(location_data(i,4)));
+%     hold off
 end
 
 %fix estimation error on first envelope -----
@@ -102,7 +102,7 @@ difference = data_table(:,1) - abs(data_table(:,2));
 %correct for pitch
 zero_correct = max(data_table(:,1)) - abs(min(data_table(:,2)));
 if(zero_correct > .1*max(difference))
[…]

### 2016-10-15 MSc. Thesis Template.tex
add symbols list

@@
 \setstretch{1.5}  % Set the line spacing to 1.5, this makes the following tables easier to read
-%\clearpage  % Start a new page
+\clearpage  % Start a new page
 \lhead{\emph{Abbreviations}}  % Set the left side page header to "Abbreviations"
@@
 %\listofconstants{ll}  % Include a list of Physical Constants (a four column table)
-{
+%{
 % Constant Name & Symbol & = & Constant Value (with units) \\
 
-}
+%}
 
 %% ----------------------------------------------------------------
-%\clearpage  %Start a new page
-%\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
-%\listofnomenclature{ll}  % Include a list of Symbols (a three column table)
+\clearpage  %Start a new page
+\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
+\listofnomenclature{l p{5cm} l}  % Include a list of Symbols (a three column table)
 {
-% symbol & name & unit \\
-
+ \textbf{Symbol} & \textbf{Name} & \textbf{Units} \\
+ $\theta_{El}$ & Transmitter Elevation angle & degrees \\
+ $\theta_{r}$ & Ray Reflection angle & degrees \\
+ $\theta_{Az}$ & Transmitter Azimuth angle & degrees \\
+ $f_d$ & Doppler Frequency shift & Hz \\
+ $\theta_b$ & Rotor Blade angle & degrees \\
+ $Rx_x$ & Receiver position in X axis & meters \\
+ $Rx_y$ & Receiver position in Y axis & meters \\
+ $Rx_z$ & Receiver position in Z axis & meters \\
+ $G_r$ & & \\
+ $G_t$ & & \\
+ $R$ & & \\
+ $n$ & & \\
+ $d_i$ & & \\
+ $\theta_i$ & Angle of incedence with an objects normal & radians \\
+ $d$ & Total distance traveled by a ray & meters \\ 
+ $t_0$ & Starting time in a frame & seconds \\
+ $r$ & A radius along the length of the blade & meters \\
+ $\omega_r$ & Rotational velocity of the blade & rad/second \\
+ $F$ & Fading coefficient & \\
+ $\lambda$ & Wavelength & meters \\
+ $c$ & Speed of Light & meters/seconds \\
+ $f$ & frequency & Hz \\
+ $f_0$ & initial frequency & Hz \\
+ $f_s$ & sampling frequency & samples/seconds \\
+ $EnvelopeDifference$ & difference between two doppler envelopes & Hz \\
+ $MaxUpperEnvelope$ & Array of values corresponding to the maximum of each azimuth or elevation upper envelope calculation & Hz \\
+ $MinLowerEnvelope$ & Array of values corresponding to the minimum of each azimuth or elevation lower envelope calculation & Hz \\
+ $BladeLength$ & Length of single rotor blade (radius of rotor) & meters \\
+ $f_c$ & Center Frequency & Hz \\
+ $R_{Estimate}$ & Estimated reflection radius & meters \\
+ $f_{DopplerMax}$ & The maximum amount of doppler for a particular blade length and RPM & Hz \\
+ $f_{DopplerCorrect}$ & The corrected doppler per $\theta_{Az}$ to be processed & Hz \\
+ $A_{shift}$ & The amount of shift needed to correct for Blade pitch & Hz \\
 }

### 2016-10-19 Background.tex
add bold theory figure, add legends to verify figures

@@
 The resulting modulated signal has been used in several radar applications.
-First to determine the specific characteristics of a noncooperative helicopter using time frequency analysis in \cite{Bullard1991} that defines a specific signature for physical parameters of a helicopter.
-The ability to detect a hovering helicopter based on the blade flashes caused by reflected radar pulses off the blades is examined in \cite{Misiurewicz1997} where they used information the time domain to determine if a helicopter was hovering.
-The micro-Doppler produced by the radar reflection in \cite{Thayaparan2007} is used to determine the rotation rate of both the main and tail rotor blades using the wavelet transform.
-Other types of aircraft produce modulations on a returned radar pulse, one type known as Jet Engine Modulation (JEM) is the product of a radar pulse reflecting off the jet engine blades \cite{NavalAirSystemsCommand1999}.
+One radar application of RBM was to determine the specific characteristics of a noncooperative helicopter using time frequency analysis by Bullard and Dowdy in \cite{Bullard1991}.
+Where they define specific signatures for physical parameters of a helicopter.
+The ability to detect a hovering helicopter based on the blade flashes caused by reflected radar pulses off the blades is examined by Misiurewicz, Kulpa, and Czekala in \cite{Misiurewicz1997}, where they used information the time domain to determine if a helicopter was hovering.
+The micro-Doppler produced by the radar reflection was used by Thayaparan et.
+al.
+in \cite{Thayaparan2007} to determine the rotation rate of both the main and tail rotor blades using the Wavelet transform.
+Other types of aircraft produce modulations on a returned radar pulse; one type known as Jet Engine Modulation (JEM) is the product of a radar pulse reflecting off the jet engine blades \cite{NavalAirSystemsCommand1999}.
 The information can similarly be used to quantify physical aspects of the aircraft when present in order to perform classification.
 
-The Doppler shifted signal caused by RBM is shown in \cite{F.BarbieroF.VincentT.Deloues2014} to effect the performance of common adaptive Global Positioning System (GPS) anti-jamming algorithms located on helicopter platforms.
+The Doppler shifted signal, caused by RBM, is shown by Barbiero, Vincent, and Deloues in \cite{F.BarbieroF.VincentT.Deloues2014} to effect the performance of common adaptive Global Positioning System (GPS) anti-jamming algorithms located on helicopter platforms.
 They were able to mitigate the effects by estimating the covariance within a few milliseconds but this comes at an extreme computation overhead.
 And for iterative based anti-jamming approaches the non-stationary signal characteristics cause degradation as well.
-The affect of RBM on the Bit Error Rate (BER) of communications is examined in \cite{YiminZhang2000} where effects of multipath and Doppler cause large BER values at small elevation angles and large scattering coefficients described in the model.
+The affect of RBM on the Bit Error Rate (BER) of communications is examined by Zhang, Amin, and Mancuso in \cite{YiminZhang2000}, where effects of multipath and Doppler cause large BER values at small elevation angles and large scattering coefficients described in the model.
 
@@
 Next is the transmitter $Tx$, in green, and the receiver $Rx$ in blue.
-The measurements, depicted as black bars with denoting start and stop points, reference the various distances used in the following equations.
+The measurements, depicted as black bars with denoted start and stop points, reference the various distances used in the following equations.
 The dashed green line shows at which altitude the helicopter is hovering at, and the red dashed line transverses the transmitter and the center of rotation for the blades.
@@
 Lastly the line of sight (LOS) ray shows that the transmitter and receiver are in visual line of sight of each other.
+
+The resulting Doppler equation is described by
 
@@
 
-where $f_d$ is the Doppler frequency shift, $f_{DopplerMax}$ is described by equation \ref{eqn:fd_max} as the maximum amount of Doppler shift possible, $\theta_{El}$ is the elevation angle of the transmitter with respect to the rotor blades, and $\theta_{b}$ is the current angle of the rotor blade.
+where $f_d$ is the Doppler frequency shift, $f_{DopplerMax}$ is defined later by equation \ref{eqn:fd_max} as the maximum amount of Doppler shift possible, $\theta_{El}$ is the elevation angle of the transmitter with respect to the rotor blades, and $\theta_{b}$ is the current angle of the rotor blade.
 
@@
 %validation consideration
-Since this model has the receiver located at the axis of rotation this model can be seen as a special case of the next 3D models, this is because it is symmetric around the axis of rotation.
+Since this model has the receiver located at the axis of rotation this model can be seen as a special case of the next 3D models, because it is symmetric around the axis of rotation.
 Therefore, any placement of the transmitter in 3D space can be distilled down to a 2D profile as such.
@@
 The X and Y axis are specifically drawn in blue and red respectfully, with the Z axis now the green dashed line and altitude is now denoted with a measurement bar.
-The receiver offset in the +Y direction is now stated.
-and the Blades are now colored gray.
+The receiver offset in the +Y direction is now stated and the blades are now colored gray.
 All other variables and colors denote their objects as previously stated in the 2D case.
@@
 
-where $MaxUpperEnvelope$ is an array of the maximum upper envelope values for each elevation sample, $MinLowerEnvelope$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range due to
+where $MaxUpperEnvelope$ is an array of the maximum upper envelope values for each elevation sample, $MinLowerEnvelope$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range
 
 \begin{equation}
-	\theta_{Limited} = atan\left(\frac{Rx_z}{([0,\dots, (BladeLength - Rx_y)])}\right)
+	\theta_{Limited} = atan\left(\frac{Rx_z}{[0,\dots, (BladeLength - Rx_y)]}\right)
 	\label{eq:theory_90_limited}
@@
 \begin{equation}
-	\theta_{Limited} = atan\left(\frac{Rx_z}{([0, \dots, BladeLength)}\right)
+	\theta_{Limited} = atan\left(\frac{Rx_z}{[0, \dots, BladeLength]}\right)
 	\label{eq:theory_270_limited}
@@
 
-and the MinLowerEnvelope is set to 0 for the range.
+and the $MinLowerEnvelope$ is set to 0 for the range.
 
@@
 %go over the 3d model for the receding blade
-The receding model shown in Figure \ref{fig:3D_model_0az} depicts the transmitter at an azimuth of 0\textdegree \space where the axis positions back to their original places and the direction of the rotor blade is now depicted in red.
+The receding model shown in Figure \ref{fig:3D_model_0az} depicts the transmitter at an azimuth of 0\textdegree \space where the axis positions are back to their original places and the direction of the rotor blade is now depicted in red.
 
@@
 \begin{equation}
-	MinLowerEnvelope = f_{DopplerMax}cos(\theta_{El})
+	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{El})
 	\label{eq:theory_0_lower}
@@
 
-and the MaxUpperEnvelope is set to 0 for the range.
+and the $MaxUpperEnvelope$ is set to 0 for the range.
 

### 2016-10-19 Conclusion.tex
add bold theory figure, add legends to verify figures

@@
 The physical parameters associated with a helicopter blade and the positioning of transmitter and receiver hardware were swept independently to build knowledge on how they affect the resulting signal.
-That data was then processed using time frequency analysis to produce a doppler envelope.
+That data was then processed using time frequency analysis to produce a Doppler envelope.
 An envelope of each parameter step was used to determine an overall trend.
@@
 To do this appropriate hardware needs to be defined in the form of a software defined radio for both the receiver and transmitter along with a software workflow such as GNU Radio.
-Next a small scale environment would need to be set up, with some form of rotating metal blade or thin plate rotating at a sufficient rate to produce a doppler spread similar to those defined in the simulation.
+Next a small scale environment would need to be set up, with some form of rotating metal blade or thin plate rotating at a sufficient rate to produce a Doppler spread similar to those defined in the simulation.
 After that data is collected and analyzed a full scale experiment would need to be conducted including a real helicopter platform and an environment with large expanses of flat ground.
@@
 %Because there is more information in the received envelopes besides the maximum and minimum the specific shape could be used to better estimate azimuth and elevation without the need to complete a full revolution as described in the proposed method.
-The estimation methods described in this thesis rely only on the maximum and minimum values of the doppler envelopes calculated but their shape could also be of particular interest as well.
+The estimation methods described in this thesis rely only on the maximum and minimum values of the Doppler envelopes calculated but their shape could also be of particular interest as well.
 When varying the parameters of azimuth and elevation the shape of the envelope changes in a distinctive manner, by using a training algorithm the position of the transmitter might be able to be tracked in time by evaluating the change in shape.

### 2016-10-19 Introduction.tex
add bold theory figure, add legends to verify figures

@@
 \section{Organization}
-In Chapter \ref{ch:background} we present the background and theory behind rotor blade modulation. we then formulate the basic geometry behind the RBM effect.
+In Chapter \ref{ch:background} we present the background and theory behind rotor blade modulation. We then formulate the basic geometry behind the RBM effect.
 
-In Chapter \ref{ch:radio_propagation} we Introduce the radio propagation simulation in several sections.
+In Chapter \ref{ch:radio_propagation} we introduce the radio propagation simulation in several sections.
 First is the RF propagation model which defines the physical effects that are simulated within the software.
@@
 
-In Chapter  \ref{ch:results} Those characteristics are then used to estimate the azimuth and elevation angle of the transmitter based on the given rotor and receiver parameters.
+In Chapter  \ref{ch:results} those characteristics from chapter \ref{ch:simulations} are then used to estimate the azimuth and elevation angle of the transmitter based on the given rotor and receiver parameters.
 Those estimates are then compared with the original position of the transmitter to determine the methods accuracy.

### 2016-10-19 MSc. Thesis Template.tex
add bold theory figure, add legends to verify figures

--- 2016-10-14 MSc. Thesis Template.tex
@@
 I would like to thank my thesis advisor Dr.
-Tamal Bose for the opportunity to work in his lab, and for the guidance through graduate school.
+Tamal Bose for the opportunity to work in his lab and for the guidance through graduate school.
 I would also like to thank Matt Kruse and Charlie Cooper for coming up the research topic and support through the process.
@@
 \pagestyle{empty}  % Page style needs to be empty for this page
-\dedicatory{To my Mother and Father, \\my brother Danny, \\and my lovely girlfriend Clarice,\\all with love, \\Thank you for your unconditional support.}
+\dedicatory{To my Mother and Father, \\my brother Danny, \\and my lovely girlfriend Clarice,\\all with love, \\thank you for your unconditional support.}
 \addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
@@
  \textbf{3D} & 3-\textbf{D}imensional \\
- \textbf{BER} & \textbf{B}it \textbf{E}error \textbf{R}ate \\
- \textbf{BRDF} & \textbf{B}i-directional \textbf{R}eflection  \textbf{D}istrobution \textbf{F}unction \\
+ \textbf{BER} & \textbf{B}it \textbf{E}rror \textbf{R}ate \\
+ \textbf{BRDF} & \textbf{B}i-directional \textbf{R}eflection  \textbf{D}istribution \textbf{F}unction \\
  \textbf{CSV} & \textbf{C}omma \textbf{S}eparated \textbf{V}alue \\
@@
 %\listofconstants{ll}  % Include a list of Physical Constants (a four column table)
-{
+%{
 % Constant Name & Symbol & = & Constant Value (with units) \\
 
-}
+%}
 
 %% ----------------------------------------------------------------
-%\clearpage  %Start a new page
-%\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
-%\listofnomenclature{ll}  % Include a list of Symbols (a three column table)
+\clearpage  %Start a new page
+\lhead{\emph{Symbols}}  % Set the left side page header to "Symbols"
+\listofnomenclature{l p{5cm}| l}  % Include a list of Symbols (a three column table)
 {
-% symbol & name & unit \\
-
+ \textbf{Symbol} & \textbf{Name} & \textbf{Units} \\
+ $\theta_{El}$ & Transmitter Elevation angle & degrees \\
+ $\theta_{r}$ & Ray Reflection angle & degrees \\
+ $\theta_{Az}$ & Transmitter Azimuth angle & degrees \\
+ $f_d$ & Doppler Frequency shift & Hz \\
+ $\theta_b$ & Rotor Blade angle & degrees \\
+ $Rx_x$ & Receiver position in X axis & meters \\
+ $Rx_y$ & Receiver position in Y axis & meters \\
+ $Rx_z$ & Receiver position in Z axis & meters \\
+ $G_r$ & Receiver antenna gain & \\
+ $G_t$ & Transmitter antenna gain& \\
+ $R$ & Distance & meters\\
+ $\vec{n}$ & Surface normal vector & \\
+ $\vec{d_i}$ & Direction vector of incident ray & \\
+ $\Gamma$ & Reflection loss coefficient & \\
+ $\theta_i$ & Angle of incidence with an objects normal & radians \\
+ $d$ & Total distance traveled by a ray & meters \\ 
+ $t_0$ & Starting time in a frame & seconds \\
+ $r$ & A radius along the length of the blade & meters \\
+ $\omega_r$ & Rotational velocity of the blade & rad/second \\
+ $F$ & Fading coefficient & \\
+ $\lambda$ & Wavelength & meters \\
+ $c$ & Speed of Light & meters/seconds \\
+ $f$ & frequency & Hz \\
+ $f_0$ & initial frequency & Hz \\
+ $f_s$ & sampling frequency & samples/seconds \\
+ $EnvelopeDifference$ & difference between two doppler envelopes & Hz \\
+ $MaxUpperEnvelope$ & Array of values corresponding to the maximum of each azimuth or elevation upper envelope calculation & Hz \\
+ $MinLowerEnvelope$ & Array of values corresponding to the minimum of each azimuth or elevation lower envelope calculation & Hz \\
+ $BladeLength$ & Length of single rotor blade (radius of rotor) & meters \\
+ $f_c$ & Center Frequency & Hz \\
+ $R_{Estimate}$ & Estimated reflection radius & meters \\
+ $f_{DopplerMax}$ & The maximum amount of doppler for a particular blade length and RPM & Hz \\
+ $f_{DopplerCorrect}$ & The corrected doppler per $\theta_{Az}$ to be processed & Hz \\
+ $A_{shift}$ & The amount of shift needed to correct for Blade pitch & Hz \\
 }
@@
 \addtocontents{toc}{\vspace{1em}}  % Add a gap in the Contents, for aesthetics
-In RF communications with a rotorcraft, such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM).
+In RF communications with a rotorcraft such as a helicopter, the rotor blades can impart a modulation onto the received signal called Rotor Blade Modulation (RBM).
 This modulation is caused by the reflection of a signal off the rotating blades.
@@
 The developed program is based on optical ray tracing algorithms with modified physical propagation effects for RF signals, and swapping lights and cameras for RF transmitters and receivers respectively.
-The ray tracer was then run over a realistic set of physical parameters to determine their effects on the received signal, this includes transmitter azimuth and elevation angle, receiver position, blade pitch, etc.
+The ray tracer was then run over a realistic set of physical parameters to determine their effects on the received signal; this includes transmitter azimuth and elevation angle, receiver position, blade pitch, etc.
 along with their combinations.
-From the simulations the azimuth and elevation angle, of the transmitter, produce predictable modulations on the received signal.
-Based on the trends in the signal's modulation a DSP algorithm was distilled down that accurately determines the azimuth and elevation angle of the transmitter from simulated signal data.
+The simulations of the azimuth and elevation angle produce predictable modulations on the received signal.
+Based on the trends in the signal's modulation, a DSP algorithm was distilled down that accurately determines the azimuth and elevation angle of the transmitter from simulated signal data.
 }

### 2016-10-19 Radio_Propagation_Simulation.tex
add bold theory figure, add legends to verify figures

@@
 %introduce the section and what will be discussed here
-The simulation software is broken down into three main components, the radio wave propagation model, the scene model, and the ray tracing engine.
+The simulation software is broken down into three main components; the radio wave propagation model, the scene model, and the ray tracing engine.
 The wave propagation model is a collection of equations that describe the physical phenomena that affect the propagation when represented by rays.
@@
 The receiver and transmitter will also be defined in the same environment with simulated characteristics to match real life conditions.
-The ray tracing engine uses recursive execution described in \cite{Whitted1979}, replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
+The ray tracing engine uses recursive execution described by Whitted in \cite{Whitted1979}, replacing cameras and lights for receivers and transmitters respectively in a three dimensional environment.
 
@@
 %define the math behind the physical laws that are simulated within the simulation
-The propagation model defined in this project is based on the following physical phenomena; free-space path loss, reflection, and the doppler effect.
-They are all formally established models described in full in \cite{Bertoni1999}, \cite{Parsons2000}, and \cite{Willis2005}.
+The propagation model defined in this project is based on the following physical phenomena; free-space path loss, reflection, fading, and the doppler effect.
+Which are all formally established models described in \cite{Bertoni1999, Parsons2000, Willis2005}.
 Although several effects are described within the model several were left out to simplify the computation due to the overhead of implementation in 3D space and because of the assumptions made about the scene model.
@@
 %describe path loss
-Free-Space path loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power is
+Free-Space Path Loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power by
 
@@
 The hemisphere is centered at the point the ray hits, producing rays away from the surface.
-To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007}, \cite{Pharr2010}, \cite{Glassner1995}.
+To approximate a particular type of surface the rays power is attenuated by the surface's bi-directional reflectance distribution function (BRDF) \cite{Suffern2007, Pharr2010, Glassner1995}.
 There are several ways of calculating the BRDF, but the simplest is the Phong BRDF which will be used in this ray tracing implementation \cite{Phong:1998:ICG:280811.280980}.
@@
 Since this was not designed for the longer wavelengths used in RF communications, an assumption is made about surface features.
-Where features relevant to light waves,  produce a reflectance distribution similar for this application.
+Where surface features, relevant to light waves,  produce a reflectance distribution similar for this application.
 
@@
 where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection.
-This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
+This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
 
@@
 
-where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$
+where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$. The velocity in the direction of the transmitter is given by
 
@@
 $\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_t}$ is the normalized vector that is in the direction of the transmitted ray.
+The velocity in the direction of the reflection is given by
 
@@
 %go over the shape of the blade
-The rotor blade is the most complex object within the scene, due to its airfoil shape.
 The airfoil shape is designed to produce lift for the helicopter, and designing one is outside the scope of this project.
@@
 The primitive shapes are triangles that span between the ribs and go around to cover the surface.
-This was done using a lightweight mesh generation method using a priori knowledge of the blade's shape.
+This was done using a lightweight mesh generation method using knowledge of the blade's finished shape.
 The designed algorithm, located in \ref{class_blade__surface_a160959f632ad73eff846aeea81aa84ae} $create\_surface()$ method, takes advantage of the object's uniform structure in 2D.
@@
 Starting with the airfoil shape, which is defined by a set of 2D coordinates.
-The length and the number of rib sections can be configured along with the number of blades and corresponding altitude.
-As well as the RPM.
+The length and the number of rib sections can be configured along with the number of blades and corresponding altitude, as well as the RPM.
 This allows the scene to replicate any type of rotor configuration and position it at a specific altitude.
@@
 The transmitter is modeled as a point source, this means that all the radio waves are projected from this point into the scene.
-It is assumed that the transmitter is located on the ground within the x,y plane in relationship to the rotor blades.
+It is assumed that the transmitter is located on the ground within the x,y plane in relation to the rotor blades.
 The transmitter is configured with a center frequency and is assumed to produce a tone at that frequency.
@@
 Being that the transmitter is emitting radio waves into a 3D space, it is assumed to be transmitting in an omnidirectional fashion.
-But because the rotor and the receiver are the only two other objects within the scene, radio waves will only be propagated in their direction.
+The rotor and the receiver are the only two other objects within the scene, radio waves will only be propagated in their direction.
 This limitation allows for a higher concentration of rays to be casted, resulting in a higher resolution picture that eliminates computational overhead for the tracing engine.
@@
 %processing in each frame
-The sample is produced using superposition of all the rays that are acting on the receiver at that instance in time which are then extrapolated to produce a clear result.
+The sample is produced using superposition of all the rays that are acting on the receiver at that instance, which are then extrapolated to produce a clear result.
 %realism
-The receiver is configurable allowing the user to set a desired center frequency along with the sampling rate of the simulated hardware.
+The receiver is configurable which allows the user to set a desired center frequency along with the sampling rate of the simulated hardware.
 The sampling rate will determine several simulation parameters in the ray tracer due to the need to associate this rate with the change in the rotor position for the next frame.
@@
 %flow of the program
-The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene.
-Then the number of frames that will be computed.
+The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene, then the number of frames that will be computed.
 The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver defined before the beginning of the simulation.
@@
 	= \begin{pmatrix}
-			\sqrt{r} \cos{\theta_u}  + d_x\\
-			\sqrt{r} \sin{\theta_u}  + d_y \\
+			\sqrt{r_u} \cos{\theta_u}  + d_x\\
+			\sqrt{r_u} \sin{\theta_u}  + d_y \\
 			d_z \\
@@
 
+where $r_u$ and $\theta_u$ are uniformly distributed random variables from $0 \leq r_u \leq BladeLength^{2}$ and $ 0 \leq \theta_u \leq 2\pi$ respectively.
+
 The casting technique reduces the computation overhead by limiting the search space.
-It also creates a higher resolution result by focusing the limited number of rays in the direction of the other objects shown in figure \ref{fig:samp_method}.
+It also creates a higher resolution result by focusing the limited number of rays in the direction of the other objects shown in Figure \ref{fig:samp_method}.
 
@@
 The power level is adjusted based on the BRDF of the specific material.
-Due to only the rotor and receiver being in the scene, rays that are found to hit the rotor are reflected, then a dedicated ray in the direction of the receiver is also calculated with a decayed power and adjusted frequency respective to the reflection.
+Due to only the rotor and receiver being in the scene, rays that are found to hit the rotor are reflected accordingly.
+Then a dedicated ray, in the direction of the receiver, is also calculated with a decayed power and adjusted frequency respective to the reflection.
 

### 2016-10-19 Ray_Tracing_Software.tex
add bold theory figure, add legends to verify figures

@@
 The ray tracing software developed during the course of the thesis is written in C++ in an XCode environment, but a generic implementation is provided to run on other operating systems.
-This code is loosely based on the work of Eric Degroot's developed for \cite{Groot2015} and implemented some modified base classes developed by him.
+This code is loosely based on the work Eric Degroot developed for \cite{Groot2015} and implemented some modified base classes developed by him.
 It is a specific tool for analyzing the affects of rotor blade modulation on a signal tone, it does not provide generic 3D ray tracing in order to optimize the performance for this task.
@@
 First a file containing the points that define the 2D section of the airfoil shape, one default file is included in the software package for ease of use and as a template for other airfoil shapes.
-
-the other key parameters that define the simulation are shown in Table \ref{tab:key_values}
+The other key parameters that define the simulation are shown in Table \ref{tab:key_values}
 
@@
 
-On Linux machines the code must first be built using make with the main file configured before hand. Then run the Raytracer3D executable.
+On Linux machines the code must first be built using Make with the main file configured before hand. Then run the Raytracer3D executable.
 

### 2016-10-19 Results_new.tex
add bold theory figure, add legends to verify figures

@@
 The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter.
-First the azimuth angle will be estimated which will provide the information necessary for calculating the elevation angle.
+First the azimuth angle will be estimated which will provide the information necessary for also calculating the elevation angle.
 The results of the estimation techniques are then analyzed to determine their accuracy.
@@
 
-From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. By computing the difference of the two
+From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. We then take the difference
 
@@
 where $Max Upper Envelope$ is an array of the maximum value of each upper envelope calculation, and $Min Lower Envelope$ is an array of the minimum value of each lower envelope calculation.
-$Envelope Difference$ is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.
+The result is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.
 
@@
 Now we have a minimum value that should denote the 90\textdegree \space location and the two peak locations that denote the 90\textdegree \space and 270\textdegree \space locations.
-Because it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.
+Since it is possible that the minimum could find the wrong peak for the 90\textdegree \space location we can compare the peak locations on the average power data, that was used to find the successive average during data collection, to determine which location is actually 90\textdegree.
 
@@
 
-From there the Minimum method and the peak method can be compared to see if they agree on the 90\textdegree \space location.
-If this is not the case one will be chosen and the helicopter can fly in that direction and measure based on the physical movement of the helicopter or if the resulting envelope got larger or smaller because of the change in elevation angle.
+From there the minimum method and the peak method can be compared to see if they agree on the 90\textdegree \space location.
+If this is not the case one will be chosen and the helicopter can fly in that direction.
+The resulting Doppler can then be measured, based on the physical movement of the helicopter or if the resulting envelope, to confirm the correct 90\textdegree \space location.
 
@@
 Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxUpperEnvelope$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate.
-we then solve for the elevation angle
+We then solve for the elevation angle
 
@@
 
-If we now consider a pitched blade the above method for estimating Azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side.
+If we now consider a pitched blade the above method for estimating azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side.
 To correct this error we need to correct both the difference calculation and the correct Doppler data accordingly.

### 2016-10-19 Simulation.tex
add bold theory figure, add legends to verify figures

@@
 This allows for computations to be done in the time frequency domain and provides an accurate picture of how the signal is changing with time.
-Figure \label{fig:test_spec} shows an example of the computed spectrograms.
+Figure \ref{fig:test_spec} shows an example of the computed spectrograms.
 
@@
 The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values.
-The power level to set the threshold is calculated differently based on weather the elevation or the azimuth parameter is being swept.
+The power level to set the threshold is calculated differently based on whether the elevation or the azimuth parameter is being swept.
 For the azimuth angle sweep, which will be shown later in section \ref{taa}, the maximum power is found in each time slice then those values are averaged.
@@
 
-Comparing Figure \ref{fig:rx_position_0m} with \ref{fig:rx_position_7m} the max Doppler reflects the information in Figure \ref{fig:rx_position} and the overall envelope is affected.
-The envelope in Figure \ref{fig:rx_position_0m} is much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the envelope of this second figure has a more distinct shape with less variation between its two peaks.
+Comparing the received signal envelopes Figure \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m} the maximum Doppler increase reflects the information in Figure \ref{fig:rx_position}.
+The envelope in Figure \ref{fig:rx_position_0m} is also much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the signal envelope, for the receiver is at 7 m, has a distinctive shape with less variation between its two peaks.
 The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}.
@@
 
-In Figure \ref{fig:pitch_tx_elevation_angle} the max Doppler versus elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and, consequently, have changed in slope.
+In Figure \ref{fig:pitch_tx_elevation_angle} the maximum Doppler versus elevation angles are initially shifted up in frequency from a pitch of 0\textdegree \space and, consequently, have changed in slope.
 This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel.

### 2016-10-19 Thesis MATLAB Scripts/Envelope.m

@@ -2,7 +2,7 @@
 clear;
 %test_locationdatainfile_4
 %Altitude_200m/rx_test_Bistatic_dop0.000000rad2
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/rx_test_Bistatic_dop0.628319rad.csv');
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/rx_test_Bistatic_dop3.141593rad.csv');
 rpm = 250;
 
 %B = horzcat(samples,samples)';

### 2016-10-19 Thesis MATLAB Scripts/max_doppler_0deg_rx_offset.m

@@ -28,5 +28,6 @@ plot(360*elevation_angle/(2*pi),doppler_minus)
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-title('Doppler Frequency vs. Elevation angle for 0deg Transmitter Azimuth');
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Theoretical Doppler Frequency vs. Elevation angle for 0deg Transmitter Azimuth');
 

### 2016-10-19 Thesis MATLAB Scripts/max_doppler_180deg_rx_offset.m

@@ -14,16 +14,18 @@ max_fd = 2*(v*fc)/c;
 Tx_radius = 0:1:450;
 elevation_angle = atan(Altitude./(Tx_radius));
 
-doppler_plus = -ones(1,length(Tx_radius));
 doppler_minus = max_fd*cos(elevation_angle);
+doppler_plus = -ones(1,length(Tx_radius));
+
 
 hold on
-plot(360*elevation_angle/(2*pi),doppler_plus)
 plot(360*elevation_angle/(2*pi),doppler_minus)
+plot(360*elevation_angle/(2*pi),doppler_plus)
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-title('Doppler Frequency vs. Elevation angle for 180deg Transmitter Azimuth');
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Theoretical Doppler Frequency vs. Elevation angle for 180deg Transmitter Azimuth');
 
 % %Rx position (might not be needed)
 % Rx_z = Altitude - 2;

### 2016-10-19 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -26,7 +26,8 @@ plot(360*elevation_angle/(2*pi),doppler_minus)
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
 
  i = 0.01:.01:7;
  el = fliplr(atan(2./i));
@@ -41,4 +42,5 @@ title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
  hold off
  xlabel('Elevation Angle (deg)');
  ylabel('Doppler Frequency (Hz)');
- title('Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
+ legend('Max Upper Envelope', 'Min Lower Envelope');
+ title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');

### 2016-10-19 Thesis MATLAB Scripts/max_doppler_90deg_rx_offset.m

@@ -31,6 +31,7 @@ plot(360*elevation_angle/(2*pi),-max_fd*cos(elevation_angle))
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-title('Doppler Frequency vs. Elevation angle for 90deg Transmitter Azimuth');
+legend('Max Upper Envelope', 'Min Lower Envelope');
+title('Theoretical Doppler Frequency vs. Elevation angle for 90deg Transmitter Azimuth');
 
 

### 2016-10-19 Thesis MATLAB Scripts/max_doppler_theory.m

@@ -36,7 +36,7 @@ for r = Tx_radius
 end
 hold on
 for j = 1:5
-    plot(360*Rotor_angle/(2*pi),data(j,:))
+    plot(360*Rotor_angle/(2*pi),data(j,:),'linewidth',4)
 end
 hold off
 axis([0 360 -600 600]);

### 2016-10-19 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -27,7 +27,7 @@ pitch_corrected = 0;
 %--------------------------------------------------------------------------
 
 %shift data for different start sections
-%data = circshift(data,31,1);
+%data = circshift(data,11,1);
 
 data_table = zeros(num_files,3);
 
@@ -102,7 +102,7 @@ difference = data_table(:,1) - abs(data_table(:,2));
 %correct for pitch
 zero_correct = max(data_table(:,1)) - abs(min(data_table(:,2)));
 if(zero_correct > .1*max(difference))
-    difference = difference - (zero_correct/2);
+    difference = difference - (zero_correct/1);
     pitch_corrected = 1;
 end
 
@@ -117,22 +117,28 @@ end
 
 %for pitch correction
 if(pitch_corrected)
-    w = 0:(2*pi/(num_files-1)):2*pi;
-    correct_fd = correct_fd + (zero_correct/2)*cos(w);
+    %w = 0:(2*pi/(num_files-1)):2*pi;
+    %correct_fd = correct_fd + (zero_correct/2)*cos(w);
+    difference = difference + (zero_correct/2);
[…]

### 2016-10-19 Thesis MATLAB Scripts/test_reflection_power_loss.m

@@ -1,0 +1,8 @@
+%test reflection power
+theta_i = pi/100;
+epsilon = 0.001;
+P_i = 10;
+
+theta_t = asin(sin(theta_i)/sqrt(epsilon));
+Gamma = (cos(theta_i) - sqrt(epsilon)*cos(theta_t))/(cos(theta_i) + sqrt(epsilon)*cos(theta_t));
+P_reflected = P_i*abs(Gamma);

### 2016-10-24 Background.tex
starting edits for figures, got to end of azimuth sim

@@
 The received signal is then used to create a mapping between the amount of Doppler present and the position of the transmitter on the ground.
+
+\section{Thesis Scope}
+\textcolor{red}{ADD WHAT THIS THESIS IS AND POINT OUT WHAT IT IS NOT!}
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/background/2d_theoretical_doppler_profile.eps}
+		\includegraphics[width=15cm]{images/background/2d_theoretical_doppler_profile.eps}
 		\caption{Doppler Frequency vs. Rotor Position with varying Elevation Angle}
@@
 \begin{equation}
-	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{Limited})
+	MaxDopplerProfile = f_{DopplerMax}cos(\theta_{Limited})
 	\label{eq:theory_90_upper}
@@
 \begin{equation}
-	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{Limited})
+	MinDopplerProfile = -f_{DopplerMax}cos(\theta_{Limited})
 	\label{eq:theory_90_lower}
@@
 
-where $MaxUpperEnvelope$ is an array of the maximum upper envelope values for each elevation sample, $MinLowerEnvelope$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range
+where $MaxDopplerProfile$ is an array of the maximum upper envelope values for each elevation sample, $MinDopplerProfile$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range
 
 \begin{equation}
-	\theta_{Limited} = atan\left(\frac{Rx_z}{[0,\dots, (BladeLength - Rx_y)]}\right)
+	\theta_{Limited} = atan\left(\frac{Rx_z}{[0,\dots, (r_b - Rx_y)]}\right)
 	\label{eq:theory_90_limited}
@@
 
-where $Rx_z$ is the receivers position below the rotor head, $BladeLength$ is the length of the rotor blade, and $Rx_y$ is the receivers position on the Y axis.
+where $Rx_z$ is the receivers position below the rotor head, $r_b$ is the length of the rotor blade, and $Rx_y$ is the receivers position on the Y axis.
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/background/3d_geometry_tx_90az_doppler_profile.eps}
+		\includegraphics[width=15cm]{images/background/3d_geometry_tx_90az_doppler_profile.eps}
 		\caption{Doppler profile of Tx at Azimuth angle of 90\textdegree}
@@
 \begin{equation}
-	\theta_{Limited} = atan\left(\frac{Rx_z}{[0, \dots, BladeLength]}\right)
+	\theta_{Limited} = atan\left(\frac{Rx_z}{[0, \dots, Rx_y]}\right)
 	\label{eq:theory_270_limited}
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/background/3d_geometry_tx_270az_doppler_profile.eps}
+		\includegraphics[width=15cm]{images/background/3d_geometry_tx_270az_doppler_profile.eps}
 		\caption{Doppler profile of Tx at Azimuth angle of 270\textdegree}
@@
 \begin{equation}
-	MaxUpperEnvelope = f_{DopplerMax}cos(\theta_{El})
+	MaxDopplerProfile = f_{DopplerMax}cos(\theta_{El})
 	\label{eq:theory_180_upper}
@@
 
-and the $MinLowerEnvelope$ is set to 0 for the range.
+and the $MinDopplerProfile$ is set to 0 for the range.
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/background/3d_geometry_tx_180az_doppler_profile.eps}
+		\includegraphics[width=15cm]{images/background/3d_geometry_tx_180az_doppler_profile.eps}
 		\caption{Doppler profile of Tx at Azimuth angle of 180\textdegree}
@@
 
-Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree.
+Figure \ref{fig:3D_model_180az_doppler} shows the maximum and minimum Doppler profile values versus elevation angle for a transmitter at an azimuth angle of 180\textdegree.
 The data from the figure shows the maximum, of the Doppler profile, decrease as the elevation angle gets larger.
@@
 \begin{equation}
-	MinLowerEnvelope = -f_{DopplerMax}cos(\theta_{El})
+	MinDopplerProfile = -f_{DopplerMax}cos(\theta_{El})
 	\label{eq:theory_0_lower}
@@
 
-and the $MaxUpperEnvelope$ is set to 0 for the range.
+and the $MaxDopplerProfile$ is set to 0 for the range.
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/background/3d_geometry_tx_0az_doppler_profile.eps}
+		\includegraphics[width=15cm]{images/background/3d_geometry_tx_0az_doppler_profile.eps}
 		\caption{Doppler profile of Tx at Azimuth angle of 0\textdegree}
@@
 
-Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum Doppler envelope values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree.
+Figure \ref{fig:3D_model_0az_doppler} shows the maximum and minimum Doppler profile values versus elevation angle for a transmitter at an azimuth angle of 0\textdegree.
 The data from the figure shows the minimum of the Doppler profile increase as the elevation angle gets larger.

### 2016-10-24 MSc. Thesis Template.tex
starting edits for figures, got to end of azimuth sim

@@
  $\theta_i$ & Angle of incidence with an objects normal & radians \\
- $d$ & Total distance traveled by a ray & meters \\ 
- $t_0$ & Starting time in a frame & seconds \\
  $r$ & A radius along the length of the blade & meters \\
@@
  $f_s$ & sampling frequency & samples/seconds \\
- $EnvelopeDifference$ & difference between two doppler envelopes & Hz \\
- $MaxUpperEnvelope$ & Array of values corresponding to the maximum of each azimuth or elevation upper envelope calculation & Hz \\
- $MinLowerEnvelope$ & Array of values corresponding to the minimum of each azimuth or elevation lower envelope calculation & Hz \\
- $BladeLength$ & Length of single rotor blade (radius of rotor) & meters \\
+ $ProfileDifference$ & Difference between two Doppler profiles & Hz \\
+ $MaxDopplerProfile$ & Array of values corresponding to the maximum of each azimuth or elevation doppler profile calculation & Hz \\
+ $MinDopplerProfile$ & Array of values corresponding to the minimum of each azimuth or elevation doppler profile calculation & Hz \\
+ $r_b$ & Length of single rotor blade (radius of rotor) & meters \\
  $f_c$ & Center Frequency & Hz \\

### 2016-10-24 Radio_Propagation_Simulation.tex
starting edits for figures, got to end of azimuth sim

@@
 
-\begin{equation}
-	F = cos\left(2\pi \frac{d}{c} + t_0\right)
-	\label{eqn:fading_coeff}
-\end{equation}
+\textcolor{red}{FIGURE OUT WHAT TO PUT HERE FOR FADING COEFFICIENT?}
 
-where $F$ is the fading coefficient, $d$ is the total distance the particular ray has traveled, $c$ is the speed of light, and $t_0$ is the starting time of the current frame.
 The power can then be calculated using
 
-\begin{equation}
-	P_{faded} = PF
-	\label{eqn:power_faded}
-\end{equation}
+\textcolor{red}{FADING POWER?}
 
-where $P_{faded}$ is the adjusted power due to fading and $P$ is the signal power. The superposition of each ray's faded power becomes the received signal.
+The superposition of each ray's faded power becomes the received signal.
 
@@
 %define doppler effect
-The Doppler effect is characterized by
-
-%Doppler formula
-\begin{equation}
-	f = \left ( \frac{c + v_r}{c + v_s} \right ) f_0
-	\label{eqn:formalDop}
-\end{equation}
-
 It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades.
@@
 where $f_0$ is the initial transmitted frequency, $\lambda$ is the wavelength, $v_t$ is the velocity in the direction of the transmitter, and $v_r$ is the velocity in the direction of the reflection.
-This is similar to the Bistatic radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
+This is similar to the Bi-static radar equation for Doppler, but since the reflection is not guaranteed to be toward the receiver we calculate the Doppler as it makes contact with the surface and as it is re-radiated according the blades direction of travel.
 
@@
 
+\textcolor{red}{ADD MORE ABOUT RAY TRACING}
+
 \subsection{Computation}

### 2016-10-24 Simulation.tex
starting edits for figures, got to end of azimuth sim

@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram.eps}
+		\includegraphics[width=15cm]{images/simulation/test_analysis_spectrogram.eps}
 		\caption{Example Spectrum for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/simulation/test_analysis_spectrogram_with_envelope.eps}
+		\includegraphics[width=15cm]{images/simulation/test_analysis_spectrogram_with_envelope.eps}
 		\caption{Example Spectrum with Doppler Profile for one Blade revolution with transmitter at Azimuth of 45\textdegree \space and Elevation of 35\textdegree}
@@
 		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_200_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 45\textdegree}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 45\textdegree}
 		\label{fig:tx_azimuth_angle_200}
@@
 		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_50_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 76\textdegree}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 76\textdegree}
 		\label{fig:tx_azimuth_angle_50}
@@
 		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_400_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 26.5\textdegree}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Tx Elevation at 26.5\textdegree}
 		\label{fig:tx_azimuth_angle_400}

### 2016-10-24 Thesis MATLAB Scripts/Envelope.m

@@ -2,7 +2,7 @@
 clear;
 %test_locationdatainfile_4
 %Altitude_200m/rx_test_Bistatic_dop0.000000rad2
-samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/bistatic_azimuth_45_pitch/rx_test_Bistatic_dop3.141593rad.csv');
+samples = csvread('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/.csv');
 rpm = 250;
 
 %B = horzcat(samples,samples)';
@@ -57,9 +57,9 @@ figure;
 hold on
 plot3(t*1000,smooth(lower_envelope/1e6,.02),z,'b','linewidth',4)
 plot3(t*1000,smooth(upper_envelope/1e6,.02),z,'r','linewidth',4)
-plot3(t*1000,cos(angle_b1(1:end-1)),z);
-plot3(t*1000,cos(angle_b2(1:end-1)),z);
-legend('Lower Envelope','Upper Envelope');
+%plot3(t*1000,cos(angle_b1(1:end-1)),z);
+%plot3(t*1000,cos(angle_b2(1:end-1)),z);
+legend('Lower Doppler Profile','Upper Doppler Profile');
 spectrogram(samples,5000,500,5000,fs_real,'yaxis','centered')
 hold off
 ylabel('Doppler Frequency (kHz)');

### 2016-10-24 Thesis MATLAB Scripts/Signal_analysis_w_metadata.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//*.csv');
 num_files = length(files);
 %data = zeros(num_files,959006); %479000;
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m//',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -117,7 +117,7 @@ hold on
 plot(Azimuth,data_table(:,1))
 plot(Azimuth,data_table(:,2))
 hold off
-legend('Max Upper Envelope', 'Min Lower Envelope');
+legend('Max Doppler Profile', 'Min Doppler Profile');
 title('Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with 7.5deg Pitch');
 xlabel('Transmitter Azimuth Angle (deg)');
 ylabel('Doppler Frequency (Hz)');

### 2016-10-24 Thesis MATLAB Scripts/elevationEstimation_on_data_with_metadata.m

@@ -85,8 +85,8 @@ end
 
 figure;
 hold on
-plot((location_data(:,5)/(2*pi))*360,-data_table(:,2))
-plot((location_data(:,5)/(2*pi))*360,-data_table(:,1))
+plot((location_data(:,5)/(2*pi))*360,data_table(:,2))
+plot((location_data(:,5)/(2*pi))*360,data_table(:,1))
 hold off
 legend('Max Upper Envelope', 'Min Lower Envelope');
 title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle');

### 2016-10-24 Thesis MATLAB Scripts/max_doppler_0deg_rx_offset.m

@@ -28,6 +28,6 @@ plot(360*elevation_angle/(2*pi),doppler_minus)
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-legend('Max Upper Envelope', 'Min Lower Envelope');
+legend('Max Doppler Profile', 'Min Doppler Profile');
 title('Theoretical Doppler Frequency vs. Elevation angle for 0deg Transmitter Azimuth');
 

### 2016-10-24 Thesis MATLAB Scripts/max_doppler_180deg_rx_offset.m

@@ -24,7 +24,7 @@ plot(360*elevation_angle/(2*pi),doppler_plus)
 hold off
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
-legend('Max Upper Envelope', 'Min Lower Envelope');
+legend('Max Doppler Profile', 'Min Doppler Profile');
 title('Theoretical Doppler Frequency vs. Elevation angle for 180deg Transmitter Azimuth');
 
 % %Rx position (might not be needed)

### 2016-10-24 Thesis MATLAB Scripts/max_doppler_270deg_rx_offset.m

@@ -30,7 +30,8 @@ legend('Max Upper Envelope', 'Min Lower Envelope');
 title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
 
  i = 0.01:.01:7;
- el = fliplr(atan(2./i));
+ b = fliplr(i);
+ el = (atan(2./i));
  v = ((2*pi)/60)*RPM*2;%? i or 2 .....
  max_fd = 2*(v*fc)/c;
  doppler_plus = max_fd.*(cos(el));
@@ -40,7 +41,10 @@ title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter 
  plot(360*el/(2*pi),doppler_plus)
  plot(360*el/(2*pi),doppler_minus)
  hold off
- xlabel('Elevation Angle (deg)');
- ylabel('Doppler Frequency (Hz)');
- legend('Max Upper Envelope', 'Min Lower Envelope');
- title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth');
+xlabel('Elevation Angle (deg)','FontSize', 14);
+ylabel('Doppler Frequency (Hz)','FontSize', 14);
+legend('Max Doppler Profile', 'Min Doppler Profile');
+title('Theoretical Doppler Frequency vs. Elevation angle for 270deg Transmitter Azimuth','FontSize', 14);
+ 
+ test = b.*cos(el);
+ 

### 2016-10-24 Thesis MATLAB Scripts/max_doppler_90deg_rx_offset.m

@@ -29,9 +29,9 @@ hold on
 plot(360*elevation_angle/(2*pi),max_fd*cos(elevation_angle))
 plot(360*elevation_angle/(2*pi),-max_fd*cos(elevation_angle))
 hold off
-xlabel('Elevation Angle (deg)');
-ylabel('Doppler Frequency (Hz)');
-legend('Max Upper Envelope', 'Min Lower Envelope');
-title('Theoretical Doppler Frequency vs. Elevation angle for 90deg Transmitter Azimuth');
+xlabel('Elevation Angle (deg)','FontSize', 14);
+ylabel('Doppler Frequency (Hz)','FontSize', 14);
+legend('Max Doppler Profile', 'Min Doppler Profile');
+title('Theoretical Doppler Frequency vs. Elevation angle for 90deg Transmitter Azimuth','FontSize', 14);
 
 

### 2016-10-24 Thesis MATLAB Scripts/plot_elevation_range_vs_pitch_2_ranges.m

@@ -19,7 +19,7 @@ plot(data_both(:,4),data_15(:,1));
 hold off
 
 legend('Pitch 0deg', '7.5deg', '15deg');
-title('Max Envelope Frequencies vs Transmitter Elevation Angle');
+title('Max Doppler Profile Frequencies vs Transmitter Elevation Angle');
 xlabel('Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 

### 2016-10-24 Thesis MATLAB Scripts/signal_analysis.m

@@ -1,11 +1,11 @@
 clear;
-total_samples = 959000;%479000; 
+total_samples = 479000;%959000 
 
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/*.csv');
 num_files = length(files);
 data = zeros(num_files,total_samples);
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/',files(i).name)));
 end
 
 rpm = 250;
@@ -51,18 +51,18 @@ for i=1:num_files
     lower_envelope = smooth(lower_envelope,.02);
     upper_envelope = smooth(upper_envelope,.02);
     
-    figure;
-    
-    hold on
-    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
-    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
-    plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
-    spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
-    colormap(jet);
-    colorbar
-    view(2)
-    title(files(i).name);
-    hold off
+%     figure;
+%     
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+%     spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered')
+%     colormap(jet);
+%     colorbar
+%     view(2)
+%     title(files(i).name);
+%     hold off
 %     
 %     upper_envelope_table(i,:) = upper_envelope;
 %     lower_envelope_table(i,:) = lower_envelope;
@@ -78,14 +78,14 @@ for i=1:num_files
     
 end
 
[…]

### 2016-10-24 Thesis MATLAB Scripts/signal_analysis_pitch_0tx_pos.m

@@ -52,29 +52,29 @@ for i=1:num_files
     lower_envelope = smooth(lower_envelope,.02);
     upper_envelope = smooth(upper_envelope,.02);
     
-    figure;
-    hold on
-    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
-    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
-    %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
-    %plot3(t/60,cos(angle_b1(1:end-1)),z);
-    %plot3(t/60,cos(angle_b2(1:end-1)),z);
-    spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered')
-    title(files(i).name);
-    hold off
-    colormap(jet);
-    colorbar
-    view(2)
-    
-    figure;
-    hold on
-    plot3(t_fixed,upper_envelope,z,'r','linewidth',4)
-    plot3(t_fixed,lower_envelope,z,'b','linewidth',4)
-    title(files(i).name);
-    legend('Upper Envelope', 'Lower Envelope');
-    xlabel('Time (s)');
-    ylabel('Doppler Frequency (Hz)');
-    hold off
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+%     %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+%     %plot3(t/60,cos(angle_b1(1:end-1)),z);
+%     %plot3(t/60,cos(angle_b2(1:end-1)),z);
+%     spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered')
+%     title(files(i).name);
+%     hold off
+%     colormap(jet);
+%     colorbar
+%     view(2)
+%     
+%     figure;
+%     hold on
+%     plot3(t_fixed,upper_envelope,z,'r','linewidth',4)
+%     plot3(t_fixed,lower_envelope,z,'b','linewidth',4)
+%     title(files(i).name);
+%     legend('Upper Envelope', 'Lower Envelope');
+%     xlabel('Time (s)');
+%     ylabel('Doppler Frequency (Hz)');
+%     hold off
     
     data_table(i,2) = min(lower_envelope);
[…]

### 2016-10-24 Thesis MATLAB Scripts/signal_analysis_pitch_135deg.m

@@ -48,29 +48,29 @@ for i=1:num_files
     lower_envelope = smooth(lower_envelope,.02);
     upper_envelope = smooth(upper_envelope,.02);
     
-    figure;
-    hold on
-    plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
-    plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
-    %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
-    %plot3(t/60,cos(angle_b1(1:end-1)),z);
-    %plot3(t/60,cos(angle_b2(1:end-1)),z);
-    spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered')
-    title(files(i).name);
-    hold off
-    colormap(jet);
-    colorbar
-    view(2)
-    
-    figure;
-    hold on
-    plot3(t_fixed,upper_envelope,z,'r','linewidth',4)
-    plot3(t_fixed,lower_envelope,z,'b','linewidth',4)
-    title(files(i).name);
-    legend('Upper Envelope', 'Lower Envelope');
-    xlabel('Time (s)');
-    ylabel('Doppler Frequency (Hz)');
-    hold off
+%     figure;
+%     hold on
+%     plot3(t/60,lower_envelope/1000,z,'w','linewidth',4)
+%     plot3(t/60,upper_envelope/1000,z,'w','linewidth',4)
+%     %plot3(t/60,f(nd)/1000,q,'r','linewidth',4)
+%     %plot3(t/60,cos(angle_b1(1:end-1)),z);
+%     %plot3(t/60,cos(angle_b2(1:end-1)),z);
+%     spectrogram(data(i,:),5000,4000,5000,fs,'reassign','MinThreshold',-SNR,'yaxis','centered')
+%     title(files(i).name);
+%     hold off
+%     colormap(jet);
+%     colorbar
+%     view(2)
+%     
+%     figure;
+%     hold on
+%     plot3(t_fixed,upper_envelope,z,'r','linewidth',4)
+%     plot3(t_fixed,lower_envelope,z,'b','linewidth',4)
+%     title(files(i).name);
+%     legend('Upper Envelope', 'Lower Envelope');
+%     xlabel('Time (s)');
+%     ylabel('Doppler Frequency (Hz)');
+%     hold off
     
     data_table(i,2) = min(lower_envelope);
[…]

### 2016-10-24 Thesis MATLAB Scripts/signal_analysis_rx_position_y.m

@@ -69,7 +69,7 @@ for i=1:num_files
     plot3(t_fixed,upper_envelope,z,'r','linewidth',4)
     plot3(t_fixed,lower_envelope,z,'b','linewidth',4)
     title(files(i).name);
-    legend('Upper Envelope', 'Lower Envelope');
+    legend('Upper Doppler Profile','Lower Doppler Profile');
     xlabel('Time (s)');
     ylabel('Doppler Frequency (Hz)');
     hold off
@@ -84,7 +84,7 @@ hold on
 plot(range,data_table(:,1))
 plot(range,data_table(:,2))
 hold off
-legend('Max Upper Envelope', 'Min Lower Envelope');
+legend('Max Doppler Profile', 'Min Doppler Profile');
 title('Max and Min Envelope Frequencies vs Receiver distance');
 xlabel('Rx position (m)');
 ylabel('Doppler Frequency (Hz)');

### 2016-10-24 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/*.csv');
 num_files = length(files);
-data = zeros(num_files,959006); %959000;  479000
+data = zeros(num_files,479000); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/pitch7.5deg_rotation_200m2/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -19,7 +19,7 @@ RPM = 250;
 Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 200;
+tx_range = 50;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -31,8 +31,8 @@ pitch_corrected = 0;
 
 data_table = zeros(num_files,3);
 
-location_data = data(:,1:6);
-data = data(:,7:end);
+%location_data = data(:,1:6);
+%data = data(:,7:end);
 
 for i=1:num_files
     [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
@@ -127,7 +127,7 @@ end
 [Max,Imax] = max(correct_fd);
 
 %peak prominence calc
-min_peak_prominence = (1/(Max - Min))*.01;
+min_peak_prominence = (1/(Max - Min))*.5;
 [pk,lc] = findpeaks(1./correct_fd,'NPeaks',2,'MinPeakProminence',min_peak_prominence);
 
 %double check average power against peaks to fix 90deg
@@ -151,8 +151,8 @@ hold on
 plot(Azimuth,data_table(:,1))
 plot(Azimuth,data_table(:,2))
 hold off
[…]

### 2016-11-17 Background.tex
edits for figures and equations finished, working on scope and noise

@@
 \section{Thesis Scope}
-\textcolor{red}{ADD WHAT THIS THESIS IS AND POINT OUT WHAT IT IS NOT!}
+\textcolor{red}{EDITED}
+
+The scope of this thesis is to investigate whether it is possible to use the effect of RBM to geolocate a transmitter in ideal conditions.
+Under ideal conditions the received signal is deterministic based upon the propagation model and the initial conditions.
+This thesis does not intend to include every physical effect but is limited to the effects defined in the propagation model and by the assumptions made about the physical scene.
+The ray tracing software developed for the thesis is created for the sole purpose of understanding RBM.
+In order to determine the signals interaction with the moving rotor blade in an ideal environment, the ray traced scene is limited to the rotor blades, transmitter and receiver.
+The signal produced by the simulation is used to derive an algorithm that determines both the azimuth and elevation angle of a transmitter.
+The derived algorithm is then evaluated on both the deterministic signal to determine its azimuth and elevation accuracy.
+The algorithm is then tested again on signals in the presence of differing levels of noise to determine the algorithm's performance in a more realistic environment.
 
@@
 
-The resulting Doppler equation is described by
+The resulting Doppler equation is:
 
@@
 
-The equation for modeling the scenario for a transmitter located at 90\textdegree \space azimuth is
+The equation for modeling the scenario for a transmitter located at 90\textdegree \space azimuth is:
 
@@
 
-where $MaxDopplerProfile$ is an array of the maximum upper envelope values for each elevation sample, $MinDopplerProfile$ is an array of minimum lower envelope values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range
+where $MaxDopplerProfile$ is an array of the maximum upper profile values for each elevation sample, $MinDopplerProfile$ is an array of minimum lower profile values for each elevation sample, and $\theta_{Limited}$ is the limited elevation angle range:
 
@@
 %formulate the geometric equations
-The equation for modeling the scenario for a transmitter located at 270\textdegree \space azimuth is similar to the equations for calculating the 90\textdegree \space scenario where $f_{DopplerMax}$ is now calculated with a smaller reflection radius of 2m and $\theta_{Limited}$ is now calculated by
+The equation for modeling the scenario for a transmitter located at 270\textdegree \space azimuth is similar to the equations for calculating the 90\textdegree \space scenario where $f_{DopplerMax}$ is now calculated with a smaller reflection radius of 2m and $\theta_{Limited}$ is:
 
@@
 
-The equation for modeling the scenario for a transmitter located at 180\textdegree \space azimuth is
+The equation for modeling the scenario for a transmitter located at 180\textdegree \space azimuth is:
 
@@
 
-The equation for modeling the scenario for a transmitter located at 0\textdegree \space azimuth is
+The equation for modeling the scenario for a transmitter located at 0\textdegree \space azimuth is:
 

### 2016-11-17 Radio_Propagation_Simulation.tex
edits for figures and equations finished, working on scope and noise

@@
 %describe path loss
-Free-Space Path Loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power by
+Free-Space Path Loss is calculated using the Friis transmission and is incorporated into the model by keeping track of the distance a ray travels and adjusting its power:
 
@@
 \subsubsection{Specular Reflection}
-In the case of a perfect reflection the angle of the reflection is calculated by
+In the case of a perfect reflection the angle of the reflection is:
 
@@
 \subsubsection{Reflection Loss}
-Power loss due to surface reflection is described through the following coefficient
+Power loss due to surface reflection is described through the following coefficient:
 
@@
 %formula description
-where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell's law
+where $\theta_i$ is the angle of incidence with the object's surface normal, $\varepsilon$ is the dielectric constant for that surface, and $\theta_t$ is the angle of refraction as described by Snell's law:
 
@@
 
-The final reflected power is then
+The final reflected power is then:
 
@@
 \subsection{Fading}
-The transmitted signal power experiences fading described by
+\textcolor{red}{EDITED}
 
-\textcolor{red}{FIGURE OUT WHAT TO PUT HERE FOR FADING COEFFICIENT?}
-
-The power can then be calculated using
-
-\textcolor{red}{FADING POWER?}
-
-The superposition of each ray's faded power becomes the received signal.
+The transmitted signal power experiences fading due to multiple signal paths in the environment.
+The resulting signal that the receiver sees is a superposition of the multiple copies of the transmitted signal.
+The difference in signal's attenuation, phase, and delay cause destructive and constructive interference at the receiver.
+In the ray tracing simulation the received signal is calculated by keeping track of the distance each ray travels as well as the reflections, then finding the superposition of those signals which will produce the constructive and destructive interference.
 
@@
 %define doppler effect
-It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades.
-The associated Doppler is calculated using
+It is assumed that both the receiver and the transmitter are not moving therefore, the only Doppler imparted on the signal will be from the rotation of the blades. The associated Doppler is:
 
@@
 
-where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$. The velocity in the direction of the transmitter is given by
+where $\lambda$ is the wavelength of the transmitted signal based off of the speed of light $c$ and its initial frequency $f_0$. The velocity in the direction of the transmitter is:
 
@@
 $\vec{d_p}$ is the normalized vector that is perpendicular to the rotor in its direction of travel and $\vec{d_t}$ is the normalized vector that is in the direction of the transmitted ray.
-The velocity in the direction of the reflection is given by
+The velocity in the direction of the reflection is:
 
@@
 	\begin{center}
-		\includegraphics[width=15cm]{images/radio_propagation/2d_airfoil.png}
+		\includegraphics[width=14cm]{images/radio_propagation/2d_airfoil.png}
 		\caption{Airfoil Cross-Section}
@@
 Starting with the airfoil shape, which is defined by a set of 2D coordinates.
-The length and the number of rib sections can be configured along with the number of blades and corresponding altitude, as well as the RPM.
+The length and the number of rib sections can be configured along with the number of blades and corresponding altitude, as well as the $\omega_r$.
 This allows the scene to replicate any type of rotor configuration and position it at a specific altitude.
@@
 \section{Ray Tracing}
+\textcolor{red}{EDITED}
+
 %describe the core tracing engine and describe the flow of the program
-The ray tracing simulation is conducted in the Monte Carlo fashion acting on the scene and propagation models.
-This method of raytracing is established for creating realistic images in \cite{Suffern2007}, \cite{Pharr2010}.
-The simulation is performed over successive iterations.
-Each iteration is a discrete element called a frame and each frame will be updated to represent the change in the position of the rotor blade.
-
-\textcolor{red}{ADD MORE ABOUT RAY TRACING}
+The ray tracing simulation is conducted in the Monte Carlo fashion acting on the previously described scene and propagation models.
+Ray tracing allows for the calculation of a particle or wave's path within an environment in order to produce photo realistic images.
+This method is established for creating images in \cite{Suffern2007}, \cite{Pharr2010} by tracing light throughout a virtual 3D environment of objects.
+Objects have physical characteristics that determine its shape along with how light rays interact with that object.
+The rays are then casted, in a distributed manner according to the light source, into the scene.
+The image is then built up by evaluating the color and luminance of the ray at each pixel.
+In the case of this simulation light is replaced with RF waves and are evaluated based on the propagation model described, and lights and cameras are replaced with transmitters and receivers respectively.
+The simulation is then performed over successive iterations as the objects move within the scene.
+Each iteration is a discrete element called a frame where each frame is updated to represent the change in the position of the rotor blade.
 
@@
 The ray tracing engine first sets up the environment, creating the surfaces and placing the objects in the scene, then the number of frames that will be computed.
-The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor in RPM and the sampling frequency of the receiver defined before the beginning of the simulation.
-This is described by
+The number of frames is determined by the number of rotations that the rotor makes within the simulation, the speed of the rotor $\omega_r$ and the sampling frequency of the receiver defined before the beginning of the simulation.
+The number of frames in the simulation is:
 
@@
 \begin{equation}
-	Frames = \frac{60  f_s}{RPM} Rev
+	n_{Frames} = \frac{f_s}{\omega_r}\omega_{Rev}
 	\label{eqn:frames}
@@
 
-where $Frames$ is the number of frames that will be computed in the simulation, $f_s$ is the sampling frequency of the receiver, $RPM$ is the revolutions per minuet of the rotor, and $Rev$ is the number of revolutions that the rotor makes in the simulation.
+where $n_{Frames}$ is the number of frames that will be computed in the simulation, $f_s$ is the sampling frequency of the receiver, $\omega_r$ is the rotational velocity of the rotor, and $\omega_{Rev}$ is the rotation that the rotor makes in the simulation.
 
-In each frame a set number of rays are casted into the scene in a uniformly distributed circle in the direction of the rotor and receiver using
+In each frame a set number of rays are casted into the scene in a uniformly distributed circle in the direction of the rotor and receiver:
 
@@
 
-where $r_u$ and $\theta_u$ are uniformly distributed random variables from $0 \leq r_u \leq BladeLength^{2}$ and $ 0 \leq \theta_u \leq 2\pi$ respectively.
+where $r_u$ and $\theta_u$ are uniformly distributed random variables from $0 \leq r_u \leq r_b^{2}$ and $ 0 \leq \theta_u \leq 2\pi$ respectively.
 

### 2016-11-17 Results_new.tex
edits for figures and equations finished, working on scope and noise

@@
 %introduce the results section and what processing will be done
-The information gathered from the previous section is used to estimate the azimuth and elevation angles of the transmitter.
+The information gathered from the previous chapter is used to estimate the azimuth and elevation angles of the transmitter.
 First the azimuth angle will be estimated which will provide the information necessary for also calculating the elevation angle.
@@
 %formulate the estimation equation and discuss ambiguity considerations
-The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which a Doppler envelope and subsequent maximum and minimum values are calculated.
+The azimuth angle estimation technique is based on the data collected by rotating the helicopter platform in a clockwise manner, during which a Doppler profile and subsequent maximum and minimum values are calculated.
 After a complete rotation the Doppler maximum and minimum values produce a sinusoidal pattern as shown in Figure \ref{fig:tx_azimuth_angle_200} without knowing the starting azimuth angle.
 With this data we find an unambiguous angle that will set the coordinate space and provide an estimate of current azimuth angle.
-To do this the absolute value of the minimum envelope data is superimposed onto the maximum envelope data as shown in Figure \ref{fig:azimuth_estimation_max_vs_absMin}.
+To do this the absolute value of the minimum Doppler profile data is superimposed onto the maximum Doppler profile data as shown in Figure \ref{fig:azimuth_estimation_max_vs_absMin}.
 
@@
 		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_max_vs_absMin.eps}
-		\caption{Max and Absolute value of Min Envelope Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
+		\caption{Max and Absolute value of Min Doppler Profile Frequencies vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
 		\label{fig:azimuth_estimation_max_vs_absMin}
@@
 
-From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. We then take the difference
+From Figure \ref{fig:azimuth_estimation_max_vs_absMin} there are two points at which the maximums and the absolute value of the minimums cross. We then take the difference:
 
@@
 \begin{equation}
-	 Envelope Difference = Max Upper Envelope - | Min Lower Envelope |
+	 Profile Difference = Max Doppler Profile - | Min Doppler Profile |
 	 \label{eqn:difference}
@@
 
-where $Max Upper Envelope$ is an array of the maximum value of each upper envelope calculation, and $Min Lower Envelope$ is an array of the minimum value of each lower envelope calculation.
+where $Max Doppler Profile$ is an array of the maximum value of each upper profile calculation, and $Min Doppler Profile$ is an array of the minimum value of each lower profile calculation.
 The result is an almost exact sinusoid centered around zero, shown in Figure \ref{fig:azimuth_estimation_difference}.
@@
 		\includegraphics[width=10cm]{images/results/Azimuth_angle_estimation_difference.eps}
-		\caption{Difference between Max and Min Envelope Calculations vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
+		\caption{Difference between Max and Min Doppler Profile Calculations vs Transmitter Azimuth Angle at an Elevation Angle of 45\textdegree}
 		\label{fig:azimuth_estimation_difference}
@@
 While Figure \ref{fig:azimuth_estimation_difference} provides information about the angle of the transmitter it does not contain enough to locate an unambiguous azimuth angle in itself.
-Therefore by finding the correct Doppler for each azimuth, from the $Max Upper Envelope$ and the $| Min Lower Envelope |$, we can determine an unambiguous reference.
-This is done by evaluating the difference at each angle, and if the difference is negative the $| Min Lower Envelope |$ is used and if positive the $Max Upper Envelope$.
+Therefore by finding the correct Doppler for each azimuth, from the $Max Doppler Profile$ and the $| Min Doppler Profile |$, we can determine an unambiguous reference.
+This is done by evaluating the difference at each angle, and if the difference is negative the $| Min Doppler Profile |$ is used and if positive the $Max Doppler Profile$.
 
@@
 If this is not the case one will be chosen and the helicopter can fly in that direction.
-The resulting Doppler can then be measured, based on the physical movement of the helicopter or if the resulting envelope, to confirm the correct 90\textdegree \space location.
+The resulting Doppler can then be measured, based on the physical movement of the helicopter or if the resulting profile, to confirm the correct 90\textdegree \space location.
 
@@
 Using the information gathered from the azimuth estimation procedure, we can compute the elevation angle of the transmitter.
-In the process of gathering azimuth information, the maximum and minimum envelopes follow a sinusoidal pattern that contains a maximum Doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles.
-Using that maximum value, along with the correct Doppler and the assumption that the maximum will occur near the tip of the rotor blade, we can approximate the respected reflection radii off the blade as the azimuth angle changes.
-This is done through
+In the process of gathering azimuth information, the maximum and minimum profiles follow a sinusoidal pattern that contains a maximum Doppler information at approximately 180\textdegree \space and 0\textdegree \space azimuth angles.
+Using that maximum value, along with the correct Doppler and the assumption that the maximum will occur near the tip of the rotor blade, we can approximate the respected reflection radii by:
 %reflection radius aproximation equation
 \begin{equation}
-	R_{Estimate} = BladeLength \left(\frac{f_{DopplerCorrect}(\theta_{Az})}{Max(f_{DopplerCorrect})}\right)
+	R_{Estimate} = r_b \left(\frac{f_{DopplerCorrect}(\theta_{Az})}{Max(f_{DopplerCorrect})}\right)
 	\label{eqn:r_estimate}
@@
 
-where $R_{Estimate}$ is the estimated reflection radius at a particular azimuth, $BladeLength$ is the length of a single blade or radius of the rotor, and $f_{DopplerCorrect}$ is the correct Doppler frequency for each azimuth angle $\theta_{Az}$.
+where $R_{Estimate}$ is the estimated reflection radius at a particular azimuth, $r_b$ is the length of a single blade or radius of the rotor, and $f_{DopplerCorrect}$ is the correct Doppler frequency for each azimuth angle $\theta_{Az}$.
 
@@
 
-Now we find the maximum amount of Doppler that could be induced at that reflection radius location through
+Now we find the maximum amount of Doppler that could be induced at that reflection radius location is:
 %max doppler at radius location
@@
 where $f_{Doppler_{R Estimate Max}}$ is the maximum amount of Doppler that could happen at that location if the signal was reflected parallel to the direction of motion.
-$f_c$ is the center frequency of the signal, $c$ is the speed of light and $v_r$ is the radial velocity based of the $RPM$ defined by
+$f_c$ is the center frequency of the signal, $c$ is the speed of light and $v_r$ is the radial velocity based of the $\omega_r$ is:
 
@@
 \begin{equation}
-	v_r = \frac{2\pi}{60} RPM R_{Estimate}
+	v_r = \omega_r R_{Estimate}
 	\label{eqn:v_radial}
@@
 
-Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxUpperEnvelope$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate.
-We then solve for the elevation angle
+Then to find the elevation angle we look back at equation \ref{eq:theory_180_upper} swapping $MaxDopplerProfile$ with $f_{DopplerCorrect(\theta_{Az})}$ because this is now over the azimuth range and swap $f_{DopplerMax}$ for $f_{Doppler_{R Estimate Max}}$ because we need the maximum doppler for the current reflection estimate.
+We then solve for the elevation angle:
 
@@
 
-where $\theta_{El}$ is the elevation angle of the transmitter. If the elevation angle is all the information needed equation \ref{eqn:elevation_angle} distills down to
+where $\theta_{El}$ is the elevation angle of the transmitter. If the elevation angle is all the information needed equation \ref{eqn:elevation_angle} distills down to:
 
@@
 The error in elevation is caused by a limitation on the estimation.
-Where the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is calculated by
+Where the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is:
 
@@
 \begin{equation}
-	v_{rMax} = \frac{2\pi}{60} RPM BladeLength
+	v_{rMax} = \omega_r r_b
 	\label{eqn:v_radial_max}
@@
 
-then using that to find the maximum available Doppler through
+then using $v_{rMax}$ to find the maximum available Doppler:
 
@@
 This limitation is shown by varying the elevation angle at the azimuth angle that provides the maximum Doppler shift, which is 180\textdegree.
-The maximum and minimum envelope data is shown in Figure \ref{fig:envelope_180deg}
+The maximum and minimum profile data is shown in Figure \ref{fig:envelope_180deg}
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/results/Elevation_angle_envelopes_180deg_Azimuth.eps}
-		\caption{Max and Min Envelope Frequencies vs Elevation Angle with Transmitter Azimuth Angle of 180\textdegree}
+		\includegraphics[width=10cm]{images/simulation/elevation_angle_max_doppler_180deg.eps}
+		\caption{Max and Min Doppler Profile Frequencies vs Elevation Angle with Transmitter Azimuth Angle of 180\textdegree}
 		\label{fig:envelope_180deg}
@@
 The estimation method is accurate till elevation angles of 18\textdegree \space or 20\textdegree, where it becomes noisy.
-This is due to the inability of the envelope estimation to resolve the correct maximum Doppler for that range.
+This is due to the inability of the profile estimation to resolve the correct maximum Doppler for that range.
 By going back to Figure \ref{fig:tx_range_elevation_rel} we can see that as the transmitter moves farther and farther away the elevation angle is still decreasing but at a much smaller and smaller rate.
@@
 		\includegraphics[width=10cm]{images/results/difference_pitch_noCorrection.eps}
-		\caption{Uncorrected Envelope Difference vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
+		\caption{Uncorrected Doppler Profile Difference vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
 		\label{fig:diff_pitch_noCorrection}
@@
 		\includegraphics[width=10cm]{images/results/correct_dop_pitch_noCorrection.eps}
-		\caption{Uncorrected Doppler vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
+		\caption{Uncorrected Pitch Doppler Profile vs. Transmitter Azimuth and Elevation angle of 45\textdegree with Blade pitch of 7.5\textdegree}
 		\label{fig:dop_pitch_noCorrection}
@@
 
-Comparing the envelope difference of no pitch and pitched blade, in Figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
-Therefore we can first correct this by re-centering the pitch difference according to
+Comparing the Doppler profile difference of no pitch and pitched blade, in Figures \ref{fig:azimuth_estimation_difference} and \ref{fig:diff_pitch_noCorrection} respectively, we can see that the difference calculation of the pitch is a shifted up version of the one with no pitch.
+Therefore we can first correct this by re-centering the pitch difference:
 
 \begin{equation}
-	A_{shift} = \frac{Max(Max Upper Envelope) - |Min(Min Lower Envelope)|}{2}
+	A_{shift} = \frac{Max(Max Doppler Profile) - |Min(Min Doppler Profile)|}{2}
 	\label{eqn:pitch_shift}
@@
 
-where $A_{shift}$ is the amount that the difference calculation will be shifted down
+where $A_{shift}$ is the amount that the difference calculation will be shifted:
 
 \begin{equation}
-	EnvelopeDifference = EnvelopeDifference - A_{shift}
+	ProfileDifference = ProfileDifference - A_{shift}
 	\label{eqn:diff_shift}
@@
 
-Then with this knowledge $f_{DopplerCorrect}$ is recalculated and then is adjusted to the correct frequencies with
+Then $f_{DopplerCorrect}$ is recalculated and then adjusted to the correct frequencies:
 
@@
 
-Since $\theta_{Az}$ is unknown during the calculation of equation \ref{eqn:fd_pitch_correct} the correct starting phase can be determined by matching it to the $EnvelopeDifference$ and that the cosine should be one period in length.
+Since $\theta_{Az}$ is unknown during the calculation of equation \ref{eqn:fd_pitch_correct} the correct starting phase can be determined by matching it to the $ProfileDifference$ and that the cosine should be one period in length.
 These corrections result in the percent azimuth error of 0\% and 7\% elevation angle error.

### 2016-11-17 Simulation.tex
edits for figures and equations finished, working on scope and noise

@@
 
-After the computation of the short time Fourier transform; the Doppler envelope is calculated by performing a threshold on the power, in both the positive and negative Doppler, at each time slice.
-The envelope value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values.
+After the computation of the short time Fourier transform; the Doppler profile is calculated by performing a threshold on the power, in both the positive and negative Doppler, at each time slice.
+The profile value for that time slice is found by approaching zero frequency and stopping as the power reaches a predetermined level from both the negative and positive values.
 The power level to set the threshold is calculated differently based on whether the elevation or the azimuth parameter is being swept.
@@
 
-The Doppler envelopes are displayed in Figure \ref{fig:test_spec_w_doppler_profile}, the lower in blue and the upper in red.
-The minimum is calculated from the lower envelope, and the maximum from the upper envelope.
+The Doppler profiles are displayed in Figure \ref{fig:test_spec_w_doppler_profile}, the lower in blue and the upper in red.
+The minimum is calculated from the lower profile, and the maximum from the upper profile.
 Those values are then used to characterize that Doppler profile and analyze signal trends as different variables change.
@@
 The rotor blade length from Figure \ref{fig:rx_position_image} is 7.5 m so the receiver will be varied from 0 m to 9 m in 1 m increments.
-The resulting signal is analyzed by calculating its Doppler envelope.
-Then the maximum and minimum of that envelope will then be used to determined the overall effect of the position of the receiver.
+The resulting signal is analyzed by calculating its Doppler profile.
+Then the maximum and minimum of that profile will then be used to determined the overall effect of the position of the receiver.
 
@@
 		\includegraphics[width=10cm]{images/simulation/receiver_position_max_doppler.eps}
-		\caption{Max and Min Doppler vs. Receiver Position with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
+		\caption{Max and Min Doppler Profile vs. Receiver Position with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
 		\label{fig:rx_position}
@@
 Figure \ref{fig:rx_position} shows maximum Doppler versus the position of the receiver.
-From this graph, the maximum Doppler frequency changes significantly as the receiver is moved from directly underneath the rotor to past the tip of the rotor at 9 m.The position of the receiver also effects the resulting signal envelope shapes shown in Figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
+From this graph, the maximum Doppler frequency changes significantly as the receiver is moved from directly underneath the rotor to past the tip of the rotor at 9 m.The position of the receiver also effects the resulting signal profile shape shown in Figures \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m}.
 
@@
 		\includegraphics[width=10cm]{images/simulation/Doppler_Receiver_0m.eps}
-		\caption{Doppler Envelope with receiver at 0m}
+		\caption{Doppler Profile with receiver at 0m}
 		\label{fig:rx_position_0m}
@@
 		\includegraphics[width=10cm]{images/simulation/Doppler_Receiver_7m.eps}
-		\caption{Doppler Envelope with receiver at 7m}
+		\caption{Doppler Profile with receiver at 7m}
 		\label{fig:rx_position_7m}
@@
 
-Comparing the received signal envelopes Figure \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m} the maximum Doppler increase reflects the information in Figure \ref{fig:rx_position}.
-The envelope in Figure \ref{fig:rx_position_0m} is also much noisier than the envelope of Figure \ref{fig:rx_position_7m} and the signal envelope, for the receiver is at 7 m, has a distinctive shape with less variation between its two peaks.
+Comparing the received Doppler profiles Figure \ref{fig:rx_position_0m} and \ref{fig:rx_position_7m} the maximum Doppler increase reflects the information in Figure \ref{fig:rx_position}.
+The profile in Figure \ref{fig:rx_position_0m} is also much noisier than the profile of Figure \ref{fig:rx_position_7m} and the Doppler profile, for the receiver is at 7 m, has a distinctive shape with less variation between its two peaks.
 The position of the receiver will also determine whether the azimuth angle can be derived from the resulting signal shown later in section \ref{taa}.
@@
 
-The resulting signal is analyzed by calculating its Doppler envelope. Then the maximum and minimum of that envelope will then be used to determined the overall effect of pitching the rotor blade.
+The resulting signal is analyzed by calculating its Doppler profile. Then the maximum and minimum of that profile will then be used to determined the overall effect of pitching the rotor blade.
 
@@
 		\includegraphics[width=10cm]{images/simulation/pitch_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Rotor Pitch with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
+		\caption{Max and Min Doppler Profile Frequencies vs Rotor Pitch with Tx Azimuth at 135\textdegree \space and Elevation at 54\textdegree}
 		\label{fig:pitch_15_135deg}
@@
 		\includegraphics[width=10cm]{images/simulation/pitch_0txPos_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Rotor Pitch Transmitter Underneath the Helicopter}
+		\caption{Max and Min Doppler Profile Frequencies vs Rotor Pitch Transmitter Underneath the Helicopter}
 		\label{fig:pitch_tx0}
@@
 		\includegraphics[width=10cm]{images/simulation/elevation_angle_with_pitch_max_doppler.eps}
-		\caption{Max Envelope Frequencies vs Transmitter Elevation Angle}
+		\caption{Max Doppler Profile Frequencies vs Transmitter Elevation Angle}
 		\label{fig:pitch_tx_elevation_angle}
@@
 This is because the rays hitting the blades from below are reflecting into the receiver at an angle that is closer to the direction of blade travel.
-The interesting thing about this plot is that the pitch envelopes actually become closer to the 0\textdegree \space envelope as the elevation angle becomes smaller.
+The interesting thing about this plot is that the pitch profiles actually become closer to the 0\textdegree \space profile as the elevation angle becomes smaller.
 Figure \ref{fig:pitch_tx_elevation_angle_difference} shows the difference plotted over elevation angle.
@@
 		\includegraphics[width=10cm]{images/simulation/Azimuth_angle_rx0_max_doppler.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Azimuth Angle with Rx at Axis of Rotation}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle with Rx at Axis of Rotation}
 		\label{fig:tx_azimuth_rx0}
@@
 Pitching the blade modifies the results of the azimuth sweep when compared to Figure \ref{fig:tx_azimuth_angle_200}.
-The resulting minimum and maximum envelope frequencies versus azimuth angle for pitch are shown in Figure \ref{fig:pitch_azimuth_rev}.
+The resulting minimum and maximum profile frequencies versus azimuth angle for pitch are shown in Figure \ref{fig:pitch_azimuth_rev}.
 This occurs because the pitch of the blade angles RF reflections differently according to transmitter azimuth.
@@
 		\includegraphics[width=10cm]{images/simulation/pitch_azimuth_rev.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Elevation Angle with 7.5deg Pitch}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Elevation Angle with 7.5deg Pitch}
 		\label{fig:pitch_azimuth_rev}
@@
 From the model we see the amount of Doppler increase as the elevation angle decreases.
-This is mirrored in the simulation shown in Figure \ref{fig:tx_elevation_135deg} where the maximum measured Doppler as the elevation angle increases.
+This is mirrored in the simulation shown in Figure \ref{fig:tx_elevation_180deg} where the maximum measured Doppler decreases as the elevation angle increases.
 
@@
 	\begin{center}
-		\includegraphics[width=10cm]{images/simulation/elevation_angle_max_doppler_135deg.eps}
-		\caption{Max and Min Envelope Frequencies vs Transmitter Elevation Angle with Tx Azimuth of 135deg}
-		\label{fig:tx_elevation_135deg}
+		\includegraphics[width=10cm]{images/simulation/elevation_angle_max_doppler_180deg.eps}
+		\caption{Max and Min Doppler Profile Frequencies vs Transmitter Elevation Angle with Tx Azimuth of 180deg}
+		\label{fig:tx_elevation_180deg}
 	\end{center}
 \end{figure}
-%azimuth = 135deg, elevation = var
 
 Looking back at the geometric models for transmitter azimuth angles of 0\textdegree \space \ref{fig:3D_model_0az_doppler}, 90\textdegree \space \ref{fig:3D_model_90az_doppler}, 180\textdegree \space \ref{fig:3D_model_180az_doppler}, and 270\textdegree \space \ref{fig:3D_model_270az_doppler} and their simulated counterparts shown in Figure \ref{fig:verify}.
-We see that the ray traced results match their projections on the maximum and minimum envelope Doppler as transmitter elevation angle changes.
+We see that the ray traced results match their projections on the maximum and minimum Doppler Profile as transmitter elevation angle changes.
 The Doppler values do not match exactly but the trends are very similar.

### 2016-11-17 Thesis MATLAB Scripts/elevationEstimation_on_data_with_metadata.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_range_270deg_meta/*.csv');
 num_files = length(files);
 data = zeros(num_files,959006); %479000;
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_rangeFar_180deg/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/data_range_270deg_meta/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -85,11 +85,12 @@ end
 
 figure;
 hold on
-plot((location_data(:,5)/(2*pi))*360,data_table(:,2))
+
 plot((location_data(:,5)/(2*pi))*360,data_table(:,1))
+plot((location_data(:,5)/(2*pi))*360,data_table(:,2))
 hold off
-legend('Max Upper Envelope', 'Min Lower Envelope');
-title('Max and Min Envelope Frequencies vs Transmitter Elevation Angle');
+legend('Max Doppler Profile', 'Min Doppler Profile');
+title('Max and Min Doppler Profile Frequencies vs Transmitter Elevation Angle');
 xlabel('Transmitter Elevation Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 

### 2016-11-17 Thesis MATLAB Scripts/signal_analysis_pitch_0tx_pos.m

@@ -87,6 +87,6 @@ plot(pitch,data_table(:,1))
 plot(pitch,data_table(:,2))
 hold off
 legend('Max Doppler Profile', 'Min Doppler Profile');
-title('Max and Min Envelope Frequencies vs Rotor Pitch');
+title('Max and Min Doppler Profile Frequencies vs Rotor Pitch');
 xlabel('Rotor Pitch (deg)');
 ylabel('Doppler Frequency (Hz)');

### 2016-11-17 Thesis MATLAB Scripts/signal_analysis_pitch_135deg.m

@@ -83,6 +83,6 @@ plot(pitch,data_table(:,1))
 plot(pitch,data_table(:,2))
 hold off
 legend('Max Doppler Profile', 'Min Doppler Profile');
-title('Max and Min Envelope Frequencies vs Rotor Pitch');
+title('Max and Min Doppler Profile Frequencies vs Rotor Pitch');
 xlabel('Rotor Pitch (deg)');
 ylabel('Doppler Frequency (Hz)');

### 2016-11-17 Thesis MATLAB Scripts/signal_analysis_rx_position_y.m

@@ -85,6 +85,6 @@ plot(range,data_table(:,1))
 plot(range,data_table(:,2))
 hold off
 legend('Max Doppler Profile', 'Min Doppler Profile');
-title('Max and Min Envelope Frequencies vs Receiver distance');
+title('Max and Min Doppler Profile Frequencies vs Receiver distance');
 xlabel('Rx position (m)');
 ylabel('Doppler Frequency (Hz)');

### 2016-11-17 Thesis MATLAB Scripts/signal_analysis_tx_azimuth.m

@@ -1,10 +1,10 @@
 clear;
 
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/*.csv');
 num_files = length(files);
-data = zeros(num_files,479000);
+data = zeros(num_files,959000); %479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Centered/Altitude_200m/data_rotation_theta_far_range/',files(i).name)));
 end
 
 rpm = 250;
@@ -72,8 +72,8 @@ hold on
 plot(Azimuth,data_table(:,1))
 plot(Azimuth,data_table(:,2))
 hold off
-legend('Max Upper Envelope', 'Min Lower Envelope');
-title('Max and Min Envelope Frequencies vs Transmitter Azimuth Angle');
+legend('Max Doppler Profile', 'Min Doppler Profile');
+title('Max and Min Doppler Profile Frequencies vs Transmitter Azimuth Angle');
 xlabel('Transmitter Azimuth Angle (deg)');
 ylabel('Doppler Frequency (Hz)');
 

### 2016-11-17 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/*.csv');
 num_files = length(files);
 data = zeros(num_files,479000); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_50m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -19,7 +19,7 @@ RPM = 250;
 Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 50;
+tx_range = 200;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -29,13 +29,21 @@ pitch_corrected = 0;
 %shift data for different start sections
 %data = circshift(data,11,1);
 
-data_table = zeros(num_files,3);
+%data_table = zeros(num_files,3);
 
-%location_data = data(:,1:6);
-%data = data(:,7:end);
+% location_data = data(:,1:6);
+% data = data(:,7:end);
+
+hPhNoise = comm.PhaseNoise('Level',[-25 -40], ...
+        'FrequencyOffset',[10 1000], ...
+        'SampleRate',fs);
+
+ee = 1;
 
 for i=1:num_files
-    [s,f,t,p] = spectrogram(data(i,:),5000,500,5000,fs,'yaxis','centered');
+    s_awgn = awgn(data(i,:),-11.5);
+    s_pnoise = step(hPhNoise, data(i,:)');
+    [s,f,t,p] = spectrogram(s_awgn,5000,500,5000,fs,'yaxis','centered');
     angle_b1 = 0:(2*pi)/length(t):2*pi;
[…]

### 2016-11-17 Thesis MATLAB Scripts/test_pnoise.m

@@ -1,0 +1,12 @@
+% Create 16-QAM modulator
+    hMod = comm.RectangularQAMModulator(16, ...
+        'NormalizationMethod','Average power', 'AveragePower',10);
+% Create phase noise System object
+    hPhNoise = comm.PhaseNoise('Level',[-35 -100], ...
+        'FrequencyOffset',[10 200], ...
+        'SampleRate',1024);
+% Generate modulated symbols
+    modData = step(hMod, randi([0 15], 1000, 1));
+% Apply phase noise and plot the result
+    y = step(hPhNoise, modData);
+    scatterplot(y)

### 2016-11-17 Thesis MATLAB Scripts/test_snr_awgn.m

@@ -1,0 +1,6 @@
+t = (0:0.1:10)';
+x = sawtooth(t);
+
+y = awgn(x,-10);
+plot(t,[x y])
+legend('Original Signal','Signal with AWGN')

### 2016-11-19 Results_new.tex
added new tables and figured out db noise to affect the azimuth angle estimation...

@@
 
+\textcolor{red}{EDITED}
+
+The defined algorithm is then applied to a set of deterministic signals with various elevation angles and helicopter altitudes.
+There are 41 samples that make up the helicopter rotation starting at 0\textdegree \space following a counter clock wise progression ending back at 0\textdegree.
+This sampling method includes the 90\textdegree \space point but since there are only 41 discrete points there is an inherent error in the estimation of:
+
+\begin{equation}
+	\theta_{E_{samp}} = \frac{360}{2 n_{samples}}
+	\label{eqn:samp_error}
+\end{equation}
+
+where $\theta_{E_{samp}}$ is the error, in degrees, on either side of the algorithm selected 90\textdegree \space point, $n_{samples}$ is the number of unique sample angles.
+Therefore in this example there would be 40 unique sample points and a  $\theta_{E_{samp}} = 4.5$\textdegree.
+
 %azimuth error table
@@
     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
-     200 & 76\textdegree & 0 & 0  \\ \hline
-     200 & 45\textdegree & 0 & 0  \\ \hline 
-     200 & 26.5\textdegree & 0 & 0  \\ \hline
-     500 & 78.7\textdegree & 0 & 0  \\ \hline
-     500 & 51.34\textdegree & 0 & 0  \\ \hline 
-     500 & 35.5\textdegree & 0 & 0  \\ \hline
+     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     200 & 45\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
     \end{tabular}
@@
 
-From Table \ref{tab:az_error_and_percent} we can see that there is no error in the estimation of the 90\textdegree \space point over a variety of altitude and elevation angles that were tested.
-But because the algorithm could potentially pick the 270\textdegree \space we will analyze the difference in peak heights and the power difference to evaluate the estimation further.
+\textcolor{red}{EDITED}
+
+From Table \ref{tab:az_error_and_percent} we can see that the algorithm finds the exact 90\textdegree \space sample point over a variety of altitude and elevation angles of the deterministic signals.
+We analyze the difference in peak heights and the power difference to evaluate the estimation further due to the above accuracy.
 
@@
 Although from the frequency difference, at the large elevation angles, it is possible to confuse the estimation by just taking the minimum frequency.
-Therefore other values need to play a role such as the received power.
+Therefore other values need to play a role such as the received power in the following non-deterministic test signals.
+
+\textcolor{red}{EDITED}
+
+%alt 200
+%50 20db noise
+%200 12db noise
+%400 11.5db noise
+
+%alt 500
+%100 20db noise
+%400 12db noise
+%700 11.5db noise
+
+%azimuth error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
+     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     200 & 45\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+    \end{tabular}
+     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 11.5dB Noise}
+    \label{tab:az_error_and_percent_11db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 11.5dB)
+
+%azimuth error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
+     200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+    \end{tabular}
+     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 12dB Noise}
+    \label{tab:az_error_and_percent_12db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 12dB)
+
+%azimuth error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+     Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
+     200 & 76\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 78.7\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+    \end{tabular}
+     \caption{Azimuth Error and Azimuth Percent Error of Different Elevation Angles 20dB Noise}
+    \label{tab:az_error_and_percent_20db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 20dB)
 
@@
 There is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.
+
+\textcolor{red}{EDITED}
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree & \textdegree & \%  \\ \hline
+     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & \textdegree & \% \\ \hline
+     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
+     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 11.5dB Noise}
+    \label{tab:elevation_error_percent_11.5db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 11.5dB)
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree & \textdegree & \%  \\ \hline
+     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & \textdegree & \% \\ \hline
+     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
+     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 12dB Noise}
+    \label{tab:elevation_error_percent_12db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 12dB)
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree & \textdegree & \%  \\ \hline
+     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & \textdegree & \% \\ \hline
+     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
+     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 20dB Noise}
+    \label{tab:elevation_error_percent_20db}
+\end{center}
+\end{table}
+
+(text on trends in error with noise level at 20dB)
 

### 2016-11-19 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_700m/*.csv');
 num_files = length(files);
 data = zeros(num_files,479000); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_200m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_700m/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -16,10 +16,10 @@ end
 %--------------------------------------------------------------------------
 fs = 4000;
 RPM = 250;
-Altitude = 200;
+Altitude = 500;
 fc = 1e9;
 c = 3e8;
-tx_range = 200;
+tx_range = 700;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -93,8 +93,8 @@ for i=1:num_files
 end
 
 %fix estimation error on first envelope -----
-%data_table(1,1) = data_table(length(data_table),1);
-%data_table(1,2) = data_table(length(data_table),2);
+data_table(1,1) = data_table(length(data_table),1);
+data_table(1,2) = data_table(length(data_table),2);
 %important ----------------------------------
 
 

### 2016-11-23 Results_new.tex
added data to tables

@@
      200 & 45\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
-     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     200 & 26.5\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
      500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
      500 & 51.34\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline 
-     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 35.5\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
     \end{tabular}
@@
      200 & 76\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
-     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
-     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     200 & 45\textdegree & $\pm$13.5\textdegree & $\pm15\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
      500 & 78.7\textdegree & $\pm4.5$\textdegree & $\pm5\%$  \\ \hline
-     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
-     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
     \end{tabular}
@@
      Altitude & Elevation Angle & Azimuth Error in (deg) & Percent Error \\ \hline
-     200 & 76\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
-     200 & 45\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
-     200 & 26.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
-     500 & 78.7\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
-     500 & 51.34\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline 
-     500 & 35.5\textdegree & $\pm$\textdegree & $\pm\%$  \\ \hline
+     200 & 76\textdegree & $\pm22.5$\textdegree & $\pm25\%$  \\ \hline
+     200 & 45\textdegree & $\pm31.5$\textdegree & $\pm35\%$  \\ \hline 
+     200 & 26.5\textdegree & $\pm59.5$\textdegree & $\pm65\%$  \\ \hline
+     500 & 78.7\textdegree & $\pm13.5$\textdegree & $\pm15\%$  \\ \hline
+     500 & 51.34\textdegree & $\pm40.5$\textdegree & $\pm45\%$  \\ \hline 
+     500 & 35.5\textdegree & $\pm67.5$\textdegree & $\pm75\%$  \\ \hline
     \end{tabular}
@@
     Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree & \textdegree & \%  \\ \hline
-     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 76\textdegree &0.5533\textdegree & 0.7284\%  \\ \hline
+     200 & 45\textdegree & -0.2647\textdegree & -0.5882\%  \\ \hline 
      200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & \textdegree & \% \\ \hline
-     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
-     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & 0.7923\textdegree & 1.0069\% \\ \hline
+     500 & 51.34\textdegree & -0.3978\textdegree & -0.7747\%  \\ \hline 
+     500 & 35.5\textdegree & -3.9893\textdegree & -11.2255\%  \\ \hline
     \end{tabular}
@@
     Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree & \textdegree & \%  \\ \hline
-     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 76\textdegree & 0.6966\textdegree & 0.9170\%  \\ \hline
+     200 & 45\textdegree & -2.3497\textdegree & -5.2215\%  \\ \hline 
      200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & \textdegree & \% \\ \hline
-     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
-     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & 0.8916\textdegree & 1.1331\% \\ \hline
+     500 & 51.34\textdegree & -4.8613\textdegree & -9.4687\%  \\ \hline 
+     500 & 35.5\textdegree & 7.8398\textdegree & 22.0606\%  \\ \hline
     \end{tabular}
@@
     Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree & \textdegree & \%  \\ \hline
-     200 & 45\textdegree & \textdegree & \%  \\ \hline 
+     200 & 76\textdegree & -9.6248\textdegree & -12.6703\%  \\ \hline
+     200 & 45\textdegree & 7.8795\textdegree & 17.5099\%  \\ \hline 
      200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & \textdegree & \% \\ \hline
-     500 & 51.34\textdegree & \textdegree & \%  \\ \hline 
-     500 & 35.5\textdegree & \textdegree & \%  \\ \hline
+     500 & 78.7\textdegree & 1.3260\textdegree & 1.6851\% \\ \hline
+     500 & 51.34\textdegree & 4.5056\textdegree & 8.7760\%  \\ \hline 
+     500 & 35.5\textdegree & 20.8592\textdegree & 58.6959\%  \\ \hline
     \end{tabular}

### 2016-11-23 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_700m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/*.csv');
 num_files = length(files);
 data = zeros(num_files,479000); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_700m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -16,10 +16,10 @@ end
 %--------------------------------------------------------------------------
 fs = 4000;
 RPM = 250;
-Altitude = 500;
+Altitude = 200;
 fc = 1e9;
 c = 3e8;
-tx_range = 700;
+tx_range = 400;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -287,5 +287,6 @@ figure;
 plot(Azimuth,((test_alg_Elevation_angle_actual - atan(Altitude/tx_range))./atan(Altitude/tx_range))*100);
 title('Percent Error actual')
 
-AverageElevationError = (mean((test_alg_Elevation_angle_adj - atan(Altitude/tx_range)))/(2*pi))*360
-AverageElevationPercentError = mean(((test_alg_Elevation_angle_adj - atan(Altitude/tx_range))./atan(Altitude/tx_range))*100)
+AverageElevationError = (mean((abs(test_alg_Elevation_angle_adj) - atan(Altitude/tx_range)))/(2*pi))*360
+AverageElevationPercentError = mean(((abs(test_alg_Elevation_angle_adj) - atan(Altitude/tx_range))./atan(Altitude/tx_range))*100)
+close all;

### 2016-11-26 Background.tex
remove red markers, get ready to publish

@@
 \section{Thesis Scope}
-\textcolor{red}{EDITED}
 
@@
 The ray tracing software developed for the thesis is created for the sole purpose of understanding RBM.
-In order to determine the signals interaction with the moving rotor blade in an ideal environment, the ray traced scene is limited to the rotor blades, transmitter and receiver.
+In order to determine the signals interaction with the moving rotor blade, in an ideal environment, the ray traced scene is limited to the rotor blades, transmitter and receiver.
 The signal produced by the simulation is used to derive an algorithm that determines both the azimuth and elevation angle of a transmitter.
-The derived algorithm is then evaluated on both the deterministic signal to determine its azimuth and elevation accuracy.
+The derived algorithm is then evaluated on the deterministic signal to determine its azimuth and elevation accuracy.
 The algorithm is then tested again on signals in the presence of differing levels of noise to determine the algorithm's performance in a more realistic environment.

### 2016-11-26 Conclusion.tex
remove red markers, get ready to publish

@@
 Then with those trends an algorithm was derived to find the azimuth and elevation angle of the transmitter with relationship to the helicopter platform.
-The algorithm accurately finds the azimuth angle and elevation using the data collected in the simulation environment with almost no error in the azimuth estimation and less than 2\% error in elevation angle when blade pitch in 0\textdegree.
+The algorithm accurately finds the azimuth angle and elevation using the data collected in the simulation environment with little error in the azimuth estimation and less than 2\% error in elevation angle when blade pitch in 0\textdegree under a deterministic signal.
+With the addition of Gaussian noise the algorithm stays relatively constant up to a certain point, then both the azimuth and elevation estimations start to degrade with decreasing elevation angle and increasing noise level.
+For the simulation scenarios conducted, once the level of noise exceeded 10dB the algorithm started to degrade, but this level will most likely change if other simulation parameters are chosen.
 

### 2016-11-26 Results_new.tex
remove red markers, get ready to publish

@@
 
-\textcolor{red}{EDITED}
-
 The defined algorithm is then applied to a set of deterministic signals with various elevation angles and helicopter altitudes.
@@
 
-where $\theta_{E_{samp}}$ is the error, in degrees, on either side of the algorithm selected 90\textdegree \space point, $n_{samples}$ is the number of unique sample angles.
+where $\theta_{E_{samp}}$ is the error, in degrees, on either side of the selected 90\textdegree \space point, $n_{samples}$ is the number of unique sample angles.
 Therefore in this example there would be 40 unique sample points and a  $\theta_{E_{samp}} = 4.5$\textdegree.
@@
 \end{table}
-
-\textcolor{red}{EDITED}
 
@@
 
-\textcolor{red}{EDITED}
-
-%alt 200
-%50 20db noise
-%200 12db noise
-%400 11.5db noise
-
-%alt 500
-%100 20db noise
-%400 12db noise
-%700 11.5db noise
+Adding various levels of Gaussian noise to the received signal degrades the performance of the azimuth estimation.
+The estimation technique is resilient to noise, showing no change in performance until a certain level of noise is achieved.
+For the simulated altitudes and elevation angles, for the chosen simulation parameters, there is a noticeable degradation in performance of the estimation at small elevation angles starting at 11.5dB of noise.
 
@@
 
-(text on trends in error with noise level at 11.5dB)
+Table \ref{tab:az_error_and_percent_11db} shows that the performance has not changed for the higher elevation angles, while the smallest elevation angle azimuth estimations show significant error increase.
+Increasing the level of noise to 12dB starts to affect the azimuth estimation of the 45\textdegree \space and 51.34\textdegree \space elevation angle simulations shown in Table \ref{tab:az_error_and_percent_12db}.
+Increasing the noise from 11.5dB to 12dB does not show an increased error in elevation angles of 26.5\textdegree \space and 35.5\textdegree.
 
@@
 
-(text on trends in error with noise level at 12dB)
+In order for additional noise to start affecting the simulated elevation angles of 76\textdegree \space and 78.7\textdegree \space,  the added noise is raised to 20dB.
+Table \ref{tab:az_error_and_percent_20db} shows the azimuth estimation error for 20dB of added noise, where all the elevation angle simulations show an increased azimuth estimation error where elevation angles of 26.5\textdegree \space and 35.5\textdegree are affected the most.
 
@@
 
-(text on trends in error with noise level at 20dB)
+The azimuth estimation does very well under 10dB of noise, after that point it starts to degrade with decreasing elevation angle as well as increasing level of noise.
+The reason why estimation error start to show at 10dB of added noise can be traced back to the fact that the Doppler profile is estimated using a power threshold on the short time Fourier transform.
+This means that the added noise level must increase close to or beyond the threshold to start affecting the Doppler profile and the subsequent azimuth estimation.
 
@@
 From Table \ref{tab:elevation_error_percent} we can see elevation estimation error is extremely small for the given elevation angles.
-There is a trend that is evident in the data that as the elevation angle decreases the amount of error is increasing.
-
-\textcolor{red}{EDITED}
-
-% Elevation error table
-\begin{table}
-\begin{center}
-    \begin{tabular}{ | l | l | l | l |}
-    \hline
-    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree &0.5533\textdegree & 0.7284\%  \\ \hline
-     200 & 45\textdegree & -0.2647\textdegree & -0.5882\%  \\ \hline 
-     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & 0.7923\textdegree & 1.0069\% \\ \hline
-     500 & 51.34\textdegree & -0.3978\textdegree & -0.7747\%  \\ \hline 
-     500 & 35.5\textdegree & -3.9893\textdegree & -11.2255\%  \\ \hline
-    \end{tabular}
-    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 11.5dB Noise}
-    \label{tab:elevation_error_percent_11.5db}
-\end{center}
-\end{table}
-
-(text on trends in error with noise level at 11.5dB)
-
-% Elevation error table
-\begin{table}
-\begin{center}
-    \begin{tabular}{ | l | l | l | l |}
-    \hline
-    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree & 0.6966\textdegree & 0.9170\%  \\ \hline
-     200 & 45\textdegree & -2.3497\textdegree & -5.2215\%  \\ \hline 
-     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & 0.8916\textdegree & 1.1331\% \\ \hline
-     500 & 51.34\textdegree & -4.8613\textdegree & -9.4687\%  \\ \hline 
-     500 & 35.5\textdegree & 7.8398\textdegree & 22.0606\%  \\ \hline
-    \end{tabular}
-    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 12dB Noise}
-    \label{tab:elevation_error_percent_12db}
-\end{center}
-\end{table}
-
-(text on trends in error with noise level at 12dB)
-
-% Elevation error table
-\begin{table}
-\begin{center}
-    \begin{tabular}{ | l | l | l | l |}
-    \hline
-    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
-     200 & 76\textdegree & -9.6248\textdegree & -12.6703\%  \\ \hline
-     200 & 45\textdegree & 7.8795\textdegree & 17.5099\%  \\ \hline 
-     200 & 26.5\textdegree & \textdegree & \%  \\ \hline
-     500 & 78.7\textdegree & 1.3260\textdegree & 1.6851\% \\ \hline
-     500 & 51.34\textdegree & 4.5056\textdegree & 8.7760\%  \\ \hline 
-     500 & 35.5\textdegree & 20.8592\textdegree & 58.6959\%  \\ \hline
-    \end{tabular}
-    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 20dB Noise}
-    \label{tab:elevation_error_percent_20db}
-\end{center}
-\end{table}
-
-(text on trends in error with noise level at 20dB)
+There is a trend that as the elevation angle decreases the amount of error is increasing.
 
@@
 
-The error in elevation is caused by a limitation on the estimation.
+The error in elevation, on the deterministic signal, is caused by a limitation on the estimation.
 Where the Doppler shift is limited by the maximum amount Doppler that the blade rotation can produce shown in equation \ref{eqn:v_radial} by replacing $v_r$ with $v_rMax$ which is:
@@
 %------------------------------
+%Noise considerations
+%------------------------------
+
+The elevation estimation technique is then tested on the received signals with added noise at the same levels that were previously added for azimuth estimation tests.
+Starting at 11.5dB of noise, Table \ref{tab:elevation_error_percent_11.5db} shows that the error in estimation is significantly increased at elevation angles of 26.5\textdegree \space and 35.5\textdegree.
+The other elevation angle estimation errors stay relatively similar to estimation under deterministic signals except for 78.7\textdegree which has increased, but not to the same degree as the elevation angles of 26.5\textdegree \space and 35.5\textdegree.
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree &0.5533\textdegree & 0.7284\%  \\ \hline
+     200 & 45\textdegree & -0.2647\textdegree & -0.5882\%  \\ \hline 
+     200 & 26.5\textdegree & 1.9321\textdegree & 7.2731\%  \\ \hline
+     500 & 78.7\textdegree & 0.7923\textdegree & 1.0069\% \\ \hline
+     500 & 51.34\textdegree & -0.3978\textdegree & -0.7747\%  \\ \hline 
+     500 & 35.5\textdegree & -3.9893\textdegree & -11.2255\%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 11.5dB Noise}
+    \label{tab:elevation_error_percent_11.5db}
+\end{center}
+\end{table}
+
+Increasing the noise level to 12dB the error in elevation estimation almost doubles for elevation angles of 26.5\textdegree \space and 35.5\textdegree \space shown in Table \ref{tab:elevation_error_percent_12db}.
+The increased noise also affects the estimation of elevation angles 45\textdegree \space and 51.34\textdegree, increasing the error from -0.5882\% to -5.2215\% and -0.7747\% to -9.4687\% respectively.
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree & 0.6966\textdegree & 0.9170\%  \\ \hline
+     200 & 45\textdegree & -2.3497\textdegree & -5.2215\%  \\ \hline 
+     200 & 26.5\textdegree & 3.9078\textdegree & 14.7102\%  \\ \hline
+     500 & 78.7\textdegree & 0.8916\textdegree & 1.1331\% \\ \hline
+     500 & 51.34\textdegree & -4.8613\textdegree & -9.4687\%  \\ \hline 
+     500 & 35.5\textdegree & 7.8398\textdegree & 22.0606\%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 12dB Noise}
+    \label{tab:elevation_error_percent_12db}
+\end{center}
+\end{table}
+
+At the noise level of 20dB the estimation of elevation angle 76\textdegree \space experiences an error of -12.6703\%.
+While the elevation angle of 78.7\textdegree \space error increases from 1.1331\% to 1.6851\% shown in Table \ref{tab:elevation_error_percent_20db}.
+
+% Elevation error table
+\begin{table}
+\begin{center}
+    \begin{tabular}{ | l | l | l | l |}
+    \hline
+    Altitude & Elevation Angle & Average Elevation Error in (deg) & Average Percent Error \\ \hline
+     200 & 76\textdegree & -9.6248\textdegree & -12.6703\%  \\ \hline
+     200 & 45\textdegree & 7.8795\textdegree & 17.5099\%  \\ \hline 
+     200 & 26.5\textdegree & 16.7304\textdegree & 62.9791\%  \\ \hline
+     500 & 78.7\textdegree & 1.3260\textdegree & 1.6851\% \\ \hline
+     500 & 51.34\textdegree & 4.5056\textdegree & 8.7760\%  \\ \hline 
+     500 & 35.5\textdegree & 20.8592\textdegree & 58.6959\%  \\ \hline
+    \end{tabular}
+    \caption{Average Elevation Error and Average Elevation Percent Error of Different Elevation Angles 20dB Noise}
+    \label{tab:elevation_error_percent_20db}
+\end{center}
+\end{table}
+
+From the Table \ref{tab:elevation_error_percent_12db} to Table \ref{tab:elevation_error_percent_20db} the other estimation errors have now increased as well.
+The increased errors make elevation angles of 26.5\textdegree \space and 35.5\textdegree \space unresolvable.
+This means that as the noise level increases the other elevation angles will start to exhibit increasing errors in estimated elevation angle to the point where any elevation angle cannot be accurately estimated.
+
+The elevation angle estimation is more susceptible to noise than the azimuth estimation because it uses the maximum value found in the Doppler profile to find elevation angle from equation \ref{eqn:elevation_angle_only}.
+Therefor when noise is added the doppler profiles maximum value will fluctuate causing errors in elevation angle estimation.
+
+%------------------------------
 %pitch considerations
@@
 
-If we now consider a pitched blade the above method for estimating azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side.
+If we now consider a pitched blade, on the deterministic signal, the derived method for estimating azimuth and elevation becomes inaccurate due to the increased Doppler between 90\textdegree \space and 270\textdegree \space and the decreased Doppler on the other side.
 To correct this error we need to correct both the difference calculation and the correct Doppler data accordingly.

### 2016-11-26 Thesis MATLAB Scripts/test_alg_az_and_el_angle.m

@@ -4,11 +4,11 @@ clear;
 %--------------------------------------------------------------------------
 %Load Data
 %--------------------------------------------------------------------------
-files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/*.csv');
+files= dir('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_100m/*.csv');
 num_files = length(files);
 data = zeros(num_files,479000); %959000;  479000
 for i=1:num_files
-     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_200m/rotate_degs_400m/',files(i).name)));
+     data(i,:)=transpose(csvread(strcat('/Users/tschucker/Desktop/Thesis_data/Receiver_Off_Axis_7m/Altitude_500m/rotate_degs_100m/',files(i).name)));
 end
 
 %--------------------------------------------------------------------------
@@ -16,10 +16,10 @@ end
 %--------------------------------------------------------------------------
 fs = 4000;
 RPM = 250;
-Altitude = 200;
+Altitude = 500;
 fc = 1e9;
 c = 3e8;
-tx_range = 400;
+tx_range = 100;
 pitch_corrected = 0;
 
 %--------------------------------------------------------------------------
@@ -41,7 +41,7 @@ hPhNoise = comm.PhaseNoise('Level',[-25 -40], ...
 ee = 1;
 
 for i=1:num_files
-    s_awgn = awgn(data(i,:),-11.5);
+    s_awgn = awgn(data(i,:),-20);
     s_pnoise = step(hPhNoise, data(i,:)');
     [s,f,t,p] = spectrogram(s_awgn,5000,500,5000,fs,'yaxis','centered');
     angle_b1 = 0:(2*pi)/length(t):2*pi;
